---
shorttitle        : "Measurement timing"
format          : "pandoc"
header-includes:
  - \usepackage{nccmath}
  - \usepackage{caption}
  - \usepackage{textcomp} #for copyright symbol on title page
  - \usepackage{longtable}
  - \usepackage{makecell}
  - \usepackage[section]{placeins}
  - \usepackage{setspace}
  - \usepackage{biblatex}
  - \usepackage{booktabs}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{xcolor}
  - \usepackage{amsthm} 
  - \usepackage{amsmath} ##needed for argmax
  - \usepackage{bm}  #thicker bold in math 
  - \DeclareMathOperator*{\argmax}{arg\,max}
  - \usepackage{setspace} #needed to doublespace caption text (using \doublespacing)
  - \usepackage[labelfont = {bf, up}]{caption} 
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \usepackage{upgreek}  #required for non-italicized Greek letters
  - \usepackage{subcaption}
  - \captionsetup[figure]{labelfont={normalfont, bf}, singlelinecheck=false, labelsep=newline}
  - \DeclareCaptionFont{figCaptionFont}{\fontfamily{phv}\doublespacing} #sets caption font to sans serif font of Helvetica 
  - \DeclareCaptionFont{figCaptionSize}{\fontsize{11pt}{13.2pt}\selectfont} #set caption font size to footnote 
  - \DeclareCaptionFont{tabCaptionSize}{\small} #caption size for table title
  - \DeclareCaptionFont{figCaptionStyle}{\textup}  #set caption font to non-italicized font  
  - \DeclareCaptionLabelSeparator{captionSep}{\newline} #separates figure label and figure title with required white space
  - \captionsetup[figure]{labelfont={figCaptionStyle, bf}, font = {figCaptionFont,figCaptionSize, figCaptionStyle}, labelsep = captionSep, justification= raggedright}
  - \captionsetup[table]{labelfont={tabCaptionSize, bf}, font = {figCaptionFont, tabCaptionSize, figCaptionStyle}, labelsep = captionSep, justification= raggedright}
  - \newenvironment{helvenv}{\fontfamily{phv}\selectfont}{}
  - \raggedbottom #ensures text starts from top of page and any white space is at the botom

#both are needed to change font type of table footnotes
  - \usepackage{anyfontsize}
  - \AtBeginEnvironment{ThreePartTable}{\fontfamily{phv} \fontsize{10.5pt}{12pt}\selectfont} 
  - \AtBeginEnvironment{tablenotes}{\fontsize{9.5pt}{11.4pt}\selectfont} 

#environment numbering 
  - \setcounter{section}{0} 
  - \makeatletter \renewcommand\thesection{}\renewcommand\thesubsection{\@arabic\c@section.\@arabic\c@subsection} \makeatother

#set table line widths 
  - \setlength\cmidrulewidth{1pt} #line thickness of lines within table and in multi-row headers
  - \setlength\lightrulewidth{1pt} #line thickness of bottom line in header 

  - \newtheorem{theorem}{Theorem}
  - \newtheorem{example}[theorem]{Example}
  - \renewcommand\theadfont{} #sets cell font to be same as table font 
  
  #set figure title text
  - \newcommand{\figurefootnote}{\raggedright\linespread{2}\fontfamily{phv}\fontsize{9.5pt}{11.4pt}\selectfont \textit{Note. }}
  
  #modifies heading levels of 4-5 to follow apa7
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}
    
    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother
  
  
author: 
  - name          : "Sebastian Sciarra "
    affiliation   : "1"
    corresponding : yes    
    email         : "ssciarra@uoguelph.ca"
affiliation: 
  - id            : "1"
    institution   : "University of Guelph"
keywords          : "measurement timing, nonlinear "
wordcount         : "5554 words"
floatsintext      : yes
linkcolor         : blue
figsintext        : yes 
figurelist        : no
tablelist         : no
footnotelist      : no
numbersections    : yes
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa7"
csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
classoption       : "man"
output            : papaja::apa6_pdf
keep_tex: true
editor_options: 
  markdown: 
    wrap: 72
bibliography: dissertation_references.bib
---
```{r package_loading_2, include=F}
#load packages
library(easypackages)
packages <- c('devtools','tidyverse', 'RColorBrewer', 'parallel', 'data.table', 'kableExtra', 'ggtext', 'egg', 'nonlinSims','papaja', 
              'ggbrace', 'cowplot')
libraries(packages)
load_all()
```

```{r knitting_setup_2, echo=F, message = F, warning = F}
#import raw data files (needed for computing variances)
exp_1_raw <- convert_raw_var_to_sd(raw_data = read_csv('data/exp_1_data.csv')) %>%
  mutate_at(.vars = c("number_measurements", "measurement_spacing", "midpoint"), factor)
  
exp_2_raw <-convert_raw_var_to_sd(raw_data = read_csv('data/exp_2_data.csv')) %>%
  mutate_at(.vars = c("number_measurements", "measurement_spacing", "sample_size"), factor)

exp_3_raw <-convert_raw_var_to_sd(raw_data = read_csv('data/exp_3_data.csv')) %>%
  mutate_at(.vars = c("number_measurements", "time_structuredness", "sample_size"), factor)

#unfiltered data 
param_summary_exp_1 <- readRDS(file = 'data/uf_param_summary_exp_1.RData')
param_summary_exp_2 <- readRDS(file = 'data/uf_param_summary_exp_2.RData')
param_summary_exp_3 <- readRDS(file = 'data/uf_param_summary_exp_3.RData')

#create analytical versions of summary data + converts vars to sds
exp_1_analytical <- generate_likert_days_data_sets(summary_data = param_summary_exp_1, exp_num = '1')
exp_2_analytical <- generate_likert_days_data_sets(summary_data = param_summary_exp_2, exp_num = '2')
exp_3_analytical <- generate_likert_days_data_sets(summary_data = param_summary_exp_3, exp_num = '3')

combined_analytical_exp_1 <- rbind(exp_1_analytical$likert, exp_1_analytical$days)
combined_analytical_exp_2 <- rbind(exp_2_analytical$likert, exp_2_analytical$days)
combined_analytical_exp_3 <- rbind(exp_3_analytical$likert, exp_3_analytical$days)

#create condition summary data sets 
cond_summary_exp_1 <- compute_condition_summary(param_summary_data = combined_analytical_exp_1, facet_var = 'measurement_spacing', 
                          ind_vars = c('number_measurements', 'measurement_spacing', 'midpoint'))
cond_summary_exp_2 <- compute_condition_summary(param_summary_data = combined_analytical_exp_2, facet_var = 'measurement_spacing', 
                  ind_vars = c('number_measurements', 'measurement_spacing', 'sample_size'))

cond_summary_exp_3 <- compute_condition_summary(param_summary_data = combined_analytical_exp_3, facet_var = 'time_structuredness', 
                          ind_vars = c('number_measurements', 'sample_size', 'time_structuredness'))
```

```{r pre_knitting_setup_unfiltered_2, echo=F, eval=F, include=F}
#code should be computed before knitting to decrease knitting time 
#load data from experiments
exp_1 <- read_csv(file = 'data/exp_1_data.csv') %>% filter(code == 0)
exp_2 <- read_csv(file = 'data/exp_2_data.csv')
exp_3 <- read_csv(file = 'data/exp_3_data.csv')

#compute parameter summary statistics  
exp_1_long <- exp_1 %>%
    filter(code == 0) %>%
    #place parameter estimates in one column
    pivot_longer(cols = contains(c('theta', 'alpha', 'beta', 'gamma', 'epsilon')),
                 names_to = 'parameter', values_to = 'estimate') %>%
    filter(parameter == 'beta_fixed') %>%
    mutate(pop_value = midpoint)

exp_1_ordered <- order_param_spacing_levels(data = exp_1_long)

exp_1_ordered %>%
      #compute statistics for each parameter for each experimental variable
      group_by(parameter, .dots = locate_ivs(exp_1_ordered)) %>%
      summarize(
       lower_ci = compute_middle_95_estimate(param_data = estimate)[1],
       upper_ci = compute_middle_95_estimate(param_data = estimate)[2])

compute_parameter_summary(data = exp_1, exp_num = '1')

param_summary_exp_1 <- compute_parameter_summary(data = exp_1, exp_num = 1)
param_summary_exp_2 <- compute_parameter_summary(data = exp_2, exp_num = 2)
param_summary_exp_3 <- compute_parameter_summary(data = exp_3, exp_num = 3)

#necessary factor conversions 
param_summary_exp_1$number_measurements <- factor(param_summary_exp_1$number_measurements, levels = c(5, 7, 9,11))
param_summary_exp_1$midpoint <- factor(param_summary_exp_1$midpoint, levels = c(80, 180,280))

param_summary_exp_2$number_measurements <- factor(param_summary_exp_2$number_measurements, levels = c(5, 7, 9,11))
param_summary_exp_2$sample_size <- factor(param_summary_exp_2$sample_size, levels = c(30, 50, 100, 200, 500, 1000))

param_summary_exp_3$number_measurements <- factor(param_summary_exp_3$number_measurements, levels = c(5, 7, 9,11))
param_summary_exp_3$sample_size <- factor(param_summary_exp_3$sample_size, levels = c(30, 50, 100, 200, 500, 1000))

#write data sets 
#save parameter summary files as RData files so that metadata are correctly stored (e.g., factor levels, variable types)
saveRDS(object = param_summary_exp_1, file = 'data/uf_param_summary_exp_1.RData')
saveRDS(object = param_summary_exp_2, file = 'data/uf_param_summary_exp_2.RData')
saveRDS(object = param_summary_exp_3, file = 'data/uf_param_summary_exp_3.RData')
```



```{=tex}
\newpage
\vspace*{-\topskip}
\vspace*{\fill}
\nointerlineskip
```
# Experiment 3

```{=tex}
\nointerlineskip
\vfill
\newpage
```

In Experiment 3, I investigated the measurement number-sample size pairings needed to achieve accurate modelling (i.e., low bias and high precision) under different levels of time structuredness. Before presenting the results of Experiment 3, I will present my design and and analysis goals. For the design, I conducted a 3(time structuredness: time-structured data, time-unstructured data [fast response rate], time-unstructured data [slow response rate]) x 4(number of measurements: 5, 7, 9, 11) x 6(sample size: 30, 50, 100, 200, 500, 1000) study. For the analysis, I was primarily interested in determining, for each level of time structuredness, what measurement number-sample size pairings achieved accurate modelling (i.e., low bias and high precision). 


## Methods
### Variables Used in Simulation Experiment 

#### Independent Variables

##### Number of Measurements

I used the following values for the number of measurements: 5, 7, 9, and 11 (see [number of measurements](#number-measurements} for more discussion)).  

##### Sample Size

I used the following values for sample size: 30, 50, 100, 200, 500, and 100 (see [sample size](#sample-size) for more discussion). 

##### Time Structuredness and the Simulation Procedure

To simulate time-unstructured data, response rates at each collection
point followed an exponential pattern described by either a fast or slow
response rate (for a review, see section on [time
structuredness](#sec:time-structuredness)). Importantly, data generated
for each person at each time point had to be sampled according to a
probability density function defined by either the fast or slow response
rate cumulative distribution function. In the current context, a
**probability density function** describes the probability of sampling
any given time delay value $x$ where the range of time delay values is
0--36 ($\{x : 0 \le x \le  36 \}$). To obtain the probability density functions
for fast and slow response rates, the response rate function shown in
Equation \@ref(eq:exponential) was differentiated with respect to $x$ to
obtain the function shown below in Equation \ref{eq:pdf-function}\footnote{Euler's notation for differentiation is used to represent derivatives. In words, $\frac{\partial f(x)}{\partial x}$ means that the derivative of the function $f(x)$ is taken with respect to $x$.}:

```{=tex}
\begin{align}
f^\prime = \frac{\partial f(x)}{\partial x} &= \frac{\partial}{\partial x}M(1 - e^{-ax}). \nonumber \\
&= M (e^{-ax}a)
(\#eq:pdf-function)
\end {align}
```

\noindent To compute the probability density function for the fast
response rate cumulative distribution function, the growth rate
parameter $a$ was set to 0.37 in Equation \ref{eq:pdf-function} to
obtain the following function in Equation \ref{eq:fast-pdf-function}:

```{=tex}
\begin{align}
f^\prime_{fast}(x) = M (e^{-a_{fast}x}a_{fast}) = M (e^{-0.37x}0.37). 
(\#eq:fast-pdf-function)
\end {align}
```
\noindent To compute the probability density function for the slow
response rate cumulative distribution function, the growth rate
parameter $a$ was set to 0.15 in Equation \ref{eq:pdf-function} to
obtain the following function in Equation \ref{eq:slow-pdf-function}:

```{=tex}
\begin{align}
f^\prime_{slow}(x) = M (e^{-0.15}a_{slow}) = M (e^{-0.15}0.15). 
(\#eq:slow-pdf-function)
\end {align}
```
Figure \ref{fig:cdf-pdf-plots} shows the fast and slow response
cumulative distribution functions (CDF) and their corresponding
probability density functions (PDF). Panel A shows the cumulative
distribution function for the fast response rate (with a growth
parameter value $a$ set to 0.37; see Equation \ref{eq:fast-cdf}) and
Panel B shows the probability density function that results from
computing the derivative of the fast response rate cumulative
distribution function with respect to $x$ (see Equation
\ref{eq:fast-pdf-function}). Panel C shows the cumulative distribution
function for the slow response rate (with a growth parameter value $a$
set to 0.15; see Equation \ref{eq:slow-cdf})) and Panel D shows the
probability density function that results from computing the derivative
of the slow response rate cumulative distribution function with respect
to $x$ (see Equation \ref{eq:slow-pdf-function} and section on [time
structuredness](#sec:time-structuredness) for more discussion). For the
fast response rate functions, an 80% response rate is obtained after
4.32 days or, equivalently, 80% of the area underneath the probability
density function is obtained at 4.32 days
($\int^{4.32}_{0} f_{fast}^\prime (x) = 0.80$; the integral from 0 to 4.32 of the probability density function for a fast response rate $f^\prime(x)_{fast}$ is 0.80). For the slow response
rate functions, an 80% response rate is obtained after 10.80 days or,
equivalently, 80% of the area underneath the probability density
function is obtained at 10.80 days
($\int^{10.80}_{0} f_{slow}^\prime (x) = 0.80$; the integral from 0 to 10.80 of the probability density function for a slow response rate $f^\prime(x)_{slow}$ is 0.80).

```{r pdf-time-structuredness, eval=F, include=F}
#1) Generate CDFs
day <- seq(from = 0, to = 36, by = 0.01)
M <- 1
satiation_value <- 0.8
satiation_point_fast <- 4.32
satiation_point_slow <- 10.80

a_fast <- log(1 - satiation_value)/-satiation_point_fast
a_slow <- log(1 - satiation_value)/-satiation_point_slow

#y data
y_fast <- M*(1 - exp(-a_fast*day))
y_slow <- M*(1 - exp(-a_slow*day))

#probability values
cdf_fast <- expression(M*(1 - exp(-a_fast*day)))
cdf_slow <- expression(M*(1 - exp(-a_slow*day)))

pdf_fast <- D(expr = cdf_fast, 'day')
pdf_slow <- D(expr = cdf_slow, 'day')

probability_values_fast<- eval(pdf_fast)
probability_values_slow <- eval(pdf_slow)


cdf_pdf_data <- data.frame('response_rate' = factor(c(rep('fast', times = length(y_fast)), 
                                           rep('slow', times = length(y_slow)))), 
                       'day' = rep(day, times = 2), 
                       'CDF' = c(y_fast, y_slow), 
                       'PDF' = c(probability_values_fast, probability_values_slow))

cdf_pdf_data_long <- cdf_pdf_data %>%
  pivot_longer(cols = c(CDF, PDF), names_to = 'prob_dist',
  names_ptypes = factor(levels = c('CDF', 'PDF'))) %>% 
  unite('dist_type', c('response_rate', 'prob_dist')) %>%
  mutate(dist_type = factor(dist_type, levels = c('fast_CDF', 'slow_CDF','fast_PDF', 
                                                   'slow_PDF')))

cdf_pdf_data_long$dist_type <- recode_factor(cdf_pdf_data_long$dist_type,   
                                             fast_CDF = 'bold(A:~CDF~(Fast~response~rate))', 
                                             slow_CDF = 'bold(C:~CDF~(Slow~response~rate))', 
                                             fast_PDF = 'bold(B:~PDF~(Fast~response~rate))', 
                                             slow_PDF = 'bold(D:~PDF~(Slow~response~rate))')
                
#lines showing 80% mark    
v_line_data <- data.frame(
  dist_type =c("bold(A:~CDF~(Fast~response~rate))", "bold(C:~CDF~(Slow~response~rate))"), 
  x = c(4.32, 10.80), 
  x_end = c(4.32, 10.80), 
  y = c(0.8, 0.8), 
  y_end = c(0, 0))

h_line_data <- data.frame(
  dist_type = c("bold(A:~CDF~(Fast~response~rate))", "bold(C:~CDF~(Slow~response~rate))"), 
  x = c(0, 0), 
  x_end = c(4.32, 10.80), 
  y = c(0.8, 0.8), 
  y_end = c(0.8, 0.8))

#needed for shading
pdf_shading_data <- cdf_pdf_data_long %>% 
  filter(str_detect(dist_type, pattern = 'bold\\(B') & day <= 4.32 | 
         str_detect(dist_type, pattern = 'bold\\(D') & day <= 10.80)

#needed for points 
point_data <- data.frame(
  dist_type =c(rep("bold(A:~CDF~(Fast~response~rate))", times = 1), 
               rep("bold(C:~CDF~(Slow~response~rate))", times = 1)),
  x = c(4.32, 10.80), 
  y = c(0.8, 0.8))

#arrows 
arrow_data <- data.frame(
  dist_type =c(rep("bold(A:~CDF~(Fast~response~rate))", times = 1), 
               rep("bold(C:~CDF~(Slow~response~rate))", times = 1)),
  xmin = c(4.32, 10.80), 
  xmax = c(10, 17), 
  ymin = c(0.8, 0.8), 
  ymax = c(0.25, 0.25))


#equations 
equation_data <- data.frame(
  dist_type =c(rep("bold(A:~CDF~(Fast~response~rate))", times = 4), 
               rep("bold(C:~CDF~(Slow~response~rate))", times = 4), 
               rep("bold(B:~PDF~(Fast~response~rate))", times = 3), 
               rep("bold(D:~PDF~(Slow~response~rate))", times = 3)),
  
  label = c("f[fast](x) == M(1 - e^{-a[fast]~x})", "a[fast] == 0.37", "M ==1", "0.80 == 1(1-e^{-0.37(4.32)})", 
            "f[slow](x) == M(1 - e^{-a[slow]~x})", "a[slow] == 0.15", "M == 1", "0.80 == 1(1-e^{-0.15(10.80)})",
            
            "f[fast]^{phantom() * minute }(x) * {phantom() == phantom()} * frac(partialdiff *f[fast](x),  partialdiff *x) * {phantom() == phantom()} * M(e^{a[fast]*x} * a[fast])",
            "integral(f[fast]^{phantom() * minute}, 0, 4.32)*(x) == f[fast](4.32) - f[fast](0)", "phantom() == 0.80", 
            
            "f[slow]^{phantom() * minute }(x) * {phantom() == phantom()} * frac(partialdiff *f[slow](x),  partialdiff *x) * {phantom() == phantom()} * M(e^{a[slow]*x} * a[slow])",
            "integral(f[slow]^{phantom() * minute}, 0, 10.80)*(x) == f[slow](10.80) - f[slow](0)", "phantom() == 0.80"), 
  x = c(18, 17, 18, 18, 
        24, 25, 24, 24, 
        22, 22, 20.5, 
        22, 22, 20.5),
  y = c(rep(c(0.8, 0.65, 0.50, 0.2), times = 2), 
        0.35, 0.15, 0.10, 
        0.35, 0.15, 0.10))


cdf_pdf_plot <- ggplot(cdf_pdf_data_long, aes(x = day, y = value)) + 
  geom_line(size = 1.5) + 
  scale_y_continuous(breaks = c(0, 0.25, 0.50, 0.80, 1.00)) +
  theme_classic(base_family = 'Helvetica') + 
  
  geom_area(data = pdf_shading_data, mapping = aes(x = day, y = value), 
                show.legend = 'bin',  fill="grey", alpha = 1, color = 'black', size = 1.5) +
  geom_text(data = equation_data, inherit.aes = F, mapping = aes(x = x, y = y, label = label), parse = T, size = 9) + 
  geom_point(data = point_data, inherit.aes = F, mapping = aes(x = x , y = y), size = 4) + 
  
  #arrows
  geom_segment(data = arrow_data, inherit.aes = F, mapping = aes(x = xmin, xend = xmax, y = ymin, yend = ymax), 
               arrow = arrow(length = unit(0.3, 'cm')), size = 1)  + 
  
    #vertical lines 
  geom_segment(data = v_line_data, mapping = aes(x = x, y = y, xend = x_end, yend = y_end), linetype = 2, size = 1) + 
  geom_segment(data = h_line_data, mapping = aes(x = x, y = y, xend = x_end, yend = y_end), linetype = 2, size = 1)  + 



  facet_wrap_custom( ~ dist_type, scales = "free", ncol = 2, nrow = 2 , dir = 'v',
                     labeller = label_parsed,  

                            scale_overrides = list(
                            scale_override(1,
                              scale_x_continuous(
                                breaks = c(0, 4.32, 18, 24, 36),
                                limits = c(0, 36))), 
                          
                            scale_override(which = 2,
                              scale_y_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4),
                                limits = c(0, 0.4))),
                             scale_override(which = 2,
                              scale_x_continuous(breaks = c(0, 4.32, 18, 24, 36),
                                limits = c(0, 36))),
                            
                            scale_override(which = 3,
                               scale_x_continuous(
                                breaks = c(0, 10.80, 18, 24, 36),
                                limits = c(0, 36))), 
                         
                            scale_override(4,
                              scale_x_continuous(
                                breaks = c(0, 10.80, 18, 24, 36),
                                limits = c(0, 36))), 
                            scale_override(which = 4,
                                scale_y_continuous(breaks = c(0, 0.1, 0.2, 0.3, 0.4),
                                limits = c(0, 0.4))))) +  


  labs( x = 'Response window day') + 
  
  theme(strip.text.x = element_text(face = 'bold', hjust = 0, size = 30, margin = unit(c(t = 0, r = 0, b = 1, l = 0), "cm")),
        strip.background = element_rect(fill = "white", color = "white"), 

        #axis details
        axis.text = element_text(size = 22, color = 'black'),
        axis.title = element_text(size = 28),
        axis.line = element_line(size = 1),
        axis.ticks.length.x = unit(x = 0.5, units = 'cm'), 
        axis.title.x = element_text(margin = unit(c(1, 0, 0, 0), "cm")),
        axis.ticks = element_line(size = 1, colour = 'black'),

      panel.spacing.y = unit(x = 2, units = 'cm'),
      panel.spacing.x = unit(x = 2, units = 'cm'))
       

g <- ggplotGrob(cdf_pdf_plot)

#customize y-axis label 
g$grobs[[28]]$children$GRID.text.24299$label <- paste("Density (probability, f'(x))", str_pad('', width = 13), "Response percentage (f(x))")
g$grobs[[28]]$children$GRID.text.24299$y <- grid::unit(0.52,"npc")
g$grobs[[28]]$children$GRID.text.24299$x <- grid::unit(-0.2,"npc")

plot_converted <- as_ggplot(g)

#create PDF of faceted plot
set_panel_size(p = plot_converted, height = unit(x = 32, units = 'cm'),
                 width = unit(x = 40, units = 'cm'),
                 file =  'Figures/cdf_pdf_plots.pdf')
```

```{=tex}
\begin{figure}[H]
  \caption{Cumulative Distribution Functions (CDF) and Probability Density Functions (PDF) for Fast and Slow Response Rates}
  \label{fig:cdf-pdf-plots}
  \includegraphics{Figures/cdf_pdf_plots} \hfill{}
  \caption*{Note. \textup{Panel A shows the cumulative distribution function for the fast response rate (with a growth parameter value $a$ set to 0.37; see Equation \ref{eq:fast-cdf}) and Panel B shows the probability density function that results from computing the derivative of the fast response rate cumulative distribution function with respect to $x$ (see Equation \ref{eq:fast-pdf-function}). Panel C shows the cumulative distribution function for the slow response rate (with a growth parameter value $a$ set to 0.15; see Equation \ref{eq:slow-cdf}) and Panel D shows the probability density function that results from computing the derivative of the slow response rate cumulative distribution function with respect to $x$ (see Equation \ref{eq:slow-pdf-function} and section \ref{sec:time-structuredness} for more discussion on time structuredness). For the fast response rate functions, an 80\% response rate is obtained after 4.32 days or, equivalently, 80\% of the area underneath the probability density function is obtained at 4.32 days ($\int^{4.32}_{0} f_{fast}^\prime (x) = 0.80$). For the slow response rate functions, an 80\% response rate is obtained after 10.80 days or, equivalently, 80\% of the area underneath the probability density function is obtained at 10.80 days ($\int^{10.80}_{0} f_{slow}^\prime (x) = 0.80$).}}
\end{figure}
```

Having computed probability density functions for fast and slow response rates, time delays could be generated to create time-unstructured data. To generate time-unstructured data for a person at a given time point, a time delay was first
generated by sampling values according to the probability density function defined by either a fast or slow response rate (Equations \ref{eq:fast-pdf-function}--\ref{eq:slow-pdf-function}). The sampled time delay was then added to the value of the current measurement day, with the combined measurement day then being plugged into the logistic function (Equation \ref{eq:logFunction-generation}) along with a set of person-specific parameter values to generate an observed score at a given time point for a given person. 

#### Constants 

Because the nature of change not manipulated in Experiment 3, I set it to have a constant value across all cells. To keep the nature of change constant across all cells, I set the fixed-effect days-to-halfway elevation parameter ($\upbeta_{fixed}$) to have a value of 180. Another variable set to a constant value across the cells was measurement spacing (equal spacing was used). 

#### Dependent Variables

##### Convergence Success Rate

The proportion of iterations in a cell where models converged defined
the **convergence success rate**.\footnote{Specifically, convergence was obtained if the convergence code returned by OpenMx was 0.} Equation \@ref(eq:convergence) below shows the calculation used to compute the convergence success rate:

```{=tex}
\begin{align}
  \text{Convergence success rate} =  \frac{\text{Number of models that successfully converged in a cell}}{n},
  (\#eq:convergence) 
\end{align}
```
\noindent where *n* represents the total number of models run in a cell.


##### Bias

Bias was calculated to evaluate the accuracy with which each logistic
function parameter was estimated. As shown below in Equation
\@ref(eq:bias), *bias* was obtained by calculating the difference
between the population value set for a parameter and the average
estimated value in each cell.

\useshortskip
```{=tex}
\begin{align}
  \text{Bias} =  \text{Population value for parameter} - \text{Average estimated value}
  (\#eq:bias) 
\end{align}
```

\noindent Bias was calculated for the fixed- and random-effect parameters of the baseline ($\uptheta_{fixed}$, $\uptheta_{random}$), maximal elevation ($\upalpha_{fixed}$, $\upalpha_{random}$), days-to-halfway elevation ($\upbeta_{fixed}$, $\upbeta_{random}$), and the halfway-triquarter delta parameters ($\upgamma_{fixed}$, $\upgamma_{random}$). 

##### Precision

In addition to computing bias, precision was calculated to evaluate the confidence with which each parameter was estimated in a given cell. *Precision* was obtained by computing the range of values covered by the middle 95% of values estimated for a logistic parameter in each cell. By using the middle 95% of estimated values, a plausible range of population estimates was obtained.   


## Overview of Data Generation and Analysis of Dependent Variables 

Data generation and analysis of the dependent variables was the same as in Experiment 1 (see [data generation and analysis](#data-generation-analysis) for discussion).  


## Results and Discussion

In the sections that follow, I organize the results by presenting them for each level of time structuredness (time-structured data, time-unstructured data [fast response rate], time-unstructured data [slow response rate]). Importantly, only the results for the day-unit parameters will be presented (i.e., fixed- and random-effect days-to-halfway elevation and halfway-triquarter delta parameters [$\upbeta_{fixed}$, $\upbeta_{random}$, $\upgamma_{fixed}$, $\upgamma_{random}$, respectively]). The results for the likert-unit parameters (i.e., fixed- and random-effect baseline and maximal elevation parameters [$\uptheta_{fixed}$, $\uptheta_{random}$, $\upalpha_{fixed}$, $\upalpha_{random}$, respectively]) were largely trivial and so are presented in [Appendix C](#appendix-c). 

For each level of time structuredness, I first provide a concise summary of the results and then provide a detailed report of the estimation accuracy of each day-unit parameter of the logistic function. Because the lengths of the detailed reports are considerable, I provide concise summaries before the detailed reports to establish a framework to interpret the detailed reports. The detailed report of each measurement spacing schedule will summarize the results of each day-unit's parameter estimation plot, report partial $\upomega^2$ values, and then provide a qualitative summary.

### Pre-Processing of Data and Model Convergence

After collecting the output from the simulations, non-converged models
(and their corresponding parameter estimates) were removed from
subsequent analyses. Table \ref{tab:conv-exp-3} in [Appendix B](#appendix-a-convergence-rates) provides the convergence
success rates for each cell in Experiment 3. Model convergence was almost always above 90% and convergence rates
rates below 90% only occurred in two cells with five measurements. 

### Time-Structured Data 

#### Concise Summary 

For time-structured data, Table \ref{tab:summary-table-time-struc-exp3} provides a concise summary of the results for the day-unit parameters (see Figure \ref{fig:exp3_plot_days_time_struc} for the corresponding parameter estimation plots). Text within the bias and precision columns indicates the number of measurements needed to achieve either low bias or high precision. Bolded text in the 'Low Bias' and 'Qualitative Summary' columns indicates the measurement number-sample size pairing(s) that, respectively, achieves low bias and the greatest improvements in bias and precision across all day-unit parameters. 

With respect to bias under time-structured data, instances of high bias only occur for the random-effect random-effect triquarter-halfway delta parameter ($\upgamma_{random}$). For the random-effect triquarter-halfway delta parameter ($\upgamma_{random}$), bias is low when using seven or more measurements with $N \ge 100$. Therefore, with time-structured data, low bias can be achieved in the estimation of all day-unit parameters using seven or more measurements with $N \ge 100$.

With respect to precision under time-structured data, a pattern different from that with bias occurs. For the fixed-effect days-to-halfway elevation parameter ($\upbeta_{fixed}$), precision is high across all cells. For the fixed-effect triquarter-halfway delta prameter ($\upgamma_{fixed}$), precision is high using either nine or more measurements with $N = 200$ or when using seven or more measurements with $N \ge 500$. For the random-effect day-unit parameters (random-effect days-to-halfway elevation parameter [$\upbeta_{random}$] and the random-effect triquarter-halfway elevation parameter [$\upgamma_{random}$]), precision is low in all cells. Therefore, with time-structured data, although the fixed-effect day-unit parameters can be estimated with high precisionnine or more measurements with $N = 200$ or when using seven or more measurements with $N \ge 500$, no measurement number-sample size pairing allows the random-effect day-unit parameters to be modelled with high precision.  

In summarizing the results for time-structured data, low bias is achieved in the estimation of all day-unit parameters using either seven or more measurements with $N = 100$ (see [bias](#bias-time-struc-exp3)). High precision is never achieved in the estimation of all day-unit parameters with any manipulated measurement number-sample size pairing (see [precision](#precision-time-struc-exp3)). Although it may be discouraging that no manipulated measurement number-sample size pairing under time-structured data achieves high precision in the estimation of all day-unit parameters, the largest improvements in bias and precision across all day-unit parameters are achieved with moderate measurement numbers and sample sizes. With time-structured data, the largest improvements in bias and precision in the estimation of all day-unit parameters are achieved using either seven measurements with $N \ge 200$ or nine measurements with $N \le 100$ (for discussion, see [qualitative summary](#qualitative-time-struc-exp3)). 

```{r summary-table-time-struc-exp3, echo=F}

errorbar_lengths_nm5_s30 <- compute_errorbar_lengths(exp_analytical_days = exp_3_analytical$days, iv_level = 'Time structured', num_measurements = 5, sample_size = 30)

errorbar_lengths_nm9_s30 <- compute_errorbar_lengths(exp_analytical_days = exp_3_analytical$days, iv_level = 'Time structured', num_measurements = 9, sample_size = 30)
errorbar_lengths_nm7_s30 <- compute_errorbar_lengths(exp_analytical_days = exp_3_analytical$days, iv_level = 'Time structured', num_measurements = 7, sample_size = 30)


errorbar_lengths <- c(paste(errorbar_lengths_nm5_s30$errorbar_length[1]),
                      paste(errorbar_lengths_nm9_s30$errorbar_length[2]),
                      paste(errorbar_lengths_nm7_s30$errorbar_length[3]), 
                      paste(errorbar_lengths_nm9_s30$errorbar_length[4]))
                  


summary_table <- data.frame('Parameter' = c('\\thead[lt]{$\\upbeta_{fixed}$ \\\\ (Figure \\ref{fig:exp3_plot_days_time_struc}A)}',
                                            '\\thead[lt]{$\\gamma_{fixed}$ \\\\ (Figure \\ref{fig:exp3_plot_days_time_struc}B)}', 
                                            '\\thead[lt]{$\\upbeta_{random}$ \\\\ (Figure \\ref{fig:exp3_plot_days_time_struc}C)}', 
                                            '\\thead[lt]{$\\upgamma_{random}$ \\\\ (Figure \\ref{fig:exp3_plot_days_time_struc}D)}'), 
                            
                            'Low Bias' = c('All cells', 
                                           'All cells except NM = 5 with \\textit{N} = 50', 
                                           'All cells', 
                                           '\\thead[lt]{\\textbf{NM $\\boldsymbol{\\ge}$ 9 with \\textit{N} $\\ge$ 100}}'),
                            
                            'High Precision' = c('All cells', 
                                            '\\thead[lt]{NM = 7 with \\textit{N} = 200 or \\\\ 
                                            NM = 9 with \\textit{N} $\\ge$ 500}', 
                                            'No cells',
                                            'No cells'), 
                            
                            'Qualitative Summary' = c('Low bias and high precision in all cells', 

                                                      '\\thead[lt]{Largest improvements in precision \\\\ 
                                                      using \\textbf{NM = 7 with \\textit{N} $\\ge$ 200} or \\\\
                                                      \\textbf{NM = 9 with \\textit{N} $\\le$ 100}}', 
                                                     
                                                      'Largest improvements in precision with NM = 7',
                                                     
                                                      '\\thead[lt]{Largest improvements in bias and \\\\
                                                      precision using NM = 7 with \\textit{N} $\\ge$ 100 or \\\\
                                                      NM = 9 with \\textit{N} $\\le$ 50}'),
                            'Error Bar Length' = errorbar_lengths,
                            
                            check.names = F)

kbl(x = summary_table, format = 'latex',
       longtable = T, booktabs = T, centering = T, escape = F,
       align = c('l', rep('l', times = ncol(summary_table) - 1)), 
    caption = 'Concise Summary of Results for Time-Structured Data in Experiment 3') %>%
    #header
   column_spec(column = 1, width = '2cm') %>%
  column_spec(column = 2, width = '5cm') %>%
  column_spec(column = 3, width = '4cm') %>%
  column_spec(column = 4, width = '6cm') %>%
  column_spec(column = 5, width = '3cm') %>%
add_header_above(header = c(' ' = 3, 'Summary' = 2)) %>%
  footnote(escape = F, threeparttable = T, general_title = '\\\\textit{Note.}\\\\hspace{-1.2pc}',
           general = "Bolded text in the `Low Bias' and `Qualitative Summary' columns indicates the measurement number-sample size pairing needed to, respectively, achieve low bias and the greatest improvements in bias and precision across all day-unit parameters (high precision not achieved in the estimation of all day-unit parameters with time-structured data). `Error Bar Length' indicates the longest error bar length that results from using the measurement number-sample size pairings in the `Qualitative Summary` column. Parameter names and population values are as follows: $\\\\upbeta_{fixed}$ = fixed-effect days-to-halfway elevation parameter = 180; $\\\\upgamma_{fixed}$ = fixed-effect halfway-triquarter delta parameter = 20; $\\\\upbeta_{random}$ = random-effect days-to-halfway elevation parameter = 10; $\\\\upgamma_{random}$ = random-effect halfway-triquarter delta parameter = 4.") %>%
  kable_styling(position = 'left') %>%
  landscape(margin = '2.54cm')
```

#### Detailed Report 

For time-structured data, Figure \ref{fig:exp3_plot_days_time_struc} and Table \ref{tab:omega-exp3-time-struc} show the results. Figure \ref{fig:exp3_plot_days_time_struc} shows the parameter estimation plots for each day-unit parameter and  Table \ref{tab:omega-exp3-time-struc} provides the partial $\upomega^2$ values for each independent variables of each day-unit parameter. In Figure \ref{fig:exp3_plot_days_time_struc}, error bars represent the middle 95% of estimated values, blue horizontal lines indicate the population values for each parameter (with population values of $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, and $\upgamma_{random}$ = 4.00), and gray bands specify the acceptable margins of error (i.e., 10% of the parameter's population value). I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20% of the parameter's population value as indicative of low-precision estimation. Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Note that random-effect parameter units are in standard deviation units.

##### Bias {#bias-time-struc-exp3}

For all simulations pertaining to time-structured data (see Figure \ref{fig:exp3_plot_days_time_struc}), instances of high bias occur in the estimation of the random-effect triquarter-halfway delta parameter ($\upgamma_{random}$; Figure \ref{fig:exp3_plot_days_time_struc}D). The gray bands indicate the $\pm 10\%$ margin of error. I classified dots that fell outside the gray band as biased and these dots remained unfilled.  Note that the gray 10% margin of error bands for the and random-effect triquarter-halfway delta parameter ($\upgamma_{random}$) is difficult to see because 10% of its population value is small relative to the range of the y-axis (i.e., 10% of 4.00 is 0.40, which is small relative to the y-axis range of 55).  

For the random-effect halfway-triquarter delta parameter ($\upgamma_{random}$; Figure \ref{fig:exp3_plot_days_time_struc}D), bias occurs on the five-measurements line (squares) with all manipulated sample sizes (shown on x-axis), on the seven-measurements line (circles) with all manipulated sample sizes, on the nine-measurements line (triangles) with sample sizes of 30 and 50, and on the eleven-measurements line (diamonds) with sample sizes of 30 and 50. Therefore, using time-structured data, the random-effect halfway-triquarter delta parameter ($\upgamma_{random}$)---along with all other day-unit parameters---can be estimated with low bias using nine or more measurements with $N \ge 100$. 


```{r plots-time-structured-exp3, include=F, eval=F}
generate_day_likert_facet_plot(analytical_data = exp_3_analytical, 
                               target_col = 'time_structuredness', target_value = 'Time structured',
                                                              x_axis_name = expression("Sample Size ("*italic(N)*")"), 

                               x_axis_var = 'sample_size', exp_num = 'exp3_', beta_lower = 160, beta_upper = 210,
                                beta_ticks = 5)
```

```{=tex}
\begin{figure}[H]
  \caption{Summary of Day-Unit Parameter Estimates for Time-Structured Data in Experiment 3}
  \label{fig:exp3_plot_days_time_struc}
  \includegraphics{Figures/exp3_plot_days_time structured} 
\end{figure}
\begin{figure}
 \caption*{Note. \textup{Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Blue horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, $\upgamma_{random}$ = 4.00. Gray bands indicate the $\pm 10\%$ margin of error for each parameter and unfilled dots indicate cells with average parameter estimates outside of the margin. Error bars represent the middle 95\% of estimated values, with light blue error bars indicating cells with variability greater than 20\% of the parameter's population value. I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20\% of the parameter's population value as indicative of low-precision estimation. Note that random-effect parameter units are in standard deviation units. See Table \ref{tab:exp3-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:omega-exp3-time-struc} for $\upomega^2$ effect size values.}}
\end{figure}
```

\newpage 
```{r omega-exp3-time-struc, echo=F}
print_bias_var_omega_table(exp_data = exp_3_raw, target_col = 'time_structuredness', target_value = 'time_structured', 
ind_vars = c('number_measurements', 'sample_size'), 
ind_var_acronyms = c('NM', 'S', 'NM x S'), 
caption = 'Partial $\\upomega^2$ Values for Manipulated Variables With Time-Structured Data in Experiment 3',
footnote = 'NM = number of measurements (5, 7, 9, 11), S = sample size (30, 50, 100, 200, 500, 100), NM x S = interaction between number of measurements and sample size.', 
parameter_labels = c('$\\upbeta_{fixed}$ (Figure \\ref{fig:exp3_plot_days_time_structured}A)',
                     '$\\upbeta_{random}$ (Figure \\ref{fig:exp3_plot_days_time_structured}B)',
                     '$\\upgamma_{fixed}$ (Figure \\ref{fig:exp3_plot_days_time_structured}C)',
                     '$\\upgamma_{random}$ (Figure \\ref{fig:exp3_plot_days_time_structured}D)'))

```

##### Precision {#precision-time-struc-exp3}

For all simulations pertaining to time-structured data (see Figure \ref{fig:exp3_plot_days_time_struc}), instances of low precision occur for all day-unit parameters except the fixed-effect days-to-halfway elevation parameter ($\upbeta_{fixed}$; Figure \ref{fig:exp3_plot_days_time_struc}A). I considered precision to be low if the length of an error bar covered a range of values larger than 20% of the parameter's population value. Error bars indicating low precision are coloured in light blue. 

For the fixed-effect halfway-triquarter delta parameter ($\upgamma_{fixed}$; Figure \ref{fig:exp3_plot_days_time_struc}C), error bar lengths are longer than the 20% acceptable amount using five measurements (squares) with all manipulated sample sizes (shown on x-axis), seven measurements (circles) with sample sizes of 30 to 200, nine measurements (triangles) with sample sizes of 30 to 100, and eleven measurements (diamonds) with sample sizes of 30 to 100. Therefore, using time-structured data, high precision can be achieved in the estimation of the fixed-effect triquarter-halfway elevation parameter ($\upgamma_{fixed}$) using seven or more measurements with $N \ge 500$ or using nine or more measurements with $N = 200$.

For the random-effect day-unit parameters (random-effect days-to-halfway elevation parameter [$\upbeta_{random}$] in Figure \ref{fig:exp3_plot_days_time_struc}B and the random-effect halfway-triquarter delta parameter [$\upgamma_{random}$] in Figure \ref{fig:exp3_plot_days_time_struc}D), error bar lengths are longer than the 20% acceptable amount in all the cells. Therefore, with time-structured data, precision is low for the estimation of the random-effect day-unit parameters across all the manipulated measurement number-sample size pairings. 

In summary, with time-structured data, high precision is achieved in the estimation of the fixed-effect day-unit parameters using seven or more measurements with $N \ge 500$ or using nine or more measurements with $N = 200$. For the random-effect day-unit parameters, no manipulated sample size-measurement number pairing achieves high precision. 


##### Qualitative Summary {#qualitative-time-struc-exp3}

For time-structured data in Figure \ref{fig:exp3_plot_days_time_struc}, although no manipulated measurement number-sample size pairing achieves high precision in the estimation of all day-unit parameters, the largest improvements in precision (and bias) are achieved using moderate sample sizes and measurements numbers. With respect to bias under time-structured data, the largest improvements in bias occur with the following measurement number-sample size pairings for the following day-unit parameter: 

* random-effect triquarter-halfway delta parameters  ($\upgamma_{random}$): nine measurements with $N \le 50$ or seven measurements with $N \ge 100$. 

\noindent With respect to precision under time-structured data, the largest improvements in precision in the estimation of all day-unit parameters (except the fixed-effect days-to-halfway elevation parameter [$\upbeta_{fixed}$]) are achieved with following measurement number-sample size pairings:

* fixed-effect triquarter-halfway delta parameter ($\upgamma_{fixed}$): seven measurements with $N \ge 200$ or nine measurements with $N \le 100$.
* random-effect days-to-halfway elevation parameter ($\upbeta_{random}$): seven measurements across all manipulated sample sizes.
* random-effect triquarter-halfway delta parameter ($\upgamma_{random}$):  seven measurements with $N \ge 100$ or nine measurements with $N \le 50$. 

For an applied researcher, one plausible question might center on what measurement number-sample size pairing(s) achieves the greatest improvements in bias and precision in the estimation of all day-unit parameters. To determine the measurement number-sample size pairing(s) that achieves the greatest improvements in bias and precision in the estimation of all day-unit parameters, it is important to realize, when looking across the measurement number-sample size pairings in the above lists, that only a certain range of sample sizes can be used with any given number of measurements. For example, if seven measurements are used, then the sample size must be at least 200 ($N \ge 200$) to achieve the greatest improvements in bias and precision in the estimation of all day-unit parameters. Therefore, for time-structured data, the measurement number-sample size pairings that achieve the greatest improvements in bias and precision in the estimation of all day-unit parameters are either seven measurements with $N \ge 200$ or nine measurements $N \le 100$. 



### Time-Unstructured Data (Fast Response)

#### Concise Summary 

For time-unstructured data characterized by a fast response rate, Table \ref{tab:summary-table-fast-exp3} provides a concise summary of the results for the day-unit parameters (see Figure \ref{fig:exp3_plot_days_fast} for the corresponding parameter estimation plots). Text within the bias and precision columns indicates the number of measurements needed to achieve either low bias or high precision. Bolded text in the 'Low Bias' and 'Qualitative Summary' columns indicates the measurement number-sample size pairing(s) that, respectively, achieves low bias and the greatest improvements in bias and precision across all day-unit parameters. 

With respect to bias under time-unstructured data characterized by a fast response rate, instances of high bias only occur for the random-effect random-effect triquarter-halfway delta parameter ($\upgamma_{random}$). For the random-effect triquarter-halfway delta parameter ($\upgamma_{random}$), bias is low when using seven or more measurements with $N \ge 100$. Therefore, with time-unstructured data characterized by a fast response rate, low bias can be achieved in the estimation of all day-unit parameters using seven or more measurements with $N \ge 100$.

With respect to precision under time-unstructured data characterized by a fast response rate, a pattern different from that with bias occurs. For the fixed-effect days-to-halfway elevation parameter ($\upbeta_{fixed}$), precision is high across all cells. For the fixed-effect triquarter-halfway delta prameter ($\upgamma_{fixed}$), precision is high using either nine or more measurements with $N = 200$ or when using seven or more measurements with $N \ge 500$. For the random-effect day-unit parameters (random-effect days-to-halfway elevation parameter [$\upbeta_{random}$] and the random-effect triquarter-halfway elevation parameter [$\upgamma_{random}$]), precision is low in all cells. Therefore, with time-unstructured data characterized by a fast response rate, although the fixed-effect day-unit parameters can be estimated with high precision nine or more measurements with $N = 200$ or when using seven or more measurements with $N \ge 500$, no measurement number-sample size pairing allows the random-effect day-unit parameters to be modelled with high precision.  

In summarizing the results for time-unstructured data characterized by a fast response rate, low bias is achieved in the estimation of all day-unit parameters using either seven or more measurements with $N = 100$ (see [bias](#bias-fast-exp3)). High precision is never achieved in the estimation of all day-unit parameters with any manipulated measurement number-sample size pairing (see [precision](#precision-fast-exp3)). Although it may be discouraging that no manipulated measurement number-sample size pairing under time-unstructured data characterized by a fast response rate achieves high precision in the estimation of all day-unit parameters, the largest improvements in bias and precision across all day-unit parameters are achieved with moderate measurement numbers and sample sizes. With time-unstructured data characterized by a fast response rate, the largest improvements in bias and precision in the estimation of all day-unit parameters are achieved using either seven measurements with $N \ge 200$ or nine measurements with $N \le 100$ (for discussion, see [qualitative summary](#qualitative-fast-exp3)). 

```{r summary-table-fast-exp3, echo=F}

errorbar_lengths_nm5_s30 <- compute_errorbar_lengths(exp_analytical_days = exp_3_analytical$days, iv_level = 'fast response', num_measurements = 5, sample_size = 30)

errorbar_lengths_nm9_s30 <- compute_errorbar_lengths(exp_analytical_days = exp_3_analytical$days, iv_level = 'fast response', num_measurements = 9, sample_size = 30)
errorbar_lengths_nm7_s30 <- compute_errorbar_lengths(exp_analytical_days = exp_3_analytical$days, iv_level = 'fast response', num_measurements = 7, sample_size = 30)


errorbar_lengths <- c(paste(errorbar_lengths_nm5_s30$errorbar_length[1]), 
                      paste(errorbar_lengths_nm9_s30$errorbar_length[2]), 
                      paste(errorbar_lengths_nm7_s30$errorbar_length[3]), 
                      paste(errorbar_lengths_nm9_s30$errorbar_length[4]))
                    
summary_table <- data.frame('Parameter' = c('\\thead[lt]{$\\upbeta_{fixed}$ \\\\ (Figure \\ref{fig:exp3_plot_days_fast}A)}',
                                            '\\thead[lt]{$\\gamma_{fixed}$ \\\\  (Figure \\ref{fig:exp3_plot_days_fast}B)}', 
                                            '\\thead[lt]{$\\upbeta_{random}$ \\\\ (Figure \\ref{fig:exp3_plot_days_fast}C)}', 
                                            '\\thead[lt]{$\\upgamma_{random}$ \\\\ (Figure \\ref{fig:exp3_plot_days_fast}D)}'), 
                            
                            'Low Bias' = c('All cells', 
                                           'All cells except NM = 5 with \\textit{N}= 50', 
                                           'All cells', 
                                          '\\thead[lt]{\\textbf{NM = 7 with \\textit{N} = 1000} or \\\\ 
                                            \\textbf{NM = 9 with \\textit{N} $\\in$ \\{200, 500\\}} or \\\\
                                            \\textbf{NM = 11 with \\textit{N} = 1000}}'),
                            
                            'High Precision' = c('All cells', 
                                            '\\thead[lt]{NM = 7 with \\textit{N} $\\ge$ 500 or \\\\ 
                                            NM = 9 with \\textit{N} = 200}', 
                                     
                                            'No cells',
                                            'No cells'), 
                            
                            'Qualitative Summary' = c('Low bias and high precision in all cells', 

                                                      '\\thead[lt]{Largest improvements in precision \\\\ 
                                                      using \\textbf{NM = 7 with \\textit{N} $\\ge$ 200} or \\\\
                                                      \\textbf{NM = 9 with \\textit{N} $\\le$ 100}}', 
                                                     
                                                      'Largest improvements in precision with NM = 7',
                                                     
                                                      '\\thead[lt]{Largest improvements in bias and \\\\
                                                      precision using NM = 7 with \\textit{N} $\\ge$ 100 \\\\
                                                      or NM = 9 with \\textit{N} $\\le$ 50}'),
                            'Error Bar Length' = errorbar_lengths,
                            
                          
                            check.names = F)

kbl(x = summary_table, format = 'latex',
       longtable = T, booktabs = T, centering = T, escape = F,
       align = c('l', rep('l', times = ncol(summary_table) - 1)), 
    caption = 'Concise Summary of Results for Time-Unstructured Data (Fast Response Rate) in Experiment 3') %>%
  #header
   column_spec(column = 1, width = '2cm') %>%
  column_spec(column = 2, width = '5cm') %>%
  column_spec(column = 3, width = '4cm') %>%
  column_spec(column = 4, width = '6cm') %>%
  column_spec(column = 5, width = '3cm') %>%
add_header_above(header = c(' ' = 3, 'Summary' = 2)) %>%
  footnote(escape = F, threeparttable = T, general_title = '\\\\textit{Note.}\\\\hspace{-1.1pc}',
           general = "Bolded text in the `Low Bias' and `Qualitative Summary' columns indicates the measurement number-sample size pairing needed to, respectively, achieve low bias and the greatest improvements in bias and precision across all day-unit parameters (high precision not achieved in the estimation of all day-unit parameters with time-unstructured data characterized by a fast response rate). `Error Bar Length' indicates the longest error bar length that results from using the measurement number-sample size pairings in the `Qualitative Summary` column. Parameter names and population values are as follows: $\\\\upbeta_{fixed}$ = fixed-effect days-to-halfway elevation parameter = 180; $\\\\upgamma_{fixed}$ = fixed-effect halfway-triquarter delta parameter = 20; $\\\\upbeta_{random}$ = random-effect days-to-halfway elevation parameter = 10; $\\\\upgamma_{random}$ = random-effect halfway-triquarter delta parameter = 4.") %>%
  kable_styling(position = 'left') %>%
  landscape(margin = '2.54cm')

```


#### Detailed Report 

For time-unstructured data characterized by a fast response rate, Figure \ref{fig:exp3_plot_days_fast} and Table \ref{tab:omega-exp3-slow} show the results. Figure \ref{fig:exp3_plot_days_fast} shows the parameter estimation plots for each day-unit parameter and  Table \ref{tab:omega-exp3-slow} provides the partial $\upomega^2$ values for each independent variables of each day-unit parameter. In Figure \ref{fig:exp3_plot_days_fast}, error bars represent the middle 95% of estimated values, blue horizontal lines indicate the population values for each parameter (with population values of $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, and $\upgamma_{random}$ = 4.00), and gray bands specify the acceptable margins of error (i.e., 10% of the parameter's population value). I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20% of the parameter's population value as indicative of low-precision estimation. Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Note that random-effect parameter units are in standard deviation units.

##### Bias {#bias-fast-exp3}

For all simulations pertaining to time-unstructured data characterized by a fast response rate (see Figure \ref{fig:exp3_plot_days_fast}), instances of high bias occur in the estimation of the random-effect triquarter-halfway delta parameter ($\upgamma_{random}$; Figure \ref{fig:exp3_plot_days_time_struc}D). The gray bands indicate the $\pm 10\%$ margin of error. I classified dots that fell outside the gray band as biased and these dots remained unfilled.  Note that the gray 10% margin of error bands for the and random-effect triquarter-halfway delta parameter ($\upgamma_{random}$) is difficult to see because 10% of its population value is small relative to the range of the y-axis (i.e., 10% of 4.00 is 0.40, which is small relative to the y-axis range of 55).  

For the random-effect halfway-triquarter delta parameter ($\upgamma_{random}$; Figure \ref{fig:exp3_plot_days_fast}D), bias occurs on the five-measurements line (squares) with all manipulated sample sizes (shown on x-axis), on the seven-measurements line (circles) with all manipulated sample sizes, on the nine-measurements line (triangles) with sample sizes of 30 and 50, and on the eleven-measurements line (diamonds) with sample sizes of 30 and 50. Therefore, using time-unstructured data characterized by a fast response rate, the random-effect halfway-triquarter delta parameter ($\upgamma_{random}$)---along with all other day-unit parameters---can be estimated with low bias using nine or more measurements with $N \ge 100$. 


```{r plots-fast-response-exp3, include=F, eval=F}
generate_day_likert_facet_plot(analytical_data = exp_3_analytical, 
                               target_col = 'time_structuredness', target_value = 'Time unstructured (fast response)',
                              x_axis_name = expression("Sample Size ("*italic(N)*")"), 
                               x_axis_var = 'sample_size', exp_num = 'exp3_', beta_lower = 160, beta_upper = 210,
                                 beta_ticks = 5)
```

```{=tex}
\begin{figure}[H]
  \caption{Summary of Day-Unit Parameter Estimates for Time-Unstructured Data (Fast Response Rate) in Experiment 3}
  \label{fig:exp3_plot_days_fast}
  \includegraphics{Figures/exp3_plot_days_time unstructured (fast response)} 
\end{figure}
\begin{figure}
  \caption*{Note. \textup{Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Blue horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, $\upgamma_{random}$ = 4.00. Gray bands indicate the $\pm 10\%$ margin of error for each parameter and unfilled dots indicate cells with average parameter estimates outside of the margin. Error bars represent the middle 95\% of estimated values, with light blue error bars indicating cells with variability greater than 20\% of the parameter's population value. I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20\% of the parameter's population value as indicative of low-precision estimation. See Table \ref{tab:exp3-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:omega-exp3-fast} for $\upomega^2$ effect size values.}}
\end{figure}
```

\newpage 
```{r omega-exp3-fast, echo=F}
print_bias_var_omega_table(exp_data = exp_3_raw, target_col = 'time_structuredness', target_value = 'fast_response', 
ind_vars = c('number_measurements', 'sample_size'), 
ind_var_acronyms = c('NM', 'S', 'NM x S'), 
caption = 'Partial $\\upomega^2$ Values for Manipulated Variables With Time-Structured Data in Experiment 3',
footnote = 'NM = number of measurements (5, 7, 9, 11), S = sample size (30, 50, 100, 200, 500, 100), NM x S = interaction between number of measurements and sample size.', 
parameter_labels = c('$\\upbeta_{fixed}$ (Figure \\ref{fig:exp3_plot_days_fast}A)',
                     '$\\upbeta_{random}$ (Figure \\ref{fig:exp3_plot_days_fast}B)',
                     '$\\upgamma_{fixed}$ (Figure \\ref{fig:exp3_plot_days_fast}C)',
                     '$\\upgamma_{random}$ (Figure \\ref{fig:exp3_plot_days_fast}D)'))

```

##### Precision {#precision-fast-exp3}

For all simulations pertaining to time-unstructured data characterized by a fast response rate (see Figure \ref{fig:exp3_plot_days_fast}), instances of low precision occur for all day-unit parameters except the fixed-effect days-to-halfway elevation parameter ($\upbeta_{fixed}$; Figure \ref{fig:exp3_plot_days_time_struc}A). I considered precision to be low if the length of an error bar covered a range of values larger than 20% of the parameter's population value. Error bars indicating low precision are coloured in light blue. 

For the fixed-effect halfway-triquarter delta parameter ($\upgamma_{fixed}$; Figure \ref{fig:exp3_plot_days_fast}C), error bar lengths are longer than the 20% acceptable amount using five measurements (squares) with all manipulated sample sizes (shown on x-axis), seven measurements (circles) with sample sizes of 30 to 200, nine measurements (triangles) with sample sizes of 30 to 100, and eleven measurements (diamonds) with sample sizes of 30 to 100. Therefore, using time-unstructured data characterized by a fast response rate, high precision can be achieved in the estimation of the fixed-effect triquarter-halfway elevation parameter ($\upgamma_{fixed}$) using seven or more measurements with $N \ge 500$ or using nine or more measurements with $N = 200$.

For the random-effect day-unit parameters (random-effect days-to-halfway elevation parameter [$\upbeta_{random}$] in Figure \ref{fig:exp3_plot_days_fast}B and the random-effect halfway-triquarter delta parameter [$\upgamma_{random}$] in Figure \ref{fig:exp3_plot_days_fast}D), error bar lengths are longer than the 20% acceptable amount in all the cells. Therefore, with time-unstructured data characterized by a fast response rate, precision is low for the estimation of the random-effect day-unit parameters across all the manipulated measurement number-sample size pairings. 

In summary, with time-unstructured data characterized by a fast response rate, high precision is achieved in the estimation of the fixed-effect day-unit parameters using seven or more measurements with $N \ge 500$ or using nine or more measurements with $N = 200$. For the random-effect day-unit parameters, no manipulated sample size-measurement number pairing achieves high precision. 


##### Qualitative Summary {#qualitative-fast-exp3}

For time-unstructured data characterized by a fast response rate in Figure \ref{fig:exp3_plot_days_fast}, although no manipulated measurement number-sample size pairing achieves high precision in the estimation of all day-unit parameters, the largest improvements in precision (and bias) are achieved using moderate sample sizes and measurements numbers. With respect to bias under time-unstructured data characterized by a fast response rate, the largest improvements in bias occur with the following measurement number-sample size pairings for the following day-unit parameter: 

* random-effect triquarter-halfway delta parameters  ($\upgamma_{random}$): nine measurements with $N \le 50$ or seven measurements with $N \ge 100$. 

\noindent With respect to precision under time-unstructured data characterized by a fast response rate, the largest improvements in precision in the estimation of all day-unit parameters (except the fixed-effect days-to-halfway elevation parameter [$\upbeta_{fixed}$]) are achieved with following measurement number-sample size pairings:

* fixed-effect triquarter-halfway delta parameter ($\upgamma_{fixed}$): seven measurements with $N \ge 200$ or nine measurements with $N \le 100$.
* random-effect days-to-halfway elevation parameter ($\upbeta_{random}$): seven measurements across all manipulated sample sizes.
* random-effect triquarter-halfway delta parameter ($\upgamma_{random}$):  seven measurements with $N \ge 100$ or nine measurements with $N \le 50$. 

For an applied researcher, one plausible question might center on what measurement number-sample size pairing(s) achieves the greatest improvements in bias and precision in the estimation of all day-unit parameters. To determine the measurement number-sample size pairing(s) that achieves the greatest improvements in bias and precision in the estimation of all day-unit parameters, it is important to realize, when looking across the measurement number-sample size pairings in the above lists, that only a certain range of sample sizes can be used with any given number of measurements. For example, if seven measurements are used, then the sample size must be at least 200 ($N \ge 200$) to achieve the greatest improvements in bias and precision in the estimation of all day-unit parameters. Therefore, for time-unstructured data characterized by a fast response rate, the measurement number-sample size pairings that achieve the greatest improvements in bias and precision in the estimation of all day-unit parameters are either seven measurements with $N \ge 200$ or nine measurements $N \le 100$. 



### Time-Unstructured Data (Slow Response)

#### Concise Summary 

For time-unstructured data characterized by a slow response rate, Table \ref{tab:summary-table-slow-exp3} provides a concise summary of the results for the day-unit parameters (see Figure \ref{fig:exp3_plot_days_slow} for the corresponding parameter estimation plots). Text within the bias and precision columns indicates the number of measurements needed to achieve either low bias or high precision. Bolded text in the 'Low Bias' and 'Qualitative Summary' columns indicates the measurement number-sample size pairing(s) that, respectively, achieves low bias and the greatest improvements in bias and precision across all day-unit parameters. 

With respect to bias under time-unstructured data characterized by a slow response rate, instances of high bias only occur for the random-effect random-effect triquarter-halfway delta parameter ($\upgamma_{random}$). For the random-effect triquarter-halfway delta parameter ($\upgamma_{random}$), bias is low when using seven or more measurements with $N \ge 100$. Therefore, with time-unstructured data characterized by a slow response rate, low bias can be achieved in the estimation of all day-unit parameters using seven or more measurements with $N \ge 100$.

With respect to precision under time-unstructured data characterized by a slow response rate, a pattern different from that with bias occurs. For the fixed-effect days-to-halfway elevation parameter ($\upbeta_{fixed}$), precision is high across all cells. For the fixed-effect triquarter-halfway delta prameter ($\upgamma_{fixed}$), precision is high using either nine or more measurements with $N = 200$ or when using seven or more measurements with $N \ge 500$. For the random-effect day-unit parameters (random-effect days-to-halfway elevation parameter [$\upbeta_{random}$] and the random-effect triquarter-halfway elevation parameter [$\upgamma_{random}$]), precision is low in all cells. Therefore, with time-unstructured data characterized by a slow response rate, although the fixed-effect day-unit parameters can be estimated with high precision nine or more measurements with $N = 200$ or when using seven or more measurements with $N \ge 500$, no measurement number-sample size pairing allows the random-effect day-unit parameters to be modelled with high precision.  

In summarizing the results for time-unstructured data characterized by a slow response rate, low bias is achieved in the estimation of all day-unit parameters using either seven or more measurements with $N = 100$ (see [bias](#bias-slow-exp3)). High precision is never achieved in the estimation of all day-unit parameters with any manipulated measurement number-sample size pairing (see [precision](#precision-slow-exp3)). Although it may be discouraging that no manipulated measurement number-sample size pairing under time-unstructured data characterized by a slow response rate achieves high precision in the estimation of all day-unit parameters, the largest improvements in bias and precision across all day-unit parameters are achieved with moderate measurement numbers and sample sizes. With time-unstructured data characterized by a slow response rate, the largest improvements in bias and precision in the estimation of all day-unit parameters are achieved using either seven measurements with $N \ge 200$ or nine measurements with $N \le 100$ (for discussion, see [qualitative summary](#qualitative-slow-exp3)). 

```{r summary-table-slow-exp3, echo=F}
errorbar_lengths_nm5_s30 <- compute_errorbar_lengths(exp_analytical_days = exp_3_analytical$days, iv_level = 'slow response', num_measurements = 5, sample_size = 30)

errorbar_lengths_nm9_s30 <- compute_errorbar_lengths(exp_analytical_days = exp_3_analytical$days, iv_level = 'slow response', num_measurements = 9, sample_size = 30)
errorbar_lengths_nm7_s30 <- compute_errorbar_lengths(exp_analytical_days = exp_3_analytical$days, iv_level = 'slow response', num_measurements = 7, sample_size = 30)


errorbar_lengths <- c(paste(errorbar_lengths_nm5_s30$errorbar_length[1]), 
                      paste(errorbar_lengths_nm9_s30$errorbar_length[2]), 
                      paste(errorbar_lengths_nm7_s30$errorbar_length[3]), 
                      paste(errorbar_lengths_nm9_s30$errorbar_length[4]))

summary_table <- data.frame('Parameter' = c('\\thead[lt]{$\\upbeta_{fixed}$ \\\\ (Figure \\ref{fig:exp3_plot_days_slow}A)}',
                                            '\\thead[lt]{$\\gamma_{fixed}$ \\\\ (Figure \\ref{fig:exp3_plot_days_slow}B)}', 
                                            '\\thead[lt]{$\\upbeta_{random}$ \\\\ (Figure \\ref{fig:exp3_plot_days_slow}C)}', 
                                            '\\thead[lt]{$\\upgamma_{random}$ \\\\ (Figure \\ref{fig:exp3_plot_days_slow}D)}'), 
                            
                            'Low Bias' = c('All cells', 
                                           'All cells except NM = 5 with \\textit{N} = 50', 
                                           'No cells except NM = 5 with \\textit{N} = 30 and NM = 11 with \\textit{N} $\\in$ \\{30, 50\\}', 
                                           'No cells'),
                            
                            'High Precision' = c('All cells', 
                                            '\\thead[lt]{NM = 7 with \\textit{N} = 200 or \\\\ 
                                            NM = 9 with \\textit{N} $\\le$ 500}', 
                                            'No cells',
                                            'No cells'), 
                            
                            'Qualitative Summary' = c('Low bias and high precision in all cells', 

                                                      '\\thead[lt]{Largest improvements in precision \\\\ 
                                                      using \\textbf{NM = 7 with \\textit{N} $\\ge$ 200} or \\\\
                                                      \\textbf{NM = 9 with \\textit{N} $\\le$ 100}}', 
                                                     
                                                      'Largest improvements in precision with NM = 7',
                                                     
                                                      '\\thead[lt]{Largest improvements in bias and \\\\
                                                      precision using NM = 7 with \\textit{N} $\\boldsymbol{\\ge}$ 100 or \\\\
                                                      M = 9 with \\textit{N} $\\boldsymbol{\\le}$ 50}'),
                            'Error Bar Length' = errorbar_lengths,
                            
                            check.names = F)

kbl(x = summary_table, format = 'latex',
       longtable = T, booktabs = T, centering = T, escape = F,
       align = c('l', rep('l', times = ncol(summary_table) - 1)),
    caption = 'Concise Summary of Results for Time-Unstructured Data (Slow Response Rate) in Experiment 3') %>%
   #header
   column_spec(column = 1, width = '2cm') %>%
  column_spec(column = 2, width = '5cm') %>%
  column_spec(column = 3, width = '4cm') %>%
  column_spec(column = 4, width = '6.5cm') %>%
  column_spec(column = 5, width = '2.5cm') %>%
add_header_above(header = c(' ' = 3, 'Summary' = 2)) %>%
   footnote(escape = F, threeparttable = T, general_title = '\\\\textit{Note.}\\\\hspace{-1.1pc}',
           general = "Bolded text in the `Low Bias' and `Qualitative Summary' columns indicates the measurement number-sample size pairing needed to, respectively, achieve low bias and the greatest improvements in bias and precision across all day-unit parameters (high precision not achieved in the estimation of all day-unit parameters with time-unstructured data characterized by a slow response rate). `Error Bar Length' indicates the longest error bar length that results from using the measurement number-sample size pairings in the `Qualitative Summary` column. Parameter names and population values are as follows: $\\\\upbeta_{fixed}$ = fixed-effect days-to-halfway elevation parameter = 180; $\\\\upgamma_{fixed}$ = fixed-effect halfway-\\\\newline triquarter delta parameter = 20; $\\\\upbeta_{random}$ = random-effect days-to-halfway elevation parameter = 10; $\\\\upgamma_{random}$ = random-effect halfway-triquarter delta parameter = 4.") %>%
  kable_styling(position = 'left') %>%
  kable_styling(position = 'left') %>%
  landscape(margin = '2.54cm')
```


#### Detailed Report 

For time-unstructured data characterized by a slow response rate, Figure \ref{fig:exp3_plot_days_slow} and Table \ref{tab:omega-exp3-slow} show the results. Figure \ref{fig:exp3_plot_days_slow} shows the parameter estimation plots for each day-unit parameter and  Table \ref{tab:omega-exp3-slow} provides the partial $\upomega^2$ values for each independent variables of each day-unit parameter. In Figure \ref{fig:exp3_plot_days_slow}, error bars represent the middle 95% of estimated values, blue horizontal lines indicate the population values for each parameter (with population values of $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, and $\upgamma_{random}$ = 4.00), and gray bands specify the acceptable margins of error (i.e., 10% of the parameter's population value). I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20% of the parameter's population value as indicative of low-precision estimation. Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Note that random-effect parameter units are in standard deviation units.

##### Bias {#bias-slow-exp3}

For all simulations pertaining to time-unstructured data characterized by a slow response rate (see Figure \ref{fig:exp3_plot_days_slow}), instances of low high occur in the estimation of all day-unit parameters except the fixed-effect days-to-halfway elevation parameter ($\upbeta_{fixed}$; Figure \ref{fig:exp3_plot_days_slow}). The gray bands indicate the $\pm 10\%$ margin of error. I classified dots that fell outside the gray band as biased and these dots remained unfilled.  Note that the gray 10% margin of error bands for the random-effect day-unit parameters are difficult to see because 10% of their population values are small relative to the range of the y-axis (i.e., 10% of 10.00 is 1.00 and 10% of 4.00 is 0.40, which are small relative to the y-axis range of 55). 

For the fixed-effect halfway-triquarter delta parameter ($\upgamma_{fixed}$; Figure \ref{fig:exp3_plot_days_slow}B), bias only occurs on the five-measurements line (squares) with a $N = 30$ (shown on x-axis), Therefore, using time-unstructured data characterized by a slow response rate, the fixed-effect halfway-triquarter delta parameter ($\upgamma_{fixed}$) can be estimated with low bias with any measurement number-sample size pairing other than five measurements with $N = 30$. 

For the random-effect days-to-halfway elevation parameter ($\upbeta_{random}$; Figure \ref{fig:exp3_plot_days_slow}D), bias occurs across all manipulated measurement number-sample size pairings except five measurements with $N =50$ and 11 measurements with $N = \{30, 50\}$. Therefore, using time-unstructured data characterized by a slow response rate, the random-effect halfway-triquarter delta parameter ($\upgamma_{random}$) can be estimated with low bias using five measurements with $N =50$ and 11 measurements with $N = \{30, 50\}$.

For the random-effect halfway-triquarter delta parameter ($\upgamma_{random}$; Figure \ref{fig:exp3_plot_days_slow}D), bias is low for all measurement number-sample size pairings. Therefore, using time-unstructured data characterized by a slow response rate, the random-effect halfway-triquarter delta parameter ($\upgamma_{random}$) cannot be estimated with low bias with any manipulated sample size-measurement number pairing. 

In summary, using time-unstructured data characterized by a slow response rate, all manipulated measurement number-sample size achieve low bias in the estimation of the fixed-effect day-unit parameters. For the random-effect day-unit parameters, low bias can only be achieved in the estimation of the random-effect days-to-halfway elevation parameter ($\upbeta_{random}$) using five measurements with $N =50$ or 11 measurements with $N = \{30, 50\}$. The random-effect halfway-triquarter delta parameter ($\upgamma_{random}$) cannot be estimated with low bias with any manipulated sample size-measurement number pairing. 


```{r plots-slow-response-exp3, include=F, eval=F}
generate_day_likert_facet_plot(analytical_data = exp_3_analytical, 
                               target_col = 'time_structuredness', target_value = 'Time unstructured (slow response)',
                              x_axis_name = expression("Sample Size ("*italic(N)*")"), 
                               x_axis_var = 'sample_size', exp_num = 'exp3_', beta_lower = 160, beta_upper = 210,
                                 beta_ticks = 5)
```

```{=tex}
\begin{figure}[H]
  \caption{Summary of Day-Unit Parameter Estimates for Time-Unstructured Data (Slow Response Rate) in Experiment 3}
  \label{fig:exp3_plot_days_slow}
  \includegraphics{Figures/exp3_plot_days_time unstructured (slow response)} 
\end{figure}
\begin{figure}
  \caption*{Note. \textup{Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Blue horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, $\upgamma_{random}$ = 4.00. Gray bands indicate the $\pm 10\%$ margin of error for each parameter and unfilled dots indicate cells with average parameter estimates outside of the margin. Error bars represent the middle 95\% of estimated values, with light blue error bars indicating cells with variability greater than 20\% of the parameter's population value. I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20\% of the parameter's population value as indicative of low-precision estimation. See Table \ref{tab:exp3-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:omega-exp3-slow} for $\upomega^2$ effect size values.}}
\end{figure}
```

\newpage 
```{r omega-exp3-slow, echo=F}
print_bias_var_omega_table(exp_data = exp_3_raw, target_col = 'time_structuredness', target_value = 'fast_response', 
ind_vars = c('number_measurements', 'sample_size'), 
ind_var_acronyms = c('NM', 'S', 'NM x S'), 
caption = 'Partial $\\upomega^2$ Values for Manipulated Variables With Time-Structured Data in Experiment 3',
footnote = 'NM = number of measurements (5, 7, 9, 11), S = sample size (30, 50, 100, 200, 500, 100), NM x S = interaction between number of measurements and sample size.', 
parameter_labels = c('$\\upbeta_{fixed}$ (Figure \\ref{fig:exp3_plot_days_fast}A)',
                     '$\\upbeta_{random}$ (Figure \\ref{fig:exp3_plot_days_fast}B)',
                     '$\\upgamma_{fixed}$ (Figure \\ref{fig:exp3_plot_days_fast}C)',
                     '$\\upgamma_{random}$ (Figure \\ref{fig:exp3_plot_days_fast}D)'))

```

##### Precision {#precision-slow-exp3}

For all simulations pertaining to time-unstructured data characterized by a slow response rate (see Figure \ref{fig:exp3_plot_days_slow}), instances of low precision occur for all day-unit parameters except the fixed-effect days-to-halfway elevation parameter ($\upbeta_{fixed}$; Figure \ref{fig:exp3_plot_days_time_struc}A). I considered precision to be low if the length of an error bar covered a range of values larger than 20% of the parameter's population value. Error bars indicating low precision are coloured in light blue. 

For the fixed-effect halfway-triquarter delta parameter ($\upgamma_{fixed}$; Figure \ref{fig:exp3_plot_days_slow}C), error bar lengths are longer than the 20% acceptable amount using five measurements (squares) with all manipulated sample sizes (shown on x-axis), seven measurements (circles) with sample sizes of 30 to 200, nine measurements (triangles) with sample sizes of 30 to 100, and eleven measurements (diamonds) with sample sizes of 30 to 100. Therefore, using time-unstructured data characterized by a slow response rate, high precision can be achieved in the estimation of the fixed-effect triquarter-halfway elevation parameter ($\upgamma_{fixed}$) using seven or more measurements with $N \ge 500$ or using nine or more measurements with $N = 200$.

For the random-effect day-unit parameters (random-effect days-to-halfway elevation parameter [$\upbeta_{random}$] in Figure \ref{fig:exp3_plot_days_slow}B and the random-effect halfway-triquarter delta parameter [$\upgamma_{random}$] in Figure \ref{fig:exp3_plot_days_slow}D), error bar lengths are longer than the 20% acceptable amount in all the cells. Therefore, with time-unstructured data characterized by a slow response rate, precision is low for the estimation of the random-effect day-unit parameters across all the manipulated measurement number-sample size pairings. 

In summary, with time-unstructured data characterized by a slow response rate, high precision is achieved in the estimation of the fixed-effect day-unit parameters using seven or more measurements with $N \ge 500$ or using nine or more measurements with $N = 200$. For the random-effect day-unit parameters, no manipulated sample size-measurement number pairing achieves high precision. 


##### Qualitative Summary {#qualitative-slow-exp3}

For time-unstructured data characterized by a slow response rate in Figure \ref{fig:exp3_plot_days_slow}, although no manipulated measurement number-sample size pairing achieves low bias and high precision in the estimation of all day-unit parameters, the largest improvements in bias and precision are achieved using moderate sample sizes and measurements numbers. With respect to bias under time-unstructured data characterized by a slow response rate, the largest improvements in bias occur with the following measurement number-sample size pairings for the following day-unit parameter: 


* random-effect days-to-halfway elevation parameter ($\upbeta_{random}$): seven measurements across all manipulated sample sizes.
* random-effect triquarter-halfway delta parameters  ($\upgamma_{random}$): nine measurements with $N \le 50$ or seven measurements with $N \ge 100$. 

\noindent With respect to precision under time-unstructured data characterized by a slow response rate, the largest improvements in precision in the estimation of all day-unit parameters (except the fixed-effect days-to-halfway elevation parameter [$\upbeta_{fixed}$]) are achieved with following measurement number-sample size pairings:

* fixed-effect triquarter-halfway delta parameter ($\upgamma_{fixed}$): seven measurements with $N \ge 200$ or nine measurements with $N \le 100$.
* random-effect days-to-halfway elevation parameter ($\upbeta_{random}$): seven measurements across all manipulated sample sizes.
* random-effect triquarter-halfway delta parameter ($\upgamma_{random}$):  seven measurements with $N \ge 100$ or nine measurements with $N \le 50$. 
For an applied researcher, one plausible question might center on what measurement number-sample size pairing(s) achieves the greatest improvements in bias and precision in the estimation of all day-unit parameters. To determine the measurement number-sample size pairing(s) that achieves the greatest improvements in bias and precision in the estimation of all day-unit parameters, it is important to realize, when looking across the measurement number-sample size pairings in the above lists, that only a certain range of sample sizes can be used with any given number of measurements. For example, if seven measurements are used, then the sample size must be at least 200 ($N \ge 200$) to achieve the greatest improvements in bias and precision in the estimation of all day-unit parameters. Therefore, for time-unstructured data characterized by a slow response rate, the measurement number-sample size pairings that achieve the greatest improvements in bias and precision in the estimation of all day-unit parameters are either seven measurements with $N \ge 200$ or nine measurements $N \le 100$. 



# References

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```

