---
title: "other"
output: pdf_document
---
## Post-processing of data

After the simulations were completed, outliers were removed so that
irregularities did not exist in patterns of variability. For example,
Figure \ref{fig:unusual_variability} shows one example of an irregular
variability pattern. Panel \ref{fig:unusual_variability}A shows the
estimates for the triquarter point (in Experiment 2) when outliers were
not removed and Panel \ref{fig:unusual_variability}B shows the estimates
for the triquarter point (in Experiment 2) when outliers were removed
(error bars represent the middle 95% of estimated values). When outliers
were not removed, the error bars did not decrease as sample size
increased, but when outliers were removed, the error bars decreased as
sample size increased.

The median absolute deviation was used to identify outtliers. Equation
\ref{eq:median-absolute-deviation} below shows the equation for
computing the median absolute deviation:

\begin{align}
\text{Median absolute deviation} = b\Bigg(M_i\bigg(\mid x_i - M_j(x) \mid \bigg) \Bigg),
(\#eq:median-absolute-deviation)
\end{align}

where $x_i$ is each data point, $M_j(x)$ is the median of the data,
$M_i$ is the median of the median absolute deviations, and $b$ is a
constant whose value is tied to the assumption that the data will be
normally distributed after outliers are removed ($b = 1.4826$;
@leys2013). More technically, the median absolute deviation is the
median of median absolute deviations. The median absolute deviation was
used for two reasons. First, the median absolute deviation is less
impacted by outliers than the commonly used standard deviation . Second,
the median absolute deviation is sensitive to detecting outliers in
small samples such as the ones simulated in the Experiments 2--3 (*N* =
30, 50, and 100).

Estimates were identified as outliers if they lied outside of four
median absolute deviations. For each parameter in each experimental
condition, median absolute deviation values were computed and used to
remove outliers (see Tables \ref{tab:exp1-alpha-theta-removed}--\ref{tab:exp2-theta-removed} in [Appendix B][Appendix B: Number of values removed from data cleaning procedure] for number of parameter estimates removed in each Experiments 1--3). 

```{r example-unusual-variability, include=F}
#data cleaning without outlier removal 
exp_2 <- read_csv(file = 'data/exp_2.csv')
exp_2_unfiltered <- convert_var_to_sd(data = exp_2)
param_summary_exp_2_unfiltered <- compute_parameter_summary(data = exp_2_unfiltered, exp_num = 2)

#necessary factor conversions
param_summary_exp_2_unfiltered$number_measurements <- factor(param_summary_exp_2_unfiltered$number_measurements, 
                                                             levels = c(5, 7, 9, 11))
param_summary_exp_2_unfiltered$sample_size <- factor(param_summary_exp_2_unfiltered$sample_size, 
                                                     levels = c(30, 50, 100, 200, 500, 1000))
param_summary_exp_2_unfiltered$conv_fail <- factor(param_summary_exp_2_unfiltered$conv_fail, levels = c(0, 1))


#generate likert and day data sets
exp_2_analytical_unfiltered <- generate_likert_days_data_sets(summary_data = param_summary_exp_2_unfiltered, exp_num = 2)

#combine analytical and unfiltered data sets 
exp_2_analytical$days$origin <- 'filtered'
exp_2_analytical_unfiltered$days$origin <- 'unfiltered'

combined_data_exp_2 <- rbind(exp_2_analytical$days, exp_2_analytical_unfiltered$days)
combined_data_exp_2$origin <- factor(combined_data_exp_2$origin, levels = c('unfiltered', 'filtered'))

#create data set with gamma estimate from filtered and unfiltered data sets 
gamma_data_combined <- combined_data_exp_2 %>% 
  filter(measurement_spacing == 'Equal', grepl('gamma\\[fixed\\]', parameter)) %>%
  arrange(origin)

gamma_data_combined$parameter <- NA #NA overwrite needed for modifications below

#modify parameter labels
gamma_data_combined$parameter[gamma_data_combined$origin == 'unfiltered'] <- bquote(expr = 'bold(A:Unfiltered~gamma[random]~(Satiation~point))')
gamma_data_combined$parameter[gamma_data_combined$origin == 'filtered'] <- bquote(expr ='bold(B:Filtered~gamma[random]~(Satiation~point))')
gamma_data_combined$parameter <- factor(gamma_data_combined$parameter)

#create ggplot with
generate_filtered_unfiltered_facet_plot(parameter_data = gamma_data_combined, x_axis_name = 'Sample size (*N*)', x_axis_var = 'sample_size', 
                                        beta_lower = 0, beta_upper = 40, file_name = 'Figures/filtered_unfiltered.pdf', ticks = 5, 
                                        legend_direction = 'horizontal', legend_position = 'bottom')
```

```{=tex}
\begin{figure}
  \caption{Estimate Summary for Fixed-Effect Triquarter Point($\upgamma_{fixed}$) With and Without Outliers}
  \label{fig:unusual_variability}
  \includegraphics{Figures/filtered_unfiltered} \hfill{}
  \caption*{Note. \textup{}}
\end{figure}
```
## Appendix B: Parameter estimate plots for all parameter

### Equal spacing

```{r plots-equal-exp1, include=F}
generate_day_likert_facet_plot(analytical_data = exp_1_analytical, target_col = 'measurement_spacing', target_value = 'Equal spacing',
                                x_axis_name = 'Midpoint location (days)', 
                                x_axis_var = 'midpoint', exp_num = 'exp1_', beta_lower = -20, beta_upper = 20, ticks = 5)


```

```{r text-values-equal-exp1, echoF}
gamma_equal_5_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Equal', number_measurements == 5, midpoint == 80, grepl('gamma\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

gamma_equal_7_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Equal', number_measurements == 7, midpoint == 80, grepl('gamma\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci)) 
```

Figure \ref{fig:exp1_plot_equal} shows the estimation accuracy (in terms
of Likert-based or day-based units)each of the nine estimated parameters
when equal spacing is used (error bars represent the middle 95% of
estimated values and shaded horizontal lines indicate the population
value). Panels A--E show the estimation accuracy for parameters measured
in Likert scale units ($\uptheta$ and $\upalpha$; measured on a range of
1--5) and Panels F--I show the estimation accuracy for parameters
measured in day units ($\upbeta$ and $\upgamma$). Note that, in Panel F,
estimates for $\upbeta_{fixed}$ are centered around their corresponding
population values (80, 180, and 280 days), and so the y-axis represents
error (in number of days) from the population value.

Estimation of Likert-unit parameters appears to be unaffected, whereas
the estimation of day-unit parameters appears to incur considerable
variability. The estimation for the fixed- and random-effect values of
the midpoint ($\upbeta_{fixed}$ and $\upbeta_{random}$; Figure
\ref{fig:exp1_plot_equal}F--G) and the satiation point
($\upgamma_{fixed}$ and $\upgamma_{random}$; Figure
\ref{fig:exp1_plot_equal}H--I) incur considerable variability when five
measurements are taken, but this variability largely diminishes when
seven or more measurements are taken. For example, when five
measurements are taken and the midpoint occurs at 80 days, the middle
95% of values estimated for the fixed-effect parameter of the satiation
point ($\upgamma_{fixed}$; Figure \ref{fig:exp1_plot_equal}H) has a
plausible range that spans
`r gamma_equal_5_180$upper_ci - gamma_equal_5_180$lower_ci` days
(`r gamma_equal_5_180$upper_ci` to `r gamma_equal_5_180$lower_ci` days),
but the width of this range decreases to approximately
`r gamma_equal_7_180$upper_ci - gamma_equal_7_180$lower_ci` days when
seven measurements are taken (`r gamma_equal_7_180$upper_ci` to
`r gamma_equal_7_180$lower_ci` days).

```{=tex}
\begin{figure}[H]
  \caption{Summary of Day-Unit Parameter Estimates for Parameter Equal Spacing}
  \label{fig:exp1_plot_equal}
  \includegraphics{Figures/exp1_plot_days_equal spacing} \hfill{}
  \caption*{Note. \textup{Errors bars represent the middle 95\% of estimated values. Gray horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\uptheta_{fixed}$ = 3.00, $\upalpha_{fixed}$ = 3.32, $\upbeta_{fixed}$ = 180.00, $\upgamma_{fixed}$ = 20.00, $\uptheta_{random}$ = 0.05, $\upalpha_{random}$ = 0.05, $\upbeta_{random}$ = 10.00, $\upgamma_{random}$ = 4.00, $\upepsilon$ = 0.03. Sample size is fixed to 225 (\textit{N} = 225). In Panel F, estimates for $\upbeta_{fixed}$ are centered around their corresponding population values (80, 180, and 280 days), and so the y-axis represents error (in number of days) from the population value. Note that random-effect units are in standard deviations. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:exp1-alpha-theta-removed} for the number of values removed for each parameter.}}
\end{figure}

\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Equal Spacing (continued)}
  \includegraphics{Figures/exp1_plot_likert_equal spacing} \hfill{}
\caption*{Note. \textup{Errors bars represent the middle 95\% of estimated values. Gray horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\uptheta_{fixed}$ = 3.00, $\upalpha_{fixed}$ = 3.32, $\upbeta_{fixed}$ = 180.00, $\upgamma_{fixed}$ = 20.00, $\uptheta_{random}$ = 0.05, $\upalpha_{random}$ = 0.05, $\upbeta_{random}$ = 10.00, $\upgamma_{random}$ = 4.00, $\upepsilon$ = 0.03. Sample size is fixed to 225 (\textit{N} = 225). In Panel F, estimates for $\upbeta_{fixed}$ are centered around their corresponding population values (80, 180, and 280 days), and so the y-axis represents error (in number of days) from the population value. Note that random-effect units are in standard deviations. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:exp1-alpha-theta-removed} for the number of values removed for each parameter.}}
\end{figure}
```

### Time-interval increasing spacing

```{r plots-time-increasing-exp1, include=F}
generate_day_likert_facet_plot(analytical_data = exp_1_analytical, target_col = 'measurement_spacing', target_value = 'Time-interval increasing',
                                x_axis_name = 'Midpoint location (days)', 
                                x_axis_var = 'midpoint', exp_num = 'exp1_', beta_lower = -70, beta_upper = 60, ticks = 10)

exp_1_analytical$likert$measurement_spacing
```

```{r text-values-time-increasing-exp1, echoF}
beta_time_inc_5_80 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time increasing', number_measurements == 5, midpoint == 80, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_inc_5_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time increasing', number_measurements == 5, midpoint == 180, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_inc_5_280 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time increasing', number_measurements == 5, midpoint == 280, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_inc_7_280 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time increasing', number_measurements == 7, midpoint == 180, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))
```

Figure \ref{fig:exp1_plot_time_increasing} shows the estimation accuracy
(in terms of Likert-based or day-based units)each of the nine estimated
parameters when time-increasing spacing is used (error bars represent
the middle 95% of estimated values and shaded horizontal lines indicate
the population value). Panels A--E show the estimation accuracy for
parameters measured in Likert scale units ($\uptheta$ and $\upalpha$;
measured on a range of 1--5) and Panels F--I show the estimation
accuracy for parameters measured in day units ($\upbeta$ and
$\upgamma$). Note that, in Panel F, estimates for $\upbeta_{fixed}$ are
centered around their corresponding population values (80, 180, and 280
days), and so the y-axis represents error from the population value (in
number of days).

As in the equal-spacing condition, estimation of Likert-unit parameters
appears to be unaffected, whereas the estimation of day-unit parameters
appears to incur considerable variability. Two general trends exist in
the estimates of day-based parameters. First, for the fixed-effect
midpoint and satiation point parameters ($\upbeta_{fixed}$ and
$\upgamma_{fixed}$; Figure \ref{fig:exp1_plot_time_increasing}F--G),
variability increases exponentially when five measurements are taken and
the and the midpoint moves from 80 to 280 days. As an example, the
middle 95% of values estimated for the fixed-effect midpoint parameter
($\upbeta_{fixed}$; Figure \ref{fig:exp1_plot_time_increasing}F) has
widths of `r beta_time_inc_5_80$upper_ci - beta_time_inc_5_80$lower_ci`
(`r beta_time_inc_5_80$upper_ci` days to `r beta_time_inc_5_80$lower_ci`
days) and
`r beta_time_inc_5_180$upper_ci - beta_time_inc_5_180$lower_ci` days
(`r beta_time_inc_5_180$lower_ci` days to
`r beta_time_inc_5_180$upper_ci` days) when the midpoint occurs at 80
and 180 days, respectively, but the width increases to
`r beta_time_inc_5_280$upper_ci - beta_time_inc_5_280$lower_ci` days
(`r beta_time_inc_5_280$lower_ci` days to
`r beta_time_inc_5_280$upper_ci` days) when the midpoint occurs at 280
days. Second, the large amount of variability observed for the
fixed-effect midpoint and satiation point parameters largely disappears
when seven or more measurements are taken. As an example, the wide range
of `r beta_time_inc_5_280$upper_ci - beta_time_inc_5_280$lower_ci` days
for the fixed-effect midpoint parameter decreases to
`r beta_time_inc_7_280$upper_ci - beta_time_inc_7_280$lower_ci` days
when seven measurements are taken (see (Figure
\ref{fig:exp1_plot_time_increasing}F)).

```{=tex}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Time-Increasing Spacing}
  \label{fig:exp1_plot_time_increasing}
  \includegraphics{Figures/exp1_plot_likert_time increasing} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Time-Increasing Spacing (continued)}
  \includegraphics{Figures/exp1_plot_days_time increasing} \hfill{}
\caption*{Note. \textup{Errors bars represent the middle 95\% of estimated values. Gray horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\uptheta_{fixed}$ = 3.00, $\upalpha_{fixed}$ = 3.32, $\upbeta_{fixed}$ = 180.00, $\upgamma_{fixed}$ = 20.00, $\uptheta_{random}$ = 0.05, $\upalpha_{random}$ = 0.05, $\upbeta_{random}$ = 10.00, $\upgamma_{random}$ = 4.00, $\upepsilon$ = 0.03. Sample size is fixed to 225 (\textit{N} = 225). In Panel F, estimates for $\upbeta_{fixed}$ are centered around their corresponding population values (80, 180, and 280 days), and so the y-axis represents error (in number of days) from the population value. Note that random-effect units are in standard deviations. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:exp1-alpha-theta-removed} for the number of values removed for each parameter.}}
\end{figure}
```
### Time-interval decreasing spacing

```{r plots-time-decreasing-exp1, include=F}
generate_day_likert_facet_plot(analytical_data = exp_1_analytical, target_col = 'measurement_spacing', target_value = 'Time-interval decreasing',
                                x_axis_name = 'Midpoint location (days)', 
                                x_axis_var = 'midpoint', exp_num = 'exp1_', beta_lower = -60, beta_upper = 70, ticks = 10)
```

```{r text-values-time-decreasing-exp1, echoF}
beta_time_dec_5_80 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time decreasing', number_measurements == 5, midpoint == 80, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_dec_5_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time decreasing', number_measurements == 5, midpoint == 180, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_dec_5_280 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time decreasing', number_measurements == 5, midpoint == 280, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_dec_7_280 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time decreasing', number_measurements == 7, midpoint == 180, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))
```

Figure \ref{fig:exp1_plot_time_decreasing} shows the estimation accuracy
(in terms of Likert-based or day-based units)each of the nine estimated
parameters when time-increasing spacing is used (error bars represent
the middle 95% of estimated values and shaded horizontal lines indicate
the population value). Panels A--E show the estimation accuracy for
parameters measured in Likert scale units ($\uptheta$ and $\upalpha$;
measured on a range of 1--5) and Panels F--I show the estimation
accuracy for parameters measured in day units ($\upbeta$ and
$\upgamma$). Note that, in Panel F, estimates for $\upbeta_{fixed}$ are
centered around their corresponding population values (80, 180, and 280
days), and so the y-axis represents error from the population value (in
number of days).

As in the equal-spacing condition, estimation of Likert-unit parameters
appears to be unaffected, whereas the estimation of day-unit parameters
appears to incur considerable variability. Two general trends exist in
the estimates of day-based parameters. First, for the fixed-effect
midpoint and satiation point parameters ($\upbeta_{fixed}$ and
$\upgamma_{fixed}$; Figure \ref{fig:exp1_plot_time_increasing}F--G),
variability increases exponentially when five measurements are taken and
the midpoint moves from 280 to 80 days. As an example, the middle 95% of
values estimated for the fixed-effect midpoint parameter
($\upbeta_{fixed}$; Figure \ref{fig:exp1_plot_time_decreasing}F) has
widths of
`r beta_time_dec_5_280$upper_ci - beta_time_dec_5_280$lower_ci`
(`r beta_time_dec_5_280$upper_ci` days to
`r beta_time_dec_5_280$lower_ci` days) and
`r beta_time_dec_5_180$upper_ci - beta_time_dec_5_180$lower_ci` days
(`r beta_time_dec_5_180$lower_ci` days to
`r beta_time_dec_5_180$upper_ci` days) when the midpoint occurs at 280
and 180 days, respectively, but the width increases to
`r beta_time_inc_5_80$upper_ci - beta_time_inc_5_80$lower_ci` days
(`r beta_time_inc_5_80$lower_ci` days to `r beta_time_inc_5_80$upper_ci`
days) when the midpoint occurs at 80 days. Second, the large amount of
variability observed for the fixed-effect midpoint and satiation point
parameters largely disappears when seven or more measurements are taken.
As an example, the wide range of
`r beta_time_inc_5_80$upper_ci - beta_time_inc_5_80$lower_ci` days for
the fixed-effect midpoint parameter decreases to
`r beta_time_dec_7_280$upper_ci - beta_time_dec_7_280$lower_ci` days
when seven measurements are taken (see (Figure
\ref{fig:exp1_plot_time_increasing}F)).

```{=tex}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Time-Decreasing Spacing}
  \label{fig:exp1_plot_time_decreasing}
  \includegraphics{Figures/exp1_plot_likert_time decreasing} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Time-Decreasing Spacing (continued)}
  \includegraphics{Figures/exp1_plot_days_time decreasing} \hfill{}
\caption*{Note. \textup{Errors bars represent the middle 95\% of estimated values. Gray horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\uptheta_{fixed}$ = 3.00, $\upalpha_{fixed}$ = 3.32, $\upbeta_{fixed}$ = 180.00, $\upgamma_{fixed}$ = 20.00, $\uptheta_{random}$ = 0.05, $\upalpha_{random}$ = 0.05, $\upbeta_{random}$ = 10.00, $\upgamma_{random}$ = 4.00, $\upepsilon$ = 0.03. Sample size is fixed to 225 (\textit{N} = 225). In Panel F, estimates for $\upbeta_{fixed}$ are centered around their corresponding population values (80, 180, and 280 days), and so the y-axis represents error (in number of days) from the population value. Note that random-effect units are in standard deviations. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:exp1-alpha-theta-removed} for the number of values removed for each parameter.}}
\end{figure}
```
### Middle-and-extreme spacing

```{r plots-mid-ext-exp1, include=F}
generate_day_likert_facet_plot(analytical_data = exp_1_analytical, target_col = 'measurement_spacing', target_value = 'Middle-and-extreme spacing',
                                x_axis_name = 'Midpoint location (days)', 
                                x_axis_var = 'midpoint', exp_num = 'exp1_', beta_lower = -20, beta_upper = 20, ticks = 5)
```

```{r text-values-mid-ext-exp1, echoF}
beta_time_dec_5_80 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Middle-and-extreme', number_measurements == 5, midpoint == 80, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_dec_5_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Middle-and-extreme', number_measurements == 5, midpoint == 180, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_dec_5_280 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Middle-and-extreme', number_measurements == 5, midpoint == 280, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_dec_7_280 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time decreasing', number_measurements == 7, midpoint == 180, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))
```

Figure \ref{fig:exp1_plot_time_mid_ext} shows the estimation accuracy
(in terms of Likert-based or day-based units) each of the nine estimated
parameters when time-increasing spacing is used (error bars represent
the middle 95% of estimated values and shaded horizontal lines indicate
the population value). Panels A--E show the estimation accuracy for
parameters measured in Likert scale units ($\uptheta$ and $\upalpha$;
measured on a range of 1--5) and Panels F--I show the estimation
accuracy for parameters measured in day units ($\upbeta$ and
$\upgamma$). Note that, in Panel F, estimates for $\upbeta_{fixed}$ are
centered around their corresponding population values (80, 180, and 280
days), and so the y-axis represents error from the population value (in
number of days).

```{=tex}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Middle-and-Extreme Spacing}
  \label{fig:exp1_plot_time_mid_ext}
  \includegraphics{Figures/exp1_plot_likert_middle-and-extreme} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Middle-and-Extreme Spacing (continued)}
  \includegraphics{Figures/exp1_plot_days_middle-and-extreme} \hfill{}
\caption*{Note. \textup{Errors bars represent the middle 95\% of estimated values. Gray horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\uptheta_{fixed}$ = 3.00, $\upalpha_{fixed}$ = 3.32, $\upbeta_{fixed}$ = 180.00, $\upgamma_{fixed}$ = 20.00, $\uptheta_{random}$ = 0.05, $\upalpha_{random}$ = 0.05, $\upbeta_{random}$ = 10.00, $\upgamma_{random}$ = 4.00, $\upepsilon$ = 0.03. Sample size is fixed to 225 (\textit{N} = 225). In Panel F, estimates for $\upbeta_{fixed}$ are centered around their corresponding population values (80, 180, and 280 days), and so the y-axis represents error (in number of days) from the population value. Note that random-effect units are in standard deviations. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:exp1-alpha-theta-removed} for the number of values removed for each parameter.}}
\end{figure}
```

### Summary of Experiment 1 
```{r plot-summary-exp1, include=F}
generate_summary_facet_plot(condition_data = cond_summary_exp_1, lower_y_limit = -6, upper_y_limit = 20, ticks = 2, exp_num = 'Figures/exp1_', 
                            y_axis_var = 'mean_sd', y_axis_name = 'Parameter variability (standard deviations)')


generate_summary_facet_plot(condition_data = cond_summary_exp_2, lower_y_limit = -6, upper_y_limit = 20, ticks = 2, exp_num = 'Figures/exp2_', 
                            y_axis_var = 'mean_sd', y_axis_name = 'Parameter variability (standard deviations)',
                            x_axis_var = 'sample_size', x_axis_name = 'Sample size (*N*)')


generate_summary_facet_plot(condition_data = cond_summary_exp_3, lower_y_limit = -6, upper_y_limit = 20, ticks = 2, exp_num = 'Figures/exp3_', 
                            y_axis_var = 'mean_sd', y_axis_name = 'Parameter variability (standard deviations)',
                            x_axis_var = 'sample_size', x_axis_name = 'Sample size (*N*)', facet_var = 'time_structuredness')


```


```{=tex}
\begin{figure}
  \caption{Parameter Estimate Accuracy Across Measurement Spacing Conditions in Experiment 1}
  \label{fig:exp1_plot_time_mid_ext}
  \includegraphics{Figures/exp1_summary_plot} \hfill{}
  \caption*{Note.}
\end{figure}
```




## Experiment 2

Experiment 2 investigated whether an optimal measurement spacing
schedule exists to handle uncertainty in the pattern of change. Three
variables were manipulated: measurement spacing, number of measurements,
and pattern of change. Measurement spacing was manipulated by creating
schedules defined by either equal, time-increasing, time-decreasing, or
middle-and-extreme spacing. The levels for number of measurements were
set to either 5, 7, 9, or 11 measurements, and the pattern of change was
manipulated such that the halfway point occurred at either 80, 180, or
280 days.

### Equal spacing

```{r plots-equal-exp2, include=F}
generate_day_likert_facet_plot(analytical_data = exp_2_analytical, 
                               target_col = 'measurement_spacing', target_value = 'Equal spacing',
                               x_axis_name = 'Sample size (*N*)', 
                               x_axis_var = 'sample_size', exp_num = 'exp2_', beta_lower = 165, beta_upper = 205,
                               ticks = 5)
```

```{r text-values-equal-exp2, echoF}
gamma_equal_5_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Equal', number_measurements == 5, midpoint == 80, grepl('gamma\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

gamma_equal_7_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Equal', number_measurements == 7, midpoint == 80, grepl('gamma\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci)) 
```

Figure \ref{fig:exp1_plot_equal} shows the estimation accuracy (in terms
of Likert-based or day-based units)each of the nine estimated parameters
when equal spacing is used (error bars represent the middle 95% of
estimated values and shaded horizontal lines indicate the population
value). Panels A--E show the estimation accuracy for parameters measured
in Likert scale units ($\uptheta$ and $\upalpha$; measured on a range of
1--5) and Panels F--I show the estimation accuracy for parameters
measured in day units ($\upbeta$ and $\upgamma$). Note that, in Panel F,
estimates for $\upbeta_{fixed}$ are centered around their corresponding
population values (80, 180, and 280 days), and so the y-axis represents
error (in number of days) from the population value.

Estimation of Likert-unit parameters appears to be unaffected, whereas
the estimation of day-unit parameters appears to incur considerable
variability. The estimation for the fixed- and random-effect values of
the midpoint ($\upbeta_{fixed}$ and $\upbeta_{random}$; Figure
\ref{fig:exp1_plot_equal}F--G) and the satiation point
($\upgamma_{fixed}$ and $\upgamma_{random}$; Figure
\ref{fig:exp1_plot_equal}H--I) incur considerable variability when five
measurements are taken, but this variability largely diminishes when
seven or more measurements are taken. For example, when five
measurements are taken and the midpoint occurs at 80 days, the middle
95% of values estimated for the fixed-effect parameter of the satiation
point ($\upgamma_{fixed}$; Figure \ref{fig:exp1_plot_equal}H) has a
plausible range that spans
`r gamma_equal_5_180$upper_ci - gamma_equal_5_180$lower_ci` days
(`r gamma_equal_5_180$upper_ci` to `r gamma_equal_5_180$lower_ci` days),
but the width of this range decreases to approximately
`r gamma_equal_7_180$upper_ci - gamma_equal_7_180$lower_ci` days when
seven measurements are taken (`r gamma_equal_7_180$upper_ci` to
`r gamma_equal_7_180$lower_ci` days).

```{=tex}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Equal Spacing}
  \label{fig:exp1_plot_equal}
  \includegraphics{Figures/exp2_plot_likert_equal} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Equal Spacing (continued)}
  \includegraphics{Figures/exp2_plot_days_equal} \hfill{}
\caption*{Note. \textup{Errors bars represent the middle 95\% of estimated values. Gray horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\uptheta_{fixed}$ = 3.00, $\upalpha_{fixed}$ = 3.32, $\upbeta_{fixed}$ = 180.00, $\upgamma_{fixed}$ = 20.00, $\uptheta_{random}$ = 0.05, $\upalpha_{random}$ = 0.05, $\upbeta_{random}$ = 10.00, $\upgamma_{random}$ = 4.00, $\upepsilon$ = 0.03. Sample size is fixed to 225 (\textit{N} = 225). In Panel F, estimates for $\upbeta_{fixed}$ are centered around their corresponding population values (80, 180, and 280 days), and so the y-axis represents error (in number of days) from the population value. Note that random-effect units are in standard deviations. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:exp1-alpha-theta-removed} for the number of values removed for each parameter.}}
\end{figure}
```

### Time-interval increasing spacing

```{r plots-time-increasing-exp2, include=F}
generate_day_likert_facet_plot(analytical_data = exp_2_analytical, 
                               target_col = 'measurement_spacing', target_value = 'Time-interval increasing',
                               x_axis_name = 'Sample size (*N*)', 
                               x_axis_var = 'sample_size', exp_num = 'exp2_', beta_lower = 165, beta_upper = 205,
                               ticks = 5)

```

```{r text-values-time-increasing-exp2, echoF}
beta_time_inc_5_80 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time increasing', number_measurements == 5, midpoint == 80, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_inc_5_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time increasing', number_measurements == 5, midpoint == 180, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_inc_5_280 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time increasing', number_measurements == 5, midpoint == 280, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_inc_7_280 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time increasing', number_measurements == 7, midpoint == 180, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))
```

Figure \ref{fig:exp2_plot_time_increasing} shows the estimation accuracy
(in terms of Likert-based or day-based units)each of the nine estimated
parameters when time-increasing spacing is used (error bars represent
the middle 95% of estimated values and shaded horizontal lines indicate
the population value). Panels A--E show the estimation accuracy for
parameters measured in Likert scale units ($\uptheta$ and $\upalpha$;
measured on a range of 1--5) and Panels F--I show the estimation
accuracy for parameters measured in day units ($\upbeta$ and
$\upgamma$). Note that, in Panel F, estimates for $\upbeta_{fixed}$ are
centered around their corresponding population values (80, 180, and 280
days), and so the y-axis represents error from the population value (in
number of days).

As in the equal-spacing condition, estimation of Likert-unit parameters
appears to be unaffected, whereas the estimation of day-unit parameters
appears to incur considerable variability. Two general trends exist in
the estimates of day-based parameters. First, for the fixed-effect
midpoint and satiation point parameters ($\upbeta_{fixed}$ and
$\upgamma_{fixed}$; Figure \ref{fig:exp1_plot_time_increasing}F--G),
variability increases exponentially when five measurements are taken and
the and the midpoint moves from 80 to 280 days. As an example, the
middle 95% of values estimated for the fixed-effect midpoint parameter
($\upbeta_{fixed}$; Figure \ref{fig:exp1_plot_time_increasing}F) has
widths of `r beta_time_inc_5_80$upper_ci - beta_time_inc_5_80$lower_ci`
(`r beta_time_inc_5_80$upper_ci` days to `r beta_time_inc_5_80$lower_ci`
days) and
`r beta_time_inc_5_180$upper_ci - beta_time_inc_5_180$lower_ci` days
(`r beta_time_inc_5_180$lower_ci` days to
`r beta_time_inc_5_180$upper_ci` days) when the midpoint occurs at 80
and 180 days, respectively, but the width increases to
`r beta_time_inc_5_280$upper_ci - beta_time_inc_5_280$lower_ci` days
(`r beta_time_inc_5_280$lower_ci` days to
`r beta_time_inc_5_280$upper_ci` days) when the midpoint occurs at 280
days. Second, the large amount of variability observed for the
fixed-effect midpoint and satiation point parameters largely disappears
when seven or more measurements are taken. As an example, the wide range
of `r beta_time_inc_5_280$upper_ci - beta_time_inc_5_280$lower_ci` days
for the fixed-effect midpoint parameter decreases to
`r beta_time_inc_7_280$upper_ci - beta_time_inc_7_280$lower_ci` days
when seven measurements are taken (see (Figure
\ref{fig:exp1_plot_time_increasing}F)).

```{=tex}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Time-Increasing Spacing}
  \label{fig:exp2_plot_time_increasing}
  \includegraphics{Figures/exp2_plot_likert_time increasing} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Time-Increasing Spacing (continued)}
  \includegraphics{Figures/exp2_plot_days_time increasing} \hfill{}
\caption*{Note. \textup{Errors bars represent the middle 95\% of estimated values. Gray horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\uptheta_{fixed}$ = 3.00, $\upalpha_{fixed}$ = 3.32, $\upbeta_{fixed}$ = 180.00, $\upgamma_{fixed}$ = 20.00, $\uptheta_{random}$ = 0.05, $\upalpha_{random}$ = 0.05, $\upbeta_{random}$ = 10.00, $\upgamma_{random}$ = 4.00, $\upepsilon$ = 0.03. Sample size is fixed to 225 (\textit{N} = 225). In Panel F, estimates for $\upbeta_{fixed}$ are centered around their corresponding population values (80, 180, and 280 days), and so the y-axis represents error (in number of days) from the population value. Note that random-effect units are in standard deviations. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:exp1-alpha-theta-removed} for the number of values removed for each parameter.}}
\end{figure}
```

### Time-interval decreasing spacing

```{r plots-time-decreasing-exp2, include=F}
generate_day_likert_facet_plot(analytical_data = exp_2_analytical, 
                               target_col = 'measurement_spacing', target_value = 'Time-interval decreasing',
                               x_axis_name = 'Sample size (*N*)', 
                               x_axis_var = 'sample_size', exp_num = 'exp2_', beta_lower = 155, beta_upper = 195,
                               ticks = 5)
```

```{r text-values-time-decreasing-exp2, echoF}
beta_time_dec_5_80 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time decreasing', number_measurements == 5, midpoint == 80, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_dec_5_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time decreasing', number_measurements == 5, midpoint == 180, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_dec_5_280 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time decreasing', number_measurements == 5, midpoint == 280, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_dec_7_280 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time decreasing', number_measurements == 7, midpoint == 180, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))
```

Figure \ref{fig:exp2_plot_time_decreasing} shows the estimation accuracy
(in terms of Likert-based or day-based units)each of the nine estimated
parameters when time-increasing spacing is used (error bars represent
the middle 95% of estimated values and shaded horizontal lines indicate
the population value). Panels A--E show the estimation accuracy for
parameters measured in Likert scale units ($\uptheta$ and $\upalpha$;
measured on a range of 1--5) and Panels F--I show the estimation
accuracy for parameters measured in day units ($\upbeta$ and
$\upgamma$). Note that, in Panel F, estimates for $\upbeta_{fixed}$ are
centered around their corresponding population values (80, 180, and 280
days), and so the y-axis represents error from the population value (in
number of days).

As in the equal-spacing condition, estimation of Likert-unit parameters
appears to be unaffected, whereas the estimation of day-unit parameters
appears to incur considerable variability. Two general trends exist in
the estimates of day-based parameters. First, for the fixed-effect
midpoint and satiation point parameters ($\upbeta_{fixed}$ and
$\upgamma_{fixed}$; Figure \ref{fig:exp1_plot_time_increasing}F--G),
variability increases exponentially when five measurements are taken and
the midpoint moves from 280 to 80 days. As an example, the middle 95% of
values estimated for the fixed-effect midpoint parameter
($\upbeta_{fixed}$; Figure \ref{fig:exp1_plot_time_decreasing}F) has
widths of
`r beta_time_dec_5_280$upper_ci - beta_time_dec_5_280$lower_ci`
(`r beta_time_dec_5_280$upper_ci` days to
`r beta_time_dec_5_280$lower_ci` days) and
`r beta_time_dec_5_180$upper_ci - beta_time_dec_5_180$lower_ci` days
(`r beta_time_dec_5_180$lower_ci` days to
`r beta_time_dec_5_180$upper_ci` days) when the midpoint occurs at 280
and 180 days, respectively, but the width increases to
`r beta_time_inc_5_80$upper_ci - beta_time_inc_5_80$lower_ci` days
(`r beta_time_inc_5_80$lower_ci` days to `r beta_time_inc_5_80$upper_ci`
days) when the midpoint occurs at 80 days. Second, the large amount of
variability observed for the fixed-effect midpoint and satiation point
parameters largely disappears when seven or more measurements are taken.
As an example, the wide range of
`r beta_time_inc_5_80$upper_ci - beta_time_inc_5_80$lower_ci` days for
the fixed-effect midpoint parameter decreases to
`r beta_time_dec_7_280$upper_ci - beta_time_dec_7_280$lower_ci` days
when seven measurements are taken (see (Figure
\ref{fig:exp1_plot_time_increasing}F)).

```{=tex}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Time-Decreasing Spacing}
  \label{fig:exp2_plot_time_decreasing}
  \includegraphics{Figures/exp1_plot_likert_time decreasing} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Time-Decreasing Spacing (continued)}
  \includegraphics{Figures/exp2_plot_days_time decreasing} \hfill{}
\caption*{Note. \textup{Errors bars represent the middle 95\% of estimated values. Gray horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\uptheta_{fixed}$ = 3.00, $\upalpha_{fixed}$ = 3.32, $\upbeta_{fixed}$ = 180.00, $\upgamma_{fixed}$ = 20.00, $\uptheta_{random}$ = 0.05, $\upalpha_{random}$ = 0.05, $\upbeta_{random}$ = 10.00, $\upgamma_{random}$ = 4.00, $\upepsilon$ = 0.03. Sample size is fixed to 225 (\textit{N} = 225). In Panel F, estimates for $\upbeta_{fixed}$ are centered around their corresponding population values (80, 180, and 280 days), and so the y-axis represents error (in number of days) from the population value. Note that random-effect units are in standard deviations. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:exp1-alpha-theta-removed} for the number of values removed for each parameter.}}
\end{figure}
```

### Middle-and-extreme spacing

```{r plots-mid-ext-exp2, include=F}
generate_day_likert_facet_plot(analytical_data = exp_2_analytical, 
                               target_col = 'measurement_spacing', target_value = 'Middle-and-extreme spacing',
                               x_axis_name = 'Sample size (*N*)', 
                               x_axis_var = 'sample_size', exp_num = 'exp2_', beta_lower = 165, beta_upper = 205,
                               ticks = 5)
```

```{r text-values-mid-ext-exp2, echoF}
beta_time_dec_5_80 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Middle-and-extreme', number_measurements == 5, midpoint == 80, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_dec_5_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Middle-and-extreme', number_measurements == 5, midpoint == 180, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_dec_5_280 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Middle-and-extreme', number_measurements == 5, midpoint == 280, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

beta_time_dec_7_280 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Time decreasing', number_measurements == 7, midpoint == 180, grepl('beta\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))
```

Figure \ref{fig:exp1_plot_time_mid_ext} shows the estimation accuracy
(in terms of Likert-based or day-based units) each of the nine estimated
parameters when time-increasing spacing is used (error bars represent
the middle 95% of estimated values and shaded horizontal lines indicate
the population value). Panels A--E show the estimation accuracy for
parameters measured in Likert scale units ($\uptheta$ and $\upalpha$;
measured on a range of 1--5) and Panels F--I show the estimation
accuracy for parameters measured in day units ($\upbeta$ and
$\upgamma$). Note that, in Panel F, estimates for $\upbeta_{fixed}$ are
centered around their corresponding population values (80, 180, and 280
days), and so the y-axis represents error from the population value (in
number of days).

```{=tex}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Middle-and-Extreme Spacing}
  \label{fig:exp2_plot_time_mid_ext}
  \includegraphics{Figures/exp1_plot_likert_middle-and-extreme} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Middle-and-Extreme Spacing (continued)}
  \includegraphics{Figures/exp2_plot_days_middle-and-extreme} \hfill{}
\caption*{Note. \textup{Errors bars represent the middle 95\% of estimated values. Gray horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\uptheta_{fixed}$ = 3.00, $\upalpha_{fixed}$ = 3.32, $\upbeta_{fixed}$ = 180.00, $\upgamma_{fixed}$ = 20.00, $\uptheta_{random}$ = 0.05, $\upalpha_{random}$ = 0.05, $\upbeta_{random}$ = 10.00, $\upgamma_{random}$ = 4.00, $\upepsilon$ = 0.03. Sample size is fixed to 225 (\textit{N} = 225). In Panel F, estimates for $\upbeta_{fixed}$ are centered around their corresponding population values (80, 180, and 280 days), and so the y-axis represents error (in number of days) from the population value. Note that random-effect units are in standard deviations. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:exp1-alpha-theta-removed} for the number of values removed for each parameter.}}
\end{figure}
```

### Summary of Experiment 2
```{r plot-summary-exp2, include=F}
generate_summary_facet_plot(condition_data = cond_summary_exp_2, lower_y_limit = -6, upper_y_limit = 20, ticks = 2, exp_num = 'Figures/exp2_', 
                            y_axis_var = 'mean_perc_error', y_axis_name = 'Parameter bias (percentage error)', 
                            x_axis_var = 'sample_size', x_axis_name = 'Sample size (*N*)')

```


```{=tex}
\begin{figure}
  \caption{Parameter Estimate Accuracy Across Measurement Spacing Conditions in Experiment 1}
  \label{fig:exp1_plot_time_mid_ext}
  \includegraphics{Figures/exp2_summary_plot} \hfill{}
  \caption*{Note.}
\end{figure}
```





## Experiment 3

Experiment 3 investigated whether an optimal measurement spacing
schedule exists to handle uncertainty in the pattern of change. Three
variables were manipulated: measurement spacing, number of measurements,
and pattern of change. Measurement spacing was manipulated by creating
schedules defined by either equal, time-increasing, time-decreasing, or
middle-and-extreme spacing. The levels for number of measurements were
set to either 5, 7, 9, or 11 measurements, and the pattern of change was
manipulated such that the halfway point occurred at either 80, 180, or
280 days.

### Time-structured data

```{r plots-time-structured-exp3, include=F}
generate_day_likert_facet_plot(analytical_data = exp_3_analytical, 
                               target_col = 'time_structuredness', target_value = 'time_structured',
                               x_axis_name = 'Sample size (*N*)', 
                               x_axis_var = 'sample_size', exp_num = 'exp3_', beta_lower = 165, beta_upper = 205,
                               ticks = 5)
```

```{r text-values-time-structured-exp3, echoF}
gamma_equal_5_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Equal', number_measurements == 5, midpoint == 80, grepl('gamma\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

gamma_equal_7_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Equal', number_measurements == 7, midpoint == 80, grepl('gamma\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci)) 
```

Figure \ref{fig:exp3_plot_equal} shows the estimation accuracy (in terms
of Likert-based or day-based units)each of the nine estimated parameters
when equal spacing is used (error bars represent the middle 95% of
estimated values and shaded horizontal lines indicate the population
value). Panels A--E show the estimation accuracy for parameters measured
in Likert scale units ($\uptheta$ and $\upalpha$; measured on a range of
1--5) and Panels F--I show the estimation accuracy for parameters
measured in day units ($\upbeta$ and $\upgamma$). Note that, in Panel F,
estimates for $\upbeta_{fixed}$ are centered around their corresponding
population values (80, 180, and 280 days), and so the y-axis represents
error (in number of days) from the population value.


```{=tex}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Time-Stuctured Data}
  \label{fig:exp1_plot_equal}
  \includegraphics{Figures/exp3_plot_likert_time_structured} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Time-Stuctured Data (continued)}
  \includegraphics{Figures/exp3_plot_days_time_structured} \hfill{}
\caption*{Note. \textup{Errors bars represent the middle 95\% of estimated values. Gray horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\uptheta_{fixed}$ = 3.00, $\upalpha_{fixed}$ = 3.32, $\upbeta_{fixed}$ = 180.00, $\upgamma_{fixed}$ = 20.00, $\uptheta_{random}$ = 0.05, $\upalpha_{random}$ = 0.05, $\upbeta_{random}$ = 10.00, $\upgamma_{random}$ = 4.00, $\upepsilon$ = 0.03. Sample size is fixed to 225 (\textit{N} = 225). In Panel F, estimates for $\upbeta_{fixed}$ are centered around their corresponding population values (80, 180, and 280 days), and so the y-axis represents error (in number of days) from the population value. Note that random-effect units are in standard deviations. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:exp1-alpha-theta-removed} for the number of values removed for each parameter.}}
\end{figure}
```

### Time-unstructured data (fast response)

```{r plots-fast-response-exp3, include=F}
generate_day_likert_facet_plot(analytical_data = exp_3_analytical, 
                               target_col = 'time_structuredness', target_value = 'fast_response',
                               x_axis_name = 'Sample size (*N*)', 
                               x_axis_var = 'sample_size', exp_num = 'exp3_', beta_lower = 165, beta_upper = 205,
                               ticks = 5)
```

```{r text-values-fast-response-exp3, echoF}
gamma_equal_5_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Equal', number_measurements == 5, midpoint == 80, grepl('gamma\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

gamma_equal_7_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Equal', number_measurements == 7, midpoint == 80, grepl('gamma\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci)) 
```

Figure \ref{fig:exp3_plot_equal} shows the estimation accuracy (in terms
of Likert-based or day-based units)each of the nine estimated parameters
when equal spacing is used (error bars represent the middle 95% of
estimated values and shaded horizontal lines indicate the population
value). Panels A--E show the estimation accuracy for parameters measured
in Likert scale units ($\uptheta$ and $\upalpha$; measured on a range of
1--5) and Panels F--I show the estimation accuracy for parameters
measured in day units ($\upbeta$ and $\upgamma$). Note that, in Panel F,
estimates for $\upbeta_{fixed}$ are centered around their corresponding
population values (80, 180, and 280 days), and so the y-axis represents
error (in number of days) from the population value.



```{=tex}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Time-Unstructured Data (Fast Response)}
  \label{fig:exp3_plot_fast_response}
  \includegraphics{Figures/exp3_plot_likert_fast_response} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Time-Unstructured Data (Fast Response; continued)}
  \includegraphics{Figures/exp3_plot_days_fast_response} \hfill{}
\caption*{Note. \textup{Errors bars represent the middle 95\% of estimated values. Gray horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\uptheta_{fixed}$ = 3.00, $\upalpha_{fixed}$ = 3.32, $\upbeta_{fixed}$ = 180.00, $\upgamma_{fixed}$ = 20.00, $\uptheta_{random}$ = 0.05, $\upalpha_{random}$ = 0.05, $\upbeta_{random}$ = 10.00, $\upgamma_{random}$ = 4.00, $\upepsilon$ = 0.03. Sample size is fixed to 225 (\textit{N} = 225). In Panel F, estimates for $\upbeta_{fixed}$ are centered around their corresponding population values (80, 180, and 280 days), and so the y-axis represents error (in number of days) from the population value. Note that random-effect units are in standard deviations. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:exp1-alpha-theta-removed} for the number of values removed for each parameter.}}
\end{figure}
```



### Time-unstructured data (slow response)

```{r plots-slow-response-exp3, include=F}
generate_day_likert_facet_plot(analytical_data = exp_3_analytical, 
                               target_col = 'time_structuredness', target_value = 'slow_response',
                               x_axis_name = 'Sample size (*N*)', 
                               x_axis_var = 'sample_size', exp_num = 'exp3_', beta_lower = 165, beta_upper = 205,
                               ticks = 5)
```

```{r text-values-slow-response-exp3, echoF}
gamma_equal_5_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Equal', number_measurements == 5, midpoint == 80, grepl('gamma\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci))

gamma_equal_7_180 <- exp_1_analytical$days %>% 
  filter(measurement_spacing == 'Equal', number_measurements == 7, midpoint == 80, grepl('gamma\\[fixed\\]', parameter)) %>%
  select(lower_ci, upper_ci) %>%
  mutate(lower_ci = as.integer(lower_ci), 
         upper_ci = as.integer(upper_ci)) 
```

Figure \ref{fig:exp3_plot_equal} shows the estimation accuracy (in terms
of Likert-based or day-based units)each of the nine estimated parameters
when equal spacing is used (error bars represent the middle 95% of
estimated values and shaded horizontal lines indicate the population
value). Panels A--E show the estimation accuracy for parameters measured
in Likert scale units ($\uptheta$ and $\upalpha$; measured on a range of
1--5) and Panels F--I show the estimation accuracy for parameters
measured in day units ($\upbeta$ and $\upgamma$). Note that, in Panel F,
estimates for $\upbeta_{fixed}$ are centered around their corresponding
population values (80, 180, and 280 days), and so the y-axis represents
error (in number of days) from the population value.



```{=tex}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Time-Unstructured Data (Slow Response)}
  \label{fig:exp3_plot_slow_response}
  \includegraphics{Figures/exp3_plot_likert_slow_response} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Summary of Parameter Estimates for Time-Unstructured Data (Slow Response; continued)}
  \includegraphics{Figures/exp3_plot_days_slow_response} \hfill{}
\caption*{Note. \textup{Errors bars represent the middle 95\% of estimated values. Gray horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\uptheta_{fixed}$ = 3.00, $\upalpha_{fixed}$ = 3.32, $\upbeta_{fixed}$ = 180.00, $\upgamma_{fixed}$ = 20.00, $\uptheta_{random}$ = 0.05, $\upalpha_{random}$ = 0.05, $\upbeta_{random}$ = 10.00, $\upgamma_{random}$ = 4.00, $\upepsilon$ = 0.03. Sample size is fixed to 225 (\textit{N} = 225). In Panel F, estimates for $\upbeta_{fixed}$ are centered around their corresponding population values (80, 180, and 280 days), and so the y-axis represents error (in number of days) from the population value. Note that random-effect units are in standard deviations. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:exp1-alpha-theta-removed} for the number of values removed for each parameter.}}
\end{figure}
```




### Experiment 1

```{r exp1-alpha-theta-removed, echo=F}
print_param_table(table_ready_data = exp_1_tables$removed_value_table, parameter_name = 'theta|alpha', 
            caption_name = 'Number of Removed Values for Each Parameter Estimated in Experiment 1', 
            col_header_name = c('$\\\\uptheta_{fixed}$(lower plateau)', '$\\\\uptheta_{random}$(lower plateau)',
                                '$\\\\upalpha_{fixed}$(upper plateau)', '$\\\\upalpha_{random}$(upper plateau)'), 
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c(80, 180, 280))
```

\addtocounter{table}{-1}

```{r exp1-beta-gamma-removed, echo=F}
print_param_table(table_ready_data = exp_1_tables$removed_value_table, parameter_name = 'beta|gamma', 
            caption_name = 'Number of Removed Values for Each Parameter Estimated in Experiment 1 (continued)', 
            col_header_name = c('$\\\\upbeta_{fixed}$(midpoint)', '$\\\\upbeta_{random}$(midpoint)',
                                '$\\\\upgamma_{fixed}$(satiation point)', '$\\\\upgamma_{random}$(satiation point)'), 
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c(80, 180, 280))
```

\addtocounter{table}{-1}

```{r exp1-epsilon-removed, echo=F}
print_param_table(table_ready_data = exp_1_tables$removed_value_table, parameter_name = 'epsilon', 
            caption_name = 'Number of Removed Values for Each Parameter Estimated in Experiment 1 (continued)', 
            col_header_name = c('$\\\\upepsilon$(error)'),
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c(80, 180, 280))
```

### Experiment 2

```{r exp2-theta-removed, echo=F}
print_param_table(table_ready_data = exp_2_tables$removed_value_table, parameter_name = 'theta', 
            caption_name = 'Parameter Values Estimated in Experiment 2', 
            col_header_name = c('$\\\\uptheta_{fixed}$(lower plateau)', '$\\\\uptheta_{random}$(lower plateau)'), 
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```

\addtocounter{table}{-1}

```{r exp2-alpha-removed, echo=F}
print_param_table(table_ready_data = exp_2_tables$removed_value_table, parameter_name = 'theta', 
            caption_name = 'Parameter Values Estimated in Experiment 2 (continued)', 
            col_header_name = c('$\\\\upalpha_{fixed}$(upper plateau)', '$\\\\upalpha_{random}$(upper plateau)'), 
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```

\addtocounter{table}{-1}

```{r exp2-beta-removed, echo=F}
print_param_table(table_ready_data = exp_2_tables$removed_value_table, parameter_name = 'beta', 
            caption_name = 'Parameter Values Estimated in Experiment 2 (continued)', 
            col_header_name = c('$\\\\upbeta_{fixed}$(midpoint)', '$\\\\upbeta_{random}$(midpoint)'), 
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```

\addtocounter{table}{-1}

```{r exp2-gamma-removed, echo=F}
print_param_table(table_ready_data = exp_2_tables$removed_value_table, parameter_name = 'gamma', 
            caption_name = 'Parameter Values Estimated in Experiment 2 (continued)', 
            col_header_name = c('$\\\\upgamma_{fixed}$(midpoint)', '$\\\\upgamma_{random}$(midpoint)'), 
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```

\addtocounter{table}{-1}

```{r exp2-epsilon-removed, echo=F}
print_param_table(table_ready_data = exp_2_tables$removed_value_table, parameter_name = 'epsilon', 
            caption_name = 'Parameter Values Estimated in Experiment 2 (continued)', 
            col_header_name = c('$\\\\upepsilon$(error)'), 
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```

