---
shorttitle        : "Measurement timing"
format          : "pandoc"
header-includes:
  - \usepackage{nccmath}
  - \usepackage{caption}
  - \usepackage{textcomp} #for copyright symbol on title page
  - \usepackage{longtable}
  - \usepackage{makecell}
  - \usepackage[section]{placeins}
  - \usepackage{setspace}
  - \usepackage{biblatex}
  - \usepackage{booktabs}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{xcolor}
  - \usepackage{amsthm} 
  - \usepackage{amsmath} ##needed for argmax
  - \usepackage{bm}  #thicker bold in math 
  - \DeclareMathOperator*{\argmax}{arg\,max}
  - \usepackage{setspace} #needed to doublespace caption text (using \doublespacing)
  - \usepackage[labelfont = {bf, up}]{caption} 
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \usepackage{upgreek}  #required for non-italicized Greek letters
  - \usepackage{subcaption}
  - \captionsetup[figure]{labelfont={normalfont, bf}, singlelinecheck=false, labelsep=newline}
  - \DeclareCaptionFont{figCaptionFont}{\fontfamily{phv}\doublespacing} #sets caption font to sans serif font of Helvetica 
  - \DeclareCaptionFont{figCaptionSize}{\fontsize{9.5pt}{11.4pt}\selectfont} #set caption font size to footnote 
  - \DeclareCaptionFont{tabCaptionSize}{\small} #caption size for table title
  - \DeclareCaptionFont{figCaptionStyle}{\textup}  #set caption font to non-italicized font  
  - \DeclareCaptionLabelSeparator{captionSep}{\newline} #separates figure label and figure title with required white space
  - \captionsetup[figure]{labelfont={figCaptionStyle, bf}, font = {figCaptionFont,figCaptionSize, figCaptionStyle}, labelsep = captionSep, justification= raggedright}
  - \captionsetup[table]{labelfont={tabCaptionSize, bf}, font = {figCaptionFont, tabCaptionSize, figCaptionStyle}, labelsep = captionSep, justification= raggedright}
  - \newenvironment{helvenv}{\fontfamily{phv}\selectfont}{}
  - \raggedbottom #ensures text starts from top of page and any white space is at the botom

#both are needed to change font type of table footnotes
  - \usepackage{anyfontsize}
  - \AtBeginEnvironment{ThreePartTable}{\fontfamily{phv} \fontsize{10.5pt}{12pt}\selectfont} 
  - \AtBeginEnvironment{tablenotes}{\fontsize{9.5pt}{11.4pt}\selectfont} 

#environment numbering 
  - \setcounter{section}{0} 
  - \makeatletter \renewcommand\thesection{}\renewcommand\thesubsection{\@arabic\c@section.\@arabic\c@subsection} \makeatother

#set table line widths 
  - \setlength\cmidrulewidth{1pt} #line thickness of lines within table and in multi-row headers
  - \setlength\lightrulewidth{1pt} #line thickness of bottom line in header 

  - \newtheorem{theorem}{Theorem}
  - \newtheorem{example}[theorem]{Example}
  - \renewcommand\theadfont{}
  #modifies heading levels of 4-5 to follow apa7
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}
    
    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother
  
  
author: 
  - name          : "Sebastian Sciarra "
    affiliation   : "1"
    corresponding : yes    
    email         : "ssciarra@uoguelph.ca"
affiliation: 
  - id            : "1"
    institution   : "University of Guelph"
keywords          : "measurement timing, nonlinear "
wordcount         : "5554 words"
floatsintext      : yes
linkcolor         : blue
figsintext        : yes 
figurelist        : no
tablelist         : no
footnotelist      : no
numbersections    : yes
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa7"
csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
classoption       : "man"
output            : papaja::apa6_pdf
keep_tex: true
editor_options: 
  markdown: 
    wrap: 72
bibliography: dissertation_references.bib
---

```{r package_loading, include=F}
#load packages
library(easypackages)
packages <- c('devtools','tidyverse', 'RColorBrewer', 'parallel', 'data.table', 'kableExtra', 'ggtext', 'egg', 'nonlinSims','papaja', 'ggbrace', 'cowplot')
libraries(packages)
load_all()
```

```{r knitting_setup, echo=F, message = F, warning = F}
#import raw data files (needed for computing variances)
exp_1_raw <- convert_raw_var_to_sd(raw_data = read_csv('data/exp_1_data.csv')) %>%
  mutate_at(.vars = c("number_measurements", "measurement_spacing", "midpoint"), factor)
  
exp_2_raw <-convert_raw_var_to_sd(raw_data = read_csv('data/exp_2_data.csv')) %>%
  mutate_at(.vars = c("number_measurements", "measurement_spacing", "sample_size"), factor)

exp_3_raw <-convert_raw_var_to_sd(raw_data = read_csv('data/exp_3_data.csv')) %>%
  mutate_at(.vars = c("number_measurements", "time_structuredness", "sample_size"), factor)

#unfiltered data 
param_summary_exp_1 <- readRDS(file = 'data/uf_param_summary_exp_1.RData')
param_summary_exp_2 <- readRDS(file = 'data/uf_param_summary_exp_2.RData')
param_summary_exp_3 <- readRDS(file = 'data/uf_param_summary_exp_3.RData')

#create analytical versions of summary data + converts vars to sds
exp_1_analytical <- generate_likert_days_data_sets(summary_data = param_summary_exp_1, exp_num = '1')
exp_2_analytical <- generate_likert_days_data_sets(summary_data = param_summary_exp_2, exp_num = '2')
exp_3_analytical <- generate_likert_days_data_sets(summary_data = param_summary_exp_3, exp_num = '3')

combined_analytical_exp_1 <- rbind(exp_1_analytical$likert, exp_1_analytical$days)
combined_analytical_exp_2 <- rbind(exp_2_analytical$likert, exp_2_analytical$days)
combined_analytical_exp_3 <- rbind(exp_3_analytical$likert, exp_3_analytical$days)

#create condition summary data sets 
cond_summary_exp_1 <- compute_condition_summary(param_summary_data = combined_analytical_exp_1, facet_var = 'measurement_spacing', 
                          ind_vars = c('number_measurements', 'measurement_spacing', 'midpoint'))
cond_summary_exp_2 <- compute_condition_summary(param_summary_data = combined_analytical_exp_2, facet_var = 'measurement_spacing', 
                  ind_vars = c('number_measurements', 'measurement_spacing', 'sample_size'))

cond_summary_exp_3 <- compute_condition_summary(param_summary_data = combined_analytical_exp_3, facet_var = 'time_structuredness', 
                          ind_vars = c('number_measurements', 'sample_size', 'time_structuredness'))
```

```{r pre_knitting_setup_unfiltered, echo=F, eval=F, include=F}
#code should be computed before knitting to decrease knitting time 
#load data from experiments
exp_1 <- read_csv(file = 'data/exp_1_data.csv')
exp_2 <- read_csv(file = 'data/exp_2_data.csv')
exp_3 <- read_csv(file = 'data/exp_3_data.csv')

#compute parameter summary statistics  
param_summary_exp_1 <- compute_parameter_summary(data = exp_1, exp_num = 1)
param_summary_exp_2 <- compute_parameter_summary(data = exp_2, exp_num = 2)
param_summary_exp_3 <- compute_parameter_summary(data = exp_3, exp_num = 3)

#necessary factor conversions 
param_summary_exp_1$number_measurements <- factor(param_summary_exp_1$number_measurements, levels = c(5, 7, 9,11))
param_summary_exp_1$midpoint <- factor(param_summary_exp_1$midpoint, levels = c(80, 180,280))

param_summary_exp_2$number_measurements <- factor(param_summary_exp_2$number_measurements, levels = c(5, 7, 9,11))
param_summary_exp_2$sample_size <- factor(param_summary_exp_2$sample_size, levels = c(30, 50, 100, 200, 500, 1000))

param_summary_exp_3$number_measurements <- factor(param_summary_exp_3$number_measurements, levels = c(5, 7, 9,11))
param_summary_exp_3$sample_size <- factor(param_summary_exp_3$sample_size, levels = c(30, 50, 100, 200, 500, 1000))

#write data sets 
#save parameter summary files as RData files so that metadata are correctly stored (e.g., factor levels, variable types)
saveRDS(object = param_summary_exp_1, file = 'data/uf_param_summary_exp_1.RData')
saveRDS(object = param_summary_exp_2, file = 'data/uf_param_summary_exp_2.RData')
saveRDS(object = param_summary_exp_3, file = 'data/uf_param_summary_exp_3.RData')
```


## Summary of Results Across All Spacing Schedule Levels (Exp. 1)

Table \ref{tab:summary-table-exp1} provides a summary of the results for each spacing schedule. Text within the 'Low Bias' column indicates the number of measurements needed to obtain low bias in the estimation of all day-unit parameters for each spacing schedule. Text within the 'Qualitative Summary' column indicates the number of measurements that obtain the largest improvements in bias and precision across all manipulated nature-of-change values for each spacing schedule. The 'Error Bar Summary' columns indicate the longest error bar lengths obtained for each day-unit parameter of the logistic function using the measurement number listed in the 'Qualitative Summary' column. In looking within each column in the 'Error Bar Summary' columns, each measurement schedule obtains comparable maximum error bar lengths for each day-unit parameter when using the measurement number listed in the 'Qualitative Summary' column. 

Under equal spacing, although nine measurements are needed to obtain low bias in the estimation of all day-unit parameters across all manipulated nature-of-change values, the greatest improvements in bias and precision occur with seven measurements. 
Under time-interval increasing spacing, nine or more measurements are needed to obtain low bias in the estimation of all day-unit parameters across all manipulated nature-of-change values and to obtain the greatest improvements in bias and precision. 

Under time-interval decreasing spacing, nine or more measurements are needed to obtain low bias in the estimation of all day-unit parameters across all manipulated nature-of-change values and to obtain the greatest improvements in bias and precision. 

Under middle-and-extreme spacing, 11 measurements are needed to obtain low bias in the estimation of all day-unit parameters across all manipulated nature-of-change values and the the greatest improvements in bias and precision only occur with 11 measurements.  

```{r summary-table-exp1, echo=F}
#error bar lengths for each spacing schedule
errorbar_lengths_equal <- compute_errorbar_lengths(exp_analytical_days = exp_1_analytical$days, iv_level = 'Equal spacing', num_measurements = 7)$errorbar_length

errorbar_lengths_time_inc_nm9 <- compute_errorbar_lengths(exp_analytical_days = exp_1_analytical$days, iv_level = 'Time-interval increasing', num_measurements = 9)$errorbar_length

errorbar_lengths_time_dec_nm9<- compute_errorbar_lengths(exp_analytical_days = exp_1_analytical$days, iv_level = 'Time-interval decreasing', num_measurements = 9)$errorbar_length

errorbar_lengths_mid_ext_nm9<- compute_errorbar_lengths(exp_analytical_days = exp_1_analytical$days, iv_level = 'Middle-and-extreme spacing', num_measurements = 9)$errorbar_length

#combine vectors into a list 
errorbar_lengths_list <- list('equal' = errorbar_lengths_equal, 
                              'time_inc' = errorbar_lengths_time_inc_nm9, 
                              'time_dec' = errorbar_lengths_time_dec_nm9, 
                              'mid_ext' = errorbar_lengths_mid_ext_nm9)

beta_fixed_errorbar_lengths <- as.numeric(unlist(lapply(X = errorbar_lengths_list, FUN = function(x){return(x[1])})))
gamma_fixed_errorbar_lengths <- as.numeric(unlist(lapply(X = errorbar_lengths_list, FUN = function(x){return(x[2])})))
beta_rand_errorbar_lengths <- as.numeric(unlist(lapply(X = errorbar_lengths_list, FUN = function(x){return(x[3])})))
gamma_rand_errorbar_lengths <- as.numeric(unlist(lapply(X = errorbar_lengths_list, FUN = function(x){return(x[4])})))


summary_table <- data.frame('Spacing Schedule' = c('\\thead[lt]{Equal \\\\ Figure \\ref{fig:exp1_plot_equal}}',
                                                   '\\thead[lt]{Time-interval increasing \\\\ Figure \\ref{fig:exp1_plot_time_inc}}', 
                                                   '\\thead[lt]{Time-interval decreasing \\\\ Figure \\ref{fig:exp1_plot_time_dec}}', 
                                                   '\\thead[lt]{Middle-and-extreme \\\\ Figure \\ref{fig:exp1_plot_time_mid_ext}}'), 
                            'Low Bias' = c('NM $\\ge$ 9', 
                                           'NM $\\ge$ 9', 
                                           'NM $\\ge$ 9', 
                                           'NM = 11'), 
                            'High Precision' = c('No cells', 
                                            'No cells', 
                                            'No cells',
                                            'No cells'), 
                            'Qualitative Summary' = c('Largest improvements in bias and precision with NM = 7', 
                                                      'Largest improvements in bias and precision with NM = 9', 
                                                      'Largest improvements in bias and precision with NM = 9', 
                                                      'Largest improvements in bias and precision with NM = 9'), 
                            
                            '$\\upbeta_{fixed}$' = beta_fixed_errorbar_lengths, 
                            '$\\upgamma_{fixed}$' = gamma_fixed_errorbar_lengths, 
                            '$\\upbeta_{random}$' = beta_rand_errorbar_lengths, 
                            '$\\upgamma_{random}$' = gamma_rand_errorbar_lengths, 
                            
                            
                            check.names = F)

kbl(x = summary_table, format = 'latex',
    linesep = c('\\cmidrule(l{0.25cm}r{0.25cm}){1-8}', '\\cmidrule(l{0.25cm}r{0.25cm}){1-8}', '\\cmidrule(l{0.25cm}r{0.25cm}){1-8}'), 
       longtable = T, booktabs = T, centering = T, escape = F,
    caption = 'Concise Summary of Results Across All Spacing Schedule Levels in Experiment 1', 
   align = c(rep('l', times = 4), rep('c', times = 4))) %>%
     #header
  column_spec(column = 1, width = '4.86cm') %>%
  column_spec(column = 2, width = '2cm') %>%
  column_spec(column = 3, width = '2cm') %>%
  column_spec(column = 4, width = '7cm') %>%
  column_spec(column = 5:8, width = '1cm') %>%
  add_header_above(header = c(' ' = 4, 'Error Bar Summary' = 4)) %>%
  
  #row highlighting 
  row_spec(1, background = "#DFDEDE") %>%

   #footnotes
  footnote(escape = F, threeparttable = T, general_title = '\\\\textit{Note.}\\\\hspace{-1.1pc}',
           general = "`Qualitative Summary' column indicates the number of measurements that obtains the greatest improvements in bias and precision across all day-unit parameters and manipulated nature-of-change values. `Error Bar Summary' columns list the longest error bar lengths that result for each day-unit parameter using the measurement number listed in the `Qualitative Summary' column. Note that error bar lengths were calculated by computing the average length across all manipulated nature-of-change values. Parameter names and population values are as follows: $\\\\upbeta_{fixed}$ = fixed-effect days-to-halfway elevation parameter $\\\\in$ \\\\{80, 180, 280\\\\}; $\\\\upgamma_{fixed}$ = fixed-effect halfway-triquarter delta parameter = 20; $\\\\upbeta_{random}$ = random-effect days-to-halfway elevation parameter = 10; $\\\\upgamma_{random}$ = random-effect halfway-triquarter delta parameter = 4. NM = number of measurements.") %>%
  kable_styling(position = 'left') %>%
  landscape(margin = '2.54cm')

```

```{r summary-table-exp1-nc, echo=F}

param_midpoint_equal <- exp_1_analytical$days %>%
  filter(str_detect(string = measurement_spacing, pattern = 'Equal')) %>%
  group_by(parameter, midpoint) %>%
  summarize(errorbar_length = mean(errorbar_length, digits = 2)) %>%
            #bias = round(mean(estimate) - mean(pop_value), digits = 2)) %>%
  pivot_wider(names_from = midpoint, values_from =  errorbar_length)

#combine vectors into a list 
errorbar_lengths_list <- list('equal' = param_midpoint_equal[[3]], 
                              'time_inc' = param_midpoint_time_inc[[2]], 
                              'time_dec' =  param_midpoint_time_dec[[4]], 
                              'mid_ext' =  param_midpoint_mid_ext[[3]])

beta_fixed_errorbar_lengths <- as.numeric(unlist(lapply(X = errorbar_lengths_list, FUN = function(x){return(x[1])})))
gamma_fixed_errorbar_lengths <- as.numeric(unlist(lapply(X = errorbar_lengths_list, FUN = function(x){return(x[2])})))
beta_rand_errorbar_lengths <- as.numeric(unlist(lapply(X = errorbar_lengths_list, FUN = function(x){return(x[3])})))
gamma_rand_errorbar_lengths <- as.numeric(unlist(lapply(X = errorbar_lengths_list, FUN = function(x){return(x[4])})))


summary_table <- data.frame('Spacing Schedule' = c('\\thead[lt]{Equal \\\\ Figure \\ref{fig:exp1_plot_equal} 
                                                   and Table \\ref{tab:errorbar-equal-nc}}',
                                                   '\\thead[lt]{Time-interval increasing \\\\ Figure \\ref{fig:exp1_plot_time_inc} 
                                                   and Table \\ref{tab:errorbar-time-inc-nc}}', 
                                                   '\\thead[lt]{Time-interval decreasing \\\\ Figure \\ref{fig:exp1_plot_time_dec}
                                                   and Table \\ref{tab:errorbar-time-dec-nc}}', 
                                                   '\\thead[lt]{Middle-and-extreme \\\\ Figure \\ref{fig:exp1_plot_time_mid_ext}
                                                   and Table \\ref{tab:errorbar-mid-ext-nc}}'), 
                            'Optimal Nature-of-Change Value' = c('$\\upbeta_{fixed}$ = 180', 
                                                         '$\\upbeta_{fixed}$ = 80', 
                                                         '$\\upbeta_{fixed}$ = 280', 
                                                         '$\\upbeta_{fixed}$ = 180'), 
                        
                            '$\\upbeta_{fixed}$' = beta_fixed_errorbar_lengths, 
                            '$\\upgamma_{fixed}$' = gamma_fixed_errorbar_lengths, 
                            '$\\upbeta_{random}$' = beta_rand_errorbar_lengths, 
                            '$\\upgamma_{random}$' = gamma_rand_errorbar_lengths, 
                            
                            
                            check.names = F)

kbl(x = summary_table, format = 'latex', digits = 2,
    linesep = c('\\cmidrule(l{0.25cm}r{0.25cm}){1-6}', '\\cmidrule(l{0.25cm}r{0.25cm}){1-6}', '\\cmidrule(l{0.25cm}r{0.25cm}){1-6}'), 
       longtable = T, booktabs = T, centering = T, escape = F,
    caption = 'Nature-of-Change Values That Lead to Highest Modelling Accuracy for Each Spacing Schedule in Experiment 1', 
   align = c(rep('l', times = 1), rep('c', times = 4))) %>%
     #header
    add_header_above(header = c(' ' = 2, 'Error Bar Summary' = 4)) %>%
  column_spec(column = 1, width = '4.86cm') %>%
  column_spec(column = 2, width = '6cm') %>%
  column_spec(column = 3:6, width = '1cm') %>%
    footnote(escape = F, threeparttable = T, general_title = '\\\\textit{Note.}\\\\hspace{-1pc}',
           general = "`Error Bar Summary' lists error bar lengths for each day-unit parameter such that error bar lenghts are computed by taking the average error bar length value across all the number-of-measurement (NM) values (NM $\\\\in$ \\\\{5, 7, 9, 11\\\\}). Parameter names and population values are as follows: $\\\\upbeta_{fixed}$ = fixed-effect days-to-halfway elevation parameter $\\\\in$ \\\\{80, 180, 280\\\\}; $\\\\upgamma_{fixed}$ = fixed-effect halfway-triquarter delta parameter = 20; $\\\\upbeta_{random}$ = random-effect days-to-halfway elevation parameter = 10; $\\\\upgamma_{random}$ = random-effect halfway-triquarter delta parameter = 4.") %>%
  kable_styling(position = 'left') %>%
  landscape(margin = '2.54cm')
```

```{r schedule-nc-plot, echo=F, eval=F}
#log function data 
t <- 0:360
theta <- 3
alpha <- 3.32
beta_80 <- 80
beta_180 <- 180
beta_280 <- 280
gamma <- 20

log_function_80 <- theta + (alpha - theta)/((1 + exp((beta_80 - t)/gamma)))
log_function_180 <- theta + (alpha - theta)/((1 + exp((beta_180 - t)/gamma)))
log_function_280 <- theta + (alpha - theta)/((1 + exp((beta_280 - t)/gamma)))
log_function_180b <- theta + (alpha - theta)/((1 + exp((beta_280 - t)/gamma)))

log_func_wide <- data.frame(cbind(t, log_function_180, log_function_80, log_function_280, log_function_180b)) 
log_func_long <- log_func_wide %>%
  pivot_longer(cols = 2:ncol(log_func_wide), names_to = 'midpoint', values_to = 'curve_value', names_ptypes = factor())

log_func_long$midpoint <-  recode_factor(log_func_long$midpoint,   
                                    'log_function_180' = "atop(bold(A:beta[fixed]==180~With~Equal~Spacing), phantom(randomtextforalignment))",
                                    'log_function_80' = "atop(bold(B:beta[fixed]==80~With~`Time-Interval`~ phantom(randomtextfor)), bold(Increasing~Spacing)~phantom(text~forleftaligniextrattt))",
                                    'log_function_280' = "atop(bold(C:beta[fixed]==280~With~`Time-Interval`~ phantom(randomtextfor)), bold(Decreasing~Spacing)~phantom(text~forleftaligniextratta))",
                                    'log_function_180b' = "atop(bold(D:beta[fixed]==180~With~`Middle-and-`~phantom(text~forleftaligni)), bold(`Extreme`~Spacing)~phantom(text~forleftalandalmorerand))")


#spacing schedule data
num_measurements <- 5
time_period <- 360 
smallest_int_length <- 30
schedules <- c('equal', 'time_inc', 'time_dec', 'mid_ext')

list_out <- unlist(do.call(rbind, pmap(.l = list('num_measurements' = num_measurements, 
               'time_period' = time_period, 
               'smallest_int_length' = smallest_int_length, 
               measurement_spacing = schedules), 
     .f = compute_measurement_schedule))[, 2])

measurement_days_wide <- data.frame(matrix(data = list_out, nrow = 4, ncol = num_measurements, byrow = T, 
       dimnames = list(schedules, sprintf('measurement_day_%d', 1:num_measurements)))) %>%
  rownames_to_column(var = 'schedule')

measurement_days_wide$midpoint <- c('180', '80', '280', '180a')

#add midpoint 
measurement_days_wide$midpoint <-  recode_factor(measurement_days_wide$midpoint,  
                                    '180' = "atop(bold(A:beta[fixed]==180~With~Equal~Spacing), phantom(randomtextforalignment))",
                                    '80' = "atop(bold(B:beta[fixed]==80~With~`Time-Interval`~ phantom(randomtextfor)), bold(Increasing~Spacing)~phantom(text~forleftaligniextrattt))",
                                    '280' = "atop(bold(C:beta[fixed]==280~With~`Time-Interval`~ phantom(randomtextfor)), bold(Decreasing~Spacing)~phantom(text~forleftaligniextratta))",
                                    '180a' = "atop(bold(D:beta[fixed]==180~With~`Middle-and-`~phantom(text~forleftaligni)), bold(`Extreme`~Spacing)~phantom(text~forleftalandalmorerand))")

measurement_days_long <- measurement_days_wide %>% 
  pivot_longer(cols = 2:(num_measurements + 1), names_to = 'measurement_num', values_to = 'day_number') %>%
  mutate_if(.predicate = is.character, .funs = factor)

#add curve values; match log_func_long on midpoint and then add the corresponding curve value 
measurement_days_long <- left_join(x = measurement_days_long, y = log_func_long, by = c('midpoint', 'day_number' = 't'))

#data set containing error bar widths for each parameter under each spacing schedule 
temp <- 5.34

param_midpoint_equal <- exp_1_analytical$days %>%
  filter(str_detect(string = measurement_spacing, pattern = 'Equal')) %>%
  group_by(parameter, midpoint) %>%
  summarize(errorbar_length = mean(errorbar_length, digits = 2)) %>%
            #bias = round(mean(estimate) - mean(pop_value), digits = 2)) %>%
  pivot_wider(names_from = midpoint, values_from =  errorbar_length)


param_midpoint_time_inc <- exp_1_analytical$days %>%
  filter(str_detect(string = measurement_spacing, pattern = 'increasing')) %>%
  group_by(parameter, midpoint) %>%
  summarize(errorbar_length = mean(errorbar_length, digits = 2)) %>%
            #bias = round(mean(estimate) - mean(pop_value), digits = 2)) %>%
  pivot_wider(names_from = midpoint, values_from =  errorbar_length)


param_midpoint_time_dec <- exp_1_analytical$days %>%
  filter(str_detect(string = measurement_spacing, pattern = 'decreasing')) %>%
  group_by(parameter, midpoint) %>%
  summarize(errorbar_length = mean(errorbar_length, digits = 2)) %>%
            #bias = round(mean(estimate) - mean(pop_value), digits = 2)) %>%
  pivot_wider(names_from = midpoint, values_from =  errorbar_length)


param_midpoint_mid_ext <- exp_1_analytical$days %>%
  filter(str_detect(string = measurement_spacing, pattern = 'Middle-and')) %>%
  group_by(parameter, midpoint) %>%
  summarize(errorbar_length = mean(errorbar_length, digits = 2)) %>%
            #bias = round(mean(estimate) - mean(pop_value), digits = 2)) %>%
  pivot_wider(names_from = midpoint, values_from =  errorbar_length)


#combine vectors into a list 
errorbar_lengths_list <- list('equal' = round(param_midpoint_equal[[3]], digits = 2),  
                              'time_inc' = round(param_midpoint_time_inc[[2]], digits = 2), 
                              'time_dec' =  round(param_midpoint_time_dec[[4]], digits = 2), 
                              'mid_ext' =  round(param_midpoint_mid_ext[[3]], digits = 2))

beta_fixed_errorbar_lengths <- as.numeric(unlist(lapply(X = errorbar_lengths_list, FUN = function(x){return(x[1])})))
gamma_fixed_errorbar_lengths <- as.numeric(unlist(lapply(X = errorbar_lengths_list, FUN = function(x){return(x[2])})))
beta_rand_errorbar_lengths <- as.numeric(unlist(lapply(X = errorbar_lengths_list, FUN = function(x){return(x[3])})))
gamma_rand_errorbar_lengths <- as.numeric(unlist(lapply(X = errorbar_lengths_list, FUN = function(x){return(x[4])})))

equation_data <- data.frame(
  midpoint =c(rep("atop(bold(A:beta[fixed]==180~With~Equal~Spacing), phantom(randomtextforalignment))", times = 4), 
               rep("atop(bold(B:beta[fixed]==80~With~`Time-Interval`~ phantom(randomtextfor)), bold(Increasing~Spacing)~phantom(text~forleftaligniextrattt))", times = 4), 
               rep("atop(bold(C:beta[fixed]==280~With~`Time-Interval`~ phantom(randomtextfor)), bold(Decreasing~Spacing)~phantom(text~forleftaligniextratta))", times = 4), 
               rep("atop(bold(D:beta[fixed]==180~With~`Middle-and-`~phantom(text~forleftaligni)), bold(`Extreme`~Spacing)~phantom(text~forleftalandalmorerand))", times = 4)),
  
  label = c(paste("beta[fixed] == ", beta_fixed_errorbar_lengths[1], sep = ''), 
            paste("gamma[fixed] == ", gamma_fixed_errorbar_lengths[1], sep = ''), 
            paste("beta[random] == ", beta_rand_errorbar_lengths[1], sep = ''), 
            paste("gamma[random] == ", gamma_rand_errorbar_lengths[1], sep = ''), 
            
            paste("beta[fixed] == ", beta_fixed_errorbar_lengths[2], sep = ''), 
            paste("gamma[fixed] == ", gamma_fixed_errorbar_lengths[2], sep = ''), 
            paste("beta[random] == ", beta_rand_errorbar_lengths[2], sep = ''), 
            paste("gamma[random] == ", gamma_rand_errorbar_lengths[2], sep = ''), 
            
            paste("beta[fixed] == ", beta_fixed_errorbar_lengths[3], sep = ''), 
            paste("gamma[fixed] == ", gamma_fixed_errorbar_lengths[3], sep = ''), 
            paste("beta[random] == ", beta_rand_errorbar_lengths[3], sep = ''), 
            paste("gamma[random] == ", gamma_rand_errorbar_lengths[3], sep = ''), 
            
            paste("beta[fixed] == ", beta_fixed_errorbar_lengths[4], sep = ''), 
            paste("gamma[fixed] == ", gamma_fixed_errorbar_lengths[4], sep = ''), 
            paste("beta[random] == ", beta_rand_errorbar_lengths[4], sep = ''), 
            paste("gamma[random] == ", gamma_rand_errorbar_lengths[4], sep = '')), 

  x = c(80, 80, 87, 90,
        280, 280, 287, 290, 
        rep(c(80, 80, 87, 90), times = 2)), 
  y = c(rep(c(3.24, 3.20, 3.16, 3.12), times = 4)))


#add optimal spacing midpoint column
midpoint_plot <- ggplot(data = log_func_long, mapping = aes(x = t, y = curve_value)) + 
  geom_line(size = 4) + 
  geom_text(data = equation_data, inherit.aes = F, mapping = aes(x = x, y = y, label = label), parse = T, size = 17.5) + 
  scale_y_continuous(name = 'Curve Value (Likert Units [Scale 1-5])') + 
  geom_point(data = measurement_days_long, aes(x = day_number, y = curve_value), size = 15) +
  facet_wrap_custom( ~ midpoint, scales = "free", ncol = 2, nrow = 2 , dir = 'h',
                     labeller = label_parsed,  

                            scale_overrides = list(
                            scale_override(1,
                              scale_x_continuous(name = 'Measurement Number', 
                                breaks = c(0, 80, 120, 180, 240, 300, 360),
                                limits = c(0, 360))), 
                          
                             scale_override(which = 2,
                              scale_x_continuous(name = 'Measurement Number', 
                                breaks = c(0, 60, 120, 180, 240, 300, 360),
                                limits = c(0, 360))), 
                            
                            scale_override(which = 3,
                              scale_x_continuous(name = 'Measurement Number', 
                                breaks = c(0, 60, 120, 180, 280, 360),
                                limits = c(0, 360))), 
                            
                              
                            scale_override(which = 4,
                              scale_x_continuous(name = 'Measurement Number', 
                                breaks = c(0, 60, 120, 180, 240, 300, 360),
                                limits = c(0, 360))))) +
  
      scale_shape_manual(name = 'Spacing Schedule Measurement Days', values=c(15:18)) + 
                         
  theme_classic(base_family = 'Helvetica') + 
  theme(
      #panel details
      strip.background = element_rect(fill = "white", color = "white"),
      #original text size = 60, 150 for pre-results figures
      strip.text.x = element_text(face = 'bold', hjust = 0, size = 60, margin = unit(c(t = 0, r = 0, b = 1, l = 0), "cm")),

      #axis details
      axis.text = element_text(size = 60, color = 'black'),
      axis.title = element_text(size = 70),
       
      #axis.title.x.bottom = element_markdown(),
      axis.line = element_line(size = 2),
      axis.ticks.length.x = unit(x = 1, units = 'cm'),
      axis.title.x = element_text(margin = unit(c(3, 0, 0, 0), "cm")),
      axis.title.y = element_text(margin = unit(c(t = 0, r = 3, b = 0, l = 0), units = 'cm')),
      axis.ticks = element_line(size = 2, colour = 'black'),
      axis.ticks.length.y =  unit(x = 1, units = 'cm'),

      #legend details
      legend.text = element_text(size = 50),
      legend.margin = margin(unit(c(0, 0, 0, 10), "cm")),
      legend.title = element_text(size = 60),
      legend.key.size = unit(3, 'cm'),
      legend.position = c(0.5, 0.5), 
      legend.direction = 'vertical',
      legend.box.background = element_rect(colour = 'black', size = 3),

      #panel details
      panel.spacing.y = unit(x = 4, units = 'cm')) 

set_panel_size(p = midpoint_plot, height = unit(x = 28, units = 'cm'),
                 width = unit(x = 40, units = 'cm'),
                 file =  'Figures/midpoint_plot.pdf')
```

```{=tex}
\begin{figure}[H]
  \caption{Nature-of-Change Curves That Result in Highest Modelling Accuracy for Each Spacing Schedule in Experiment 1}
  \label{fig:midpoint_plot}
  \includegraphics{Figures/midpoint_plot} 
 \caption*{Note. \textup{Panel A: Nature of change that results in the the highest modelling accuracy with equal spacing, with dots representing the days where measurements are taken when equal spacing is used. Panel B: Nature of change that results in the the highest modelling accuracy with time-interval increasing spacing, with dots representing the days where measurements are taken when time-interval increasing spacing is used. Panel C: Nature of change that results in the the highest modelling accuracy with time-interval decreasing spacing, with dots representing the days where measurements are taken when time-interval decreasing spacing is used. Panel D: Nature of change that results in the the highest modelling accuracy with middle-and-extreme spacing, with dots representing the days where measurements are taken when middle-and-extreme spacing is used.}}
\end{figure}
```


