---
shorttitle        : "Measurement timing"
format          : "pandoc"
header-includes:
  - \usepackage{nccmath}
  - \usepackage{caption}
  - \usepackage{textcomp} #for copyright symbol on title page
  - \usepackage{longtable}
  - \usepackage{makecell}
  - \usepackage[section]{placeins}
  - \usepackage{setspace}
  - \usepackage{biblatex}
  - \usepackage{booktabs}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{xcolor}
  - \usepackage{amsthm} 
  - \usepackage{amsmath} ##needed for argmax
  - \usepackage{bm}  #thicker bold in math 
  - \DeclareMathOperator*{\argmax}{arg\,max}
  - \usepackage{setspace} #needed to doublespace caption text (using \doublespacing)
  - \usepackage[labelfont = {bf, up}]{caption} 
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \usepackage{upgreek}  #required for non-italicized Greek letters
  - \usepackage{subcaption}
  - \captionsetup[figure]{labelfont={normalfont, bf}, singlelinecheck=false, labelsep=newline}
  - \DeclareCaptionFont{figCaptionFont}{\fontfamily{phv}\doublespacing} #sets caption font to sans serif font of Helvetica 
  - \DeclareCaptionFont{figCaptionSize}{\fontsize{11pt}{13.2pt}\selectfont} #set caption font size to footnote 
  - \DeclareCaptionFont{tabCaptionSize}{\small} #caption size for table title
  - \DeclareCaptionFont{figCaptionStyle}{\textup}  #set caption font to non-italicized font  
  - \DeclareCaptionLabelSeparator{captionSep}{\newline} #separates figure label and figure title with required white space
  - \captionsetup[figure]{labelfont={figCaptionStyle, bf}, font = {figCaptionFont,figCaptionSize, figCaptionStyle}, labelsep = captionSep, justification= raggedright}
  - \captionsetup[table]{labelfont={tabCaptionSize, bf}, font = {figCaptionFont, tabCaptionSize, figCaptionStyle}, labelsep = captionSep, justification= raggedright}
  - \newenvironment{helvenv}{\fontfamily{phv}\selectfont}{}
  - \raggedbottom #ensures text starts from top of page and any white space is at the botom

#both are needed to change font type of table footnotes
  - \usepackage{anyfontsize}
  - \AtBeginEnvironment{ThreePartTable}{\fontfamily{phv} \fontsize{10.5pt}{12pt}\selectfont} 
  - \AtBeginEnvironment{tablenotes}{\fontsize{9.5pt}{11.4pt}\selectfont} 

#environment numbering 
  - \setcounter{section}{0} 
  - \makeatletter \renewcommand\thesection{}\renewcommand\thesubsection{\@arabic\c@section.\@arabic\c@subsection} \makeatother

#set table line widths 
  - \setlength\cmidrulewidth{1pt} #line thickness of lines within table and in multi-row headers
  - \setlength\lightrulewidth{1pt} #line thickness of bottom line in header 

  - \newtheorem{theorem}{Theorem}
  - \newtheorem{example}[theorem]{Example}
  - \renewcommand\theadfont{} #sets cell font to be same as table font 
  
  #set figure title text
  - \newcommand{\figurefootnote}{\raggedright\linespread{2}\fontfamily{phv}\fontsize{9.5pt}{11.4pt}\selectfont \textit{Note. }}
  
  #modifies heading levels of 4-5 to follow apa7
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}
    
    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother
  
  
author: 
  - name          : "Sebastian Sciarra "
    affiliation   : "1"
    corresponding : yes    
    email         : "ssciarra@uoguelph.ca"
affiliation: 
  - id            : "1"
    institution   : "University of Guelph"
keywords          : "measurement timing, nonlinear "
wordcount         : "5554 words"
floatsintext      : yes
linkcolor         : blue
figsintext        : yes 
figurelist        : no
tablelist         : no
footnotelist      : no
numbersections    : yes
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa7"
csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
classoption       : "man"
output            : papaja::apa6_pdf
keep_tex: true
editor_options: 
  markdown: 
    wrap: 72
bibliography: dissertation_references.bib
---
```{r package_loading_2, include=F}
#load packages
library(easypackages)
packages <- c('devtools','tidyverse', 'RColorBrewer', 'parallel', 'data.table', 'kableExtra', 'ggtext', 'egg', 'nonlinSims','papaja', 
              'ggbrace', 'cowplot')
libraries(packages)
load_all()
```

```{r knitting_setup_2, echo=F, message = F, warning = F}
#import raw data files (needed for computing variances)
exp_1_raw <- convert_raw_var_to_sd(raw_data = read_csv('data/exp_1_data.csv')) %>%
  mutate_at(.vars = c("number_measurements", "measurement_spacing", "midpoint"), factor)
  
exp_2_raw <-convert_raw_var_to_sd(raw_data = read_csv('data/exp_2_data.csv')) %>%
  mutate_at(.vars = c("number_measurements", "measurement_spacing", "sample_size"), factor)

exp_3_raw <-convert_raw_var_to_sd(raw_data = read_csv('data/exp_3_data.csv')) %>%
  mutate_at(.vars = c("number_measurements", "time_structuredness", "sample_size"), factor)

#unfiltered data 
param_summary_exp_1 <- readRDS(file = 'data/uf_param_summary_exp_1.RData')
param_summary_exp_2 <- readRDS(file = 'data/uf_param_summary_exp_2.RData')
param_summary_exp_3 <- readRDS(file = 'data/uf_param_summary_exp_3.RData')

#create analytical versions of summary data + converts vars to sds
exp_1_analytical <- generate_likert_days_data_sets(summary_data = param_summary_exp_1, exp_num = '1')
exp_2_analytical <- generate_likert_days_data_sets(summary_data = param_summary_exp_2, exp_num = '2')
exp_3_analytical <- generate_likert_days_data_sets(summary_data = param_summary_exp_3, exp_num = '3')

combined_analytical_exp_1 <- rbind(exp_1_analytical$likert, exp_1_analytical$days)
combined_analytical_exp_2 <- rbind(exp_2_analytical$likert, exp_2_analytical$days)
combined_analytical_exp_3 <- rbind(exp_3_analytical$likert, exp_3_analytical$days)

#create condition summary data sets 
cond_summary_exp_1 <- compute_condition_summary(param_summary_data = combined_analytical_exp_1, facet_var = 'measurement_spacing', 
                          ind_vars = c('number_measurements', 'measurement_spacing', 'midpoint'))
cond_summary_exp_2 <- compute_condition_summary(param_summary_data = combined_analytical_exp_2, facet_var = 'measurement_spacing', 
                  ind_vars = c('number_measurements', 'measurement_spacing', 'sample_size'))

cond_summary_exp_3 <- compute_condition_summary(param_summary_data = combined_analytical_exp_3, facet_var = 'time_structuredness', 
                          ind_vars = c('number_measurements', 'sample_size', 'time_structuredness'))
```

```{r pre_knitting_setup_unfiltered_2, echo=F, eval=F, include=F}
#code should be computed before knitting to decrease knitting time 
#load data from experiments
exp_1 <- read_csv(file = 'data/exp_1_data.csv') %>% filter(code == 0)
exp_2 <- read_csv(file = 'data/exp_2_data.csv')
exp_3 <- read_csv(file = 'data/exp_3_data.csv')

#compute parameter summary statistics  
exp_1_long <- exp_1 %>%
    filter(code == 0) %>%
    #place parameter estimates in one column
    pivot_longer(cols = contains(c('theta', 'alpha', 'beta', 'gamma', 'epsilon')),
                 names_to = 'parameter', values_to = 'estimate') %>%
    filter(parameter == 'beta_fixed') %>%
    mutate(pop_value = midpoint)

exp_1_ordered <- order_param_spacing_levels(data = exp_1_long)

exp_1_ordered %>%
      #compute statistics for each parameter for each experimental variable
      group_by(parameter, .dots = locate_ivs(exp_1_ordered)) %>%
      summarize(
       lower_ci = compute_middle_95_estimate(param_data = estimate)[1],
       upper_ci = compute_middle_95_estimate(param_data = estimate)[2])

compute_parameter_summary(data = exp_1, exp_num = '1')

param_summary_exp_1 <- compute_parameter_summary(data = exp_1, exp_num = 1)
param_summary_exp_2 <- compute_parameter_summary(data = exp_2, exp_num = 2)
param_summary_exp_3 <- compute_parameter_summary(data = exp_3, exp_num = 3)

#necessary factor conversions 
param_summary_exp_1$number_measurements <- factor(param_summary_exp_1$number_measurements, levels = c(5, 7, 9,11))
param_summary_exp_1$midpoint <- factor(param_summary_exp_1$midpoint, levels = c(80, 180,280))

param_summary_exp_2$number_measurements <- factor(param_summary_exp_2$number_measurements, levels = c(5, 7, 9,11))
param_summary_exp_2$sample_size <- factor(param_summary_exp_2$sample_size, levels = c(30, 50, 100, 200, 500, 1000))

param_summary_exp_3$number_measurements <- factor(param_summary_exp_3$number_measurements, levels = c(5, 7, 9,11))
param_summary_exp_3$sample_size <- factor(param_summary_exp_3$sample_size, levels = c(30, 50, 100, 200, 500, 1000))

#write data sets 
#save parameter summary files as RData files so that metadata are correctly stored (e.g., factor levels, variable types)
saveRDS(object = param_summary_exp_1, file = 'data/uf_param_summary_exp_1.RData')
saveRDS(object = param_summary_exp_2, file = 'data/uf_param_summary_exp_2.RData')
saveRDS(object = param_summary_exp_3, file = 'data/uf_param_summary_exp_3.RData')
```



```{=tex}
\newpage
\vspace*{-\topskip}
\vspace*{\fill}
\nointerlineskip
```
```{=tex}
\begin{titlepage}
  \begin{center}
    \vspace*{3cm}
    
  \textbf{Is Timing Everything? Measurement Timing and the Ability to Accurately Model Longitudinal Data}
    
  \vspace{2cm} 
    by \\ Sebastian Sciarra 
    
      
  \vspace{2cm} 
   In partial fulfilment of requirements \\ 
   for the degree of \\
   Doctor of Philosophy \\ 
   in \\ 
   Psychology
    

  \vspace{2cm} 
    Guelph, Ontario, Canada \\ 
    \textcopyright \text{ Sebastian Sciarra, September 2022}

  
  \end{center}
\end{titlepage}
```

```{=tex}
\newpage
\vspace*{-\topskip}
\vspace*{\fill}
\nointerlineskip
```

# Supplementary Appendix
## Appendix A: Procedure for Generating Measurement Schedules in Measurement Spacing Cells {.unnumbered}

Given that no procedure existed (to my knowledge) for creating
measurement schedules, I devised a method for generating measurement
schedules for the four spacing conditions (equal, time-interval
increasing, time-interval decreasing, and middle-and-extreme spacing).
For each measurement spacing conditions across all measurement number
levels, a two-step procedure was employed to generate measurement
schedules in Experiments 2--3. At a broad level, the first step involved
computing setup variables and the second step computed the interval
lengths.

### Appendix A1: Procedure for calculating measurement schedules with equal spacing {.unnumbered}

Figure \@ref{fig:equal_spacing_diagram} shows how the two-step procedure
was implemented to construct a measurement schedule with equal spacing
and five measurements. In the first step, the number of intervals ($NI$)
was computed by subtracting one from the number of measurements ($NM$),
giving five measurements ($NM = 5$) and four intervals ($NI = 4$). In
the second step, interval lengths were calculated by dividing the length
of the measurement period ($MP$) by the number of intervals ($NI$),
yielding an interval length of 90 days
($\frac{MP}{NI} = \frac{360}{4} = 90$).

\blandscape

```{=tex}
\begin{figure}[H]
  \caption{Procedure for Generating Equal Measurement Spacing Schedules}
  \label{fig:equal_spacing_diagram}
  \includegraphics{Figures/equal_spacing_diagram} \hfill{}
  \caption*{Note. \textup{}}
\end{figure}
```
\elandscape

### Appendix A2: Procedure for calculating measurement schedules with time-interval increasing spacing

Figure \@ref{fig:time_inc_diagram} shows how the two-step procedure was
used to calculate the interval lengths for measurement schedules defined
by time-interval increasing spacing with five measurements. In the first
step, the number of intervals was determined by subtracting one from the
number of measurements, yielding a value of four for the number of
intervals ($NI = NM - 1 = 5 - 1 = 4$). Importantly, the length of each
interval increased by a constant value $c$ over time as shown below in
Equation \ref{eq:time-inc-length}:

```{=tex}
\begin{align}
\text{Interval length} = x + \#IN(c)
(\#eq:time-inc-length)
\end{align}
```
\noindent where $\#IN$ represents the interval number in increasing
order such that
$\#IN \in \{0, ..., \text{number of intervals (NI)} - 1\}$. In the
second step, the constant value by which interval lengths increased
($c$) was computed by first subtracting the smallest interval length
from each interval (i.e., $x = 36$ days) from the measurement period
($MP$), yielding 216 remaining days
($N_{remain} = MP - NIx = 360 - 4(36) = 216$). The number of remaining
days then had to be divided across the constant interval lengths.
Because each interval increased by some constant value ($c$ after each
measurement point, the total number of constant-value interval lengths
was obtained by computing the following sum in Equation
\ref{eq:time-sum-constants}:

```{=tex}
\begin{align}
\text{Number constant intervals} = \sum^{\#IN}_{i = 0} i.
(\#eq:time-sum-constants)
\end{align}
```
\noindent With $\#IN = 3$, the number of constant intervals was 6, and
so the constant value was obtained by using Equation
\ref{eq:constant-length} below:

```{=tex}
\begin{align}
\text{Number constant intervals} = \frac{N_{remain}}{\sum^{\#IN}_{i = 0} i},
(\#eq:constant-length)
\end{align}
```
\noindent giving a length of 36 days for the constant value
($c = \frac{216}{6} = 36$ days). Having computed the value for $c$, the
following interval lengths were obtained:

-   $i_{1} = x + \#IN(c) = 36 + 0(36)$ = 36 days
-   $i_{2} = x + \#IN(c) = 36 + 1(36)$ = 72 days
-   $i_{3} = x + \#IN(c) = 36 + 2(36)$ = 108 days
-   $i_{4} = x + \#IN(c) = 36 + 3(36)$ = 144 days

\blandscape

```{=tex}
\begin{figure}[H]
  \caption{Procedure for Generating Time-Interval Increasing Measurement Spacing Schedules}
  \label{fig:time_inc_diagram}
  \includegraphics{Figures/time_inc_diagram} \hfill{}
  \caption*{Note. \textup{}}
\end{figure}
```
\elandscape

### Appendix A3: Procedure for calculating measurement schedules with time-interval decreasing spacing {.unnumbered}

Figure \@ref{fig:time_dec_diagram} shows how the two-step procedure was
used to calculate the interval lengths for measurement schedules defined
by time-interval decreasing spacing with five measurements. In the first
step, the number of intervals was determined by subtracting one from the
number of measurements, yielding a value of four for the number of
intervals ($NI = NM - 1 = 5 - 1 = 4$). Importantly, the length of each
interval decreased by a constant value $c$ over time as shown below in
Equation \ref{eq:time-dec-length}:

```{=tex}
\begin{align}
\text{Interval length} = x + \#INT(c)
(\#eq:time-dec-length)
\end{align}
```
\noindent where $\#IN$ represents the interval number in decreasing
order such that
$\#IN \in \{\text{number of intervals (NI)} - 1, ... , 0\}$. In the
second step, the constant value by which interval lengths decreased
($c$) was computed by first subtracting the smallest interval length
from each interval (i.e., $x = 36$ days) from the measurement period
($MP$), yielding 216 remaining days
($N_{remain} = MP - NIx = 360 - 4(36) = 216$). The number of remaining
days then had to be divided across the constant interval lengths.
Because each interval decreased by some constant value ($c$ after each
measurement point, the total number of constant-value interval lengths
was obtained by computing the following sum in Equation
\ref{eq:dec-sum-constants}:

```{=tex}
\begin{align}
\text{Number constant intervals} = \sum_{\#IN}^{i = 0} i.
(\#eq:dec-sum-constants)
\end{align}
```
\noindent With $\#IN = 3$, the number of constant intervals was 6, and
so the constant value was obtained by using Equation
\ref{eq:constant-length-2} below:

```{=tex}
\begin{align}
\text{Number constant intervals} = \frac{N_{remain}}{\sum^{\#IN}_{i = 0} i},
(\#eq:constant-length-2)
\end{align}
```
\noindent giving a length of 36 days for the constant value
($c = \frac{216}{6} = 36$ days). Having computed the value for $c$, the
following interval lengths were obtained:

-   $i_{1} = x + \#IN(c) = 36 + 3(36)$ = 144 days
-   $i_{4} = x + \#IN(c) = 36 + 0(36)$ = 36 days
-   $i_{3} = x + \#IN(c) = 36 + 1(36)$ = 72 days
-   $i_{2} = x + \#IN(c) = 36 + 2(36)$ = 108 days

\blandscape

```{=tex}
\begin{figure}[H]
  \caption{Procedure for Generating Time-Interval Decreasing Measurement Spacing Schedules}
  \label{fig:time_dec_diagram}
  \includegraphics{Figures/time_dec_diagram} \hfill{}
  \caption*{Note. \textup{}}
\end{figure}
```
\elandscape

### Appendix A4: Procedure for calculating measurement schedules with middle-and-extreme spacing {.unnumbered}

Figure \@ref{fig:mid_ext_diagram} shows how the two-step procedure was
used to calculate the interval lengths for measurement schedules defined
by middle-and-extreme spacing with five measurements. In the first step,
the number of intervals was determined by subtracting one from the
number of measurements, yielding a value of four for the number of
intervals ($NI = NM - 1 = 5 - 1 = 4$)... 

\blandscape

```{=tex}
\begin{figure}[H]
  \caption{Procedure for Generating Time-Interval Decreasing Measurement Spacing Schedules}
  \label{fig:mid_ext_diagram}
  \includegraphics{Figures/mid_ext_diagram} \hfill{}
  \caption*{Note. \textup{}}
\end{figure}
```
\elandscape

## Appendix B: Convergence rates {#appendix-a-convergence-rates}

\newpage

```{r convergence-rates, echo=F, warning=F}
exp_1_conv <- generate_conv_success_data(condition_data = cond_summary_exp_1, first_col = 'measurement_spacing', second_col = 'number_measurements', wide_var = 'midpoint', exp_num = 1, recode_var = 'measurement_spacing')

exp_2_conv <- generate_conv_success_data(condition_data = cond_summary_exp_2, first_col = 'measurement_spacing', second_col = 'number_measurements', wide_var = 'sample_size', exp_num = 2, recode_var = 'measurement_spacing')

exp_3_conv <- generate_conv_success_data(condition_data = cond_summary_exp_3, first_col = 'time_structuredness', second_col = 'number_measurements', wide_var = 'sample_size', exp_num = 3, recode_var = 'time_structuredness')
```

\newpage

```{r conv-exp-1, echo=F}
print_conv_table(table_ready_data = exp_1_conv, 
                 caption_name = 'Convergence Success in Experiment 1', 
                 col_header_name = c('Days to halfway elevation'), 
                 IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
                 column_names = c('80', '180', '280'))
```

\newpage

```{r conv-exp-2, echo=F}
print_conv_table(table_ready_data = exp_2_conv, 
                 caption_name = 'Convergence Success in Experiment 2', 
                 col_header_name = c('Sample size (\\\\textit{N})'), 
                 IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
                 column_names = c('30', '50', '100', '200', '500', '1000'))
```

\newpage

```{r conv-exp-3, echo=F}
print_conv_table(table_ready_data = exp_3_conv, 
                 caption_name = 'Convergence Success in Experiment 3', 
                 col_header_name = c('Sample size (\\\\textit{N})'), 
                 IV_names =  c('Time Structuredness', 'Number of Measurements'), 
                 column_names = c('30', '50', '100', '200', '500', '1000'))
```

## Appendix C: Complete Versions of Parameter Estimation Plots (Day- and Likert-Unit Parameters) {#appendix-c}

### Experiment 1 
### Equal Spacing

```{=tex}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Day-Unit Parameters With Equal Spacing in Experiment 1}
  \label{fig:exp1_plot_equal_app}
  \includegraphics{Figures/exp1_plot_days_equal spacing} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Likert-Unit Parameters With Equal Spacing in Experiment 1}
  \label{fig:exp1_plot_equal_app}
  \includegraphics{Figures/exp1_plot_likert_equal spacing} 
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption*{Note. \textup{Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Panels E--F show the parameter estimation plots for the fixed- and random-effect baseline parameters ($\uptheta_{fixed}$ and $\uptheta_{random}$, respectively). Panels G--H show the parameter estimation plots for the fixed- and random-effect maximal elevation parameters ($\upalpha_{fixed}$ and $\upalpha_{random}$, respectively). Panel I shows the parameter estimation plot for the error parameter ($\upepsilon$). Blue horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, $\upgamma_{random}$ = 4.00, $\uptheta_{fixed}$ = 3.00, $\uptheta_{random}$ = 0.05, $\upalpha_{fixed}$ = 3.32, $\upalpha_{random}$ = 0.05, $\upepsilon$ = 0.05. Gray bands indicate the acceptable $\pm 10\%$ margin of error for each parameter and unfilled dots indicate cells with average parameter estimates outside of the margin. Error bars represent the middle 95\% of estimated values, with light blue error bars indicating cells with variability greater than 20\% of the parameter's population value. I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20\% of the parameter's population value as indicative of low-precision estimation. Note that random-effect parameter units are in standard deviation units. Importantly, across all population values used for the fixed-effect days-to-halfway elevation parameter ($\upbeta_{fixed}$), the acceptable amount of bias and precision was based on a population value of 180. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:omega-exp1-equal} for $\upomega^2$ effect size values.}}
\end{figure}
```

### Time-Interval Increasing Spacing

```{=tex}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Day-Unit Parameters With Time-Interval Increasing Spacing in Experiment 1}
  \label{fig:exp1_plot_time_inc_app}
  \includegraphics{Figures/exp1_plot_days_time-interval increasing} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Likert-Unit Parameters With Time-Interval Increasing Spacing in Experiment 1}
  \label{fig:exp1_plot_time_inc_app}
  \includegraphics{Figures/exp1_plot_likert_time-interval increasing} 
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption*{Note. \textup{Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Panels E--F show the parameter estimation plots for the fixed- and random-effect baseline parameters ($\uptheta_{fixed}$ and $\uptheta_{random}$, respectively). Panels G--H show the parameter estimation plots for the fixed- and random-effect maximal elevation parameters ($\upalpha_{fixed}$ and $\upalpha_{random}$, respectively). Panel I shows the parameter estimation plot for the error parameter ($\upepsilon$). Blue horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, $\upgamma_{random}$ = 4.00, $\uptheta_{fixed}$ = 3.00, $\uptheta_{random}$ = 0.05, $\upalpha_{fixed}$ = 3.32, $\upalpha_{random}$ = 0.05, $\upepsilon$ = 0.05. Gray bands indicate the acceptable $\pm 10\%$ margin of error for each parameter and unfilled dots indicate cells with average parameter estimates outside of the margin. Error bars represent the middle 95\% of estimated values, with light blue error bars indicating cells with variability greater than 20\% of the parameter's population value. I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20\% of the parameter's population value as indicative of low-precision estimation. Note that random-effect parameter units are in standard deviation units. Importantly, across all population values used for the fixed-effect days-to-halfway elevation parameter ($\upbeta_{fixed}$), the acceptable amount of bias and precision was based on a population value of 180. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:omega-exp1-equal} for $\upomega^2$ effect size values.}}
\end{figure}
```

### Time-Interval Decreasing Spacing

```{=tex}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Day-Unit Parameters With Time-Interval Decreasing Spacing in Experiment 1}
  \label{fig:exp1_plot_time_dec_app}
  \includegraphics{Figures/exp1_plot_days_time-interval decreasing} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Likert-Unit Parameters With Time-Interval Decreasing Spacing in Experiment 1}
  \label{fig:exp1_plot_time_dec_app}
  \includegraphics{Figures/exp1_plot_likert_time-interval decreasing} 
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption*{Note. \textup{Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Panels E--F show the parameter estimation plots for the fixed- and random-effect baseline parameters ($\uptheta_{fixed}$ and $\uptheta_{random}$, respectively). Panels G--H show the parameter estimation plots for the fixed- and random-effect maximal elevation parameters ($\upalpha_{fixed}$ and $\upalpha_{random}$, respectively). Panel I shows the parameter estimation plot for the error parameter ($\upepsilon$). Blue horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, $\upgamma_{random}$ = 4.00, $\uptheta_{fixed}$ = 3.00, $\uptheta_{random}$ = 0.05, $\upalpha_{fixed}$ = 3.32, $\upalpha_{random}$ = 0.05, $\upepsilon$ = 0.05. Gray bands indicate the acceptable $\pm 10\%$ margin of error for each parameter and unfilled dots indicate cells with average parameter estimates outside of the margin. Error bars represent the middle 95\% of estimated values, with light blue error bars indicating cells with variability greater than 20\% of the parameter's population value. I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20\% of the parameter's population value as indicative of low-precision estimation. Note that random-effect parameter units are in standard deviation units. Importantly, across all population values used for the fixed-effect days-to-halfway elevation parameter ($\upbeta_{fixed}$), the acceptable amount of bias and precision was based on a population value of 180. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:omega-exp1-equal} for $\upomega^2$ effect size values.}}
\end{figure}
```

### Middle-and-Extreme Spacing

```{=tex}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Day-Unit Parameters With Middle-and-Extreme Spacing in Experiment 1}
  \label{fig:exp1_plot_time_mid_ext_app}
  \includegraphics{Figures/exp1_plot_days_middle-and-extreme spacing} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Likert-Unit Parameters With Middle-and-Extreme Spacing in Experiment 1}
  \label{fig:exp1_plot_time_mid_ext_app}
  \includegraphics{Figures/exp1_plot_likert_middle-and-extreme spacing} 
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption*{Note. \textup{Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Panels E--F show the parameter estimation plots for the fixed- and random-effect baseline parameters ($\uptheta_{fixed}$ and $\uptheta_{random}$, respectively). Panels G--H show the parameter estimation plots for the fixed- and random-effect maximal elevation parameters ($\upalpha_{fixed}$ and $\upalpha_{random}$, respectively). Panel I shows the parameter estimation plot for the error parameter ($\upepsilon$). Blue horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, $\upgamma_{random}$ = 4.00, $\uptheta_{fixed}$ = 3.00, $\uptheta_{random}$ = 0.05, $\upalpha_{fixed}$ = 3.32, $\upalpha_{random}$ = 0.05, $\upepsilon$ = 0.05. Gray bands indicate the acceptable $\pm 10\%$ margin of error for each parameter and unfilled dots indicate cells with average parameter estimates outside of the margin. Error bars represent the middle 95\% of estimated values, with light blue error bars indicating cells with variability greater than 20\% of the parameter's population value. I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20\% of the parameter's population value as indicative of low-precision estimation. Note that random-effect parameter units are in standard deviation units. Importantly, across all population values used for the fixed-effect days-to-halfway elevation parameter ($\upbeta_{fixed}$), the acceptable amount of bias and precision was based on a population value of 180. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:omega-exp1-equal} for $\upomega^2$ effect size values.}}
\end{figure}
```

### Experiment 2 
### Equal Spacing

```{=tex}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Day-Unit Parameters With Equal Spacing in Experiment 2}
  \label{fig:exp1_plot_equal_app}
  \includegraphics{Figures/exp2_plot_days_equal spacing} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Likert-Unit Parameters With Equal Spacing in Experiment 2}
  \label{fig:exp1_plot_equal_app}
  \includegraphics{Figures/exp2_plot_likert_equal spacing} 
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption*{Note. \textup{Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Panels E--F show the parameter estimation plots for the fixed- and random-effect baseline parameters ($\uptheta_{fixed}$ and $\uptheta_{random}$, respectively). Panels G--H show the parameter estimation plots for the fixed- and random-effect maximal elevation parameters ($\upalpha_{fixed}$ and $\upalpha_{random}$, respectively). Panel I shows the parameter estimation plot for the error parameter ($\upepsilon$). Blue horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, $\upgamma_{random}$ = 4.00, $\uptheta_{fixed}$ = 3.00, $\uptheta_{random}$ = 0.05, $\upalpha_{fixed}$ = 3.32, $\upalpha_{random}$ = 0.05, $\upepsilon$ = 0.05. Gray bands indicate the acceptable $\pm 10\%$ margin of error for each parameter and unfilled dots indicate cells with average parameter estimates outside of the margin. Error bars represent the middle 95\% of estimated values, with light blue error bars indicating cells with variability greater than 20\% of the parameter's population value. I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20\% of the parameter's population value as indicative of low-precision estimation. Note that random-effect parameter units are in standard deviation units. See Table \ref{tab:exp1-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:omega-exp2-equal} for $\upomega^2$ effect size values.}}
\end{figure}
```


### Time-Interval Increasing Spacing

```{=tex}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Day-Unit Parameters With Time-Interval Increasing Spacing in Experiment 2}
  \label{fig:exp2_plot_time_inc_app}
  \includegraphics{Figures/exp2_plot_days_time-interval increasing} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Likert-Unit Parameters With Time-Interval Increasing Spacing in Experiment 2}
  \label{fig:exp2_plot_time_inc_app}
  \includegraphics{Figures/exp2_plot_likert_time-interval increasing} 
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption*{Note. \textup{Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Panels E--F show the parameter estimation plots for the fixed- and random-effect baseline parameters ($\uptheta_{fixed}$ and $\uptheta_{random}$, respectively). Panels G--H show the parameter estimation plots for the fixed- and random-effect maximal elevation parameters ($\upalpha_{fixed}$ and $\upalpha_{random}$, respectively). Panel I shows the parameter estimation plot for the error parameter ($\upepsilon$). Blue horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, $\upgamma_{random}$ = 4.00, $\uptheta_{fixed}$ = 3.00, $\uptheta_{random}$ = 0.05, $\upalpha_{fixed}$ = 3.32, $\upalpha_{random}$ = 0.05, $\upepsilon$ = 0.05. Gray bands indicate the acceptable $\pm 10\%$ margin of error for each parameter and unfilled dots indicate cells with average parameter estimates outside of the margin. Error bars represent the middle 95\% of estimated values, with light blue error bars indicating cells with variability greater than 20\% of the parameter's population value. I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20\% of the parameter's population value as indicative of low-precision estimation. Note that random-effect parameter units are in standard deviation units. See Table \ref{tab:exp2-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:omega-exp2-time-inc} for $\upomega^2$ effect size values.}}
\end{figure}
```

### Time-Interval Decreasing Spacing

```{=tex}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Day-Unit Parameters With Time-Interval Decreasing Spacing in Experiment 2}
  \label{fig:exp2_plot_time_dec_app}
  \includegraphics{Figures/exp2_plot_days_time-interval decreasing} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Likert-Unit Parameters With Time-Interval Decreasing Spacing in Experiment 2}
  \label{fig:exp2_plot_time_dec_app}
  \includegraphics{Figures/exp2_plot_likert_time-interval decreasing} 
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption*{Note. \textup{Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Panels E--F show the parameter estimation plots for the fixed- and random-effect baseline parameters ($\uptheta_{fixed}$ and $\uptheta_{random}$, respectively). Panels G--H show the parameter estimation plots for the fixed- and random-effect maximal elevation parameters ($\upalpha_{fixed}$ and $\upalpha_{random}$, respectively). Panel I shows the parameter estimation plot for the error parameter ($\upepsilon$). Blue horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, $\upgamma_{random}$ = 4.00, $\uptheta_{fixed}$ = 3.00, $\uptheta_{random}$ = 0.05, $\upalpha_{fixed}$ = 3.32, $\upalpha_{random}$ = 0.05, $\upepsilon$ = 0.05. Gray bands indicate the acceptable $\pm 10\%$ margin of error for each parameter and unfilled dots indicate cells with average parameter estimates outside of the margin. Error bars represent the middle 95\% of estimated values, with light blue error bars indicating cells with variability greater than 20\% of the parameter's population value. I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20\% of the parameter's population value as indicative of low-precision estimation. Note that random-effect parameter units are in standard deviation units. See Table \ref{tab:exp2-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:omega-exp2-time-inc} for $\upomega^2$ effect size values.}}
\end{figure}
```
### Middle-and-Extreme Spacing

```{=tex}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Day-Unit Parameters With Middle-and-Extreme Spacing in Experiment 2}
  \label{fig:exp2_plot_time_mid_ext_app}
  \includegraphics{Figures/exp2_plot_days_middle-and-extreme spacing} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Likert-Unit Parameters With Middle-and-Extreme Spacing in Experiment 2}
  \label{fig:exp2_plot_time_mid_ext_app}
  \includegraphics{Figures/exp2_plot_likert_middle-and-extreme spacing} 
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption*{Note. \textup{Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Panels E--F show the parameter estimation plots for the fixed- and random-effect baseline parameters ($\uptheta_{fixed}$ and $\uptheta_{random}$, respectively). Panels G--H show the parameter estimation plots for the fixed- and random-effect maximal elevation parameters ($\upalpha_{fixed}$ and $\upalpha_{random}$, respectively). Panel I shows the parameter estimation plot for the error parameter ($\upepsilon$). Blue horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, $\upgamma_{random}$ = 4.00, $\uptheta_{fixed}$ = 3.00, $\uptheta_{random}$ = 0.05, $\upalpha_{fixed}$ = 3.32, $\upalpha_{random}$ = 0.05, $\upepsilon$ = 0.05. Gray bands indicate the acceptable $\pm 10\%$ margin of error for each parameter and unfilled dots indicate cells with average parameter estimates outside of the margin. Error bars represent the middle 95\% of estimated values, with light blue error bars indicating cells with variability greater than 20\% of the parameter's population value. I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20\% of the parameter's population value as indicative of low-precision estimation. Note that random-effect parameter units are in standard deviation units. Importantly, across all population values used for the fixed-effect days-to-halfway elevation parameter ($\upbeta_{fixed}$), the acceptable amount of bias and precision was based on a population value of 180. See Table \ref{tab:exp2-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:omega-exp2-mid-ext} for $\upomega^2$ effect size values.}}
\end{figure}
```
### Experiment 3
### Time-Structured Data 

```{=tex}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Day-Unit Parameters With Time-Structured Data in Experiment 3}
  \label{fig:exp3_plot_time_struc_app}
  \includegraphics{Figures/exp3_plot_days_time structured} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Likert-Unit Parameters With Time-Structured Data in Experiment 3}
  \label{fig:exp3_plot_time_struc_app}
  \includegraphics{Figures/exp3_plot_likert_time structured} 
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption*{Note. \textup{Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Panels E--F show the parameter estimation plots for the fixed- and random-effect baseline parameters ($\uptheta_{fixed}$ and $\uptheta_{random}$, respectively). Panels G--H show the parameter estimation plots for the fixed- and random-effect maximal elevation parameters ($\upalpha_{fixed}$ and $\upalpha_{random}$, respectively). Panel I shows the parameter estimation plot for the error parameter ($\upepsilon$). Blue horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, $\upgamma_{random}$ = 4.00, $\uptheta_{fixed}$ = 3.00, $\uptheta_{random}$ = 0.05, $\upalpha_{fixed}$ = 3.32, $\upalpha_{random}$ = 0.05, $\upepsilon$ = 0.05. Gray bands indicate the acceptable $\pm 10\%$ margin of error for each parameter and unfilled dots indicate cells with average parameter estimates outside of the margin. Error bars represent the middle 95\% of estimated values, with light blue error bars indicating cells with variability greater than 20\% of the parameter's population value. I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20\% of the parameter's population value as indicative of low-precision estimation. Note that random-effect parameter units are in standard deviation units. See Table \ref{tab:exp3-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:omega-exp3-time-structured} for $\upomega^2$ effect size values.}}
\end{figure}
```

### Time-Untructured Data (Fast Response Rate)
```{=tex}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Day-Unit Parameters With Time-Unstructured Data (Fast Response Rate) in Experiment 3}
  \label{fig:exp3_plot_fast_resp_app}
  \includegraphics{Figures/exp3_plot_days_time unstructured (fast response)} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Likert-Unit Parameters With Time-Unstructured Data (Fast Response Rate) in Experiment 3}
  \label{fig:exp3_plot_fast_resp_app}
  \includegraphics{Figures/exp3_plot_likert_time unstructured (fast response)} 
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption*{Note. \textup{Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Panels E--F show the parameter estimation plots for the fixed- and random-effect baseline parameters ($\uptheta_{fixed}$ and $\uptheta_{random}$, respectively). Panels G--H show the parameter estimation plots for the fixed- and random-effect maximal elevation parameters ($\upalpha_{fixed}$ and $\upalpha_{random}$, respectively). Panel I shows the parameter estimation plot for the error parameter ($\upepsilon$). Blue horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, $\upgamma_{random}$ = 4.00, $\uptheta_{fixed}$ = 3.00, $\uptheta_{random}$ = 0.05, $\upalpha_{fixed}$ = 3.32, $\upalpha_{random}$ = 0.05, $\upepsilon$ = 0.05. Gray bands indicate the acceptable $\pm 10\%$ margin of error for each parameter and unfilled dots indicate cells with average parameter estimates outside of the margin. Error bars represent the middle 95\% of estimated values, with light blue error bars indicating cells with variability greater than 20\% of the parameter's population value. I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20\% of the parameter's population value as indicative of low-precision estimation. Note that random-effect parameter units are in standard deviation units. See Table \ref{tab:exp3-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:omega-exp3-fast-response} for $\upomega^2$ effect size values.}}
\end{figure}
```

### Time-Untructured Data (Slow Response Rate)

```{=tex}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Day-Unit Parameters With Time-Unstructured Data (Slow Response Rate) in Experiment 3}
  \label{fig:exp3_plot_slow_resp_app}
  \includegraphics{Figures/exp3_plot_days_time unstructured (slow response)} \hfill{}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption{Parameter Estimation Plots for Likert-Unit Parameters With Time-Unstructured Data (Slow Response Rate) in Experiment 3}
  \label{fig:exp3_plot_slow_resp_app}
  \includegraphics{Figures/exp3_plot_likert_time unstructured (slow response)} 
\end{figure}
\addtocounter{figure}{-1}
\begin{figure}[H]
  \caption*{Note. \textup{Panels A--B show the parameter estimation plots for the fixed- and random-effect days-to-halfway elevation parameters ($\upbeta_{fixed}$ and $\upbeta_{random}$, respectively). Panels C--D show the parameter estimation plots for the fixed- and random-effect triquarter-halfway elevation parameters ($\upgamma_{fixed}$ and $\upgamma_{random}$, respectively). Panels E--F show the parameter estimation plots for the fixed- and random-effect baseline parameters ($\uptheta_{fixed}$ and $\uptheta_{random}$, respectively). Panels G--H show the parameter estimation plots for the fixed- and random-effect maximal elevation parameters ($\upalpha_{fixed}$ and $\upalpha_{random}$, respectively). Panel I shows the parameter estimation plot for the error parameter ($\upepsilon$). Blue horizontal lines in each panel represent the population value for each parameter. Population values for each parameter are as follows: $\upbeta_{fixed}$ = 180.00, $\upbeta_{random}$ = 10.00, $\upgamma_{fixed}$ = 20.00, $\upgamma_{random}$ = 4.00, $\uptheta_{fixed}$ = 3.00, $\uptheta_{random}$ = 0.05, $\upalpha_{fixed}$ = 3.32, $\upalpha_{random}$ = 0.05, $\upepsilon$ = 0.05. Gray bands indicate the acceptable $\pm 10\%$ margin of error for each parameter and unfilled dots indicate cells with average parameter estimates outside of the margin. Error bars represent the middle 95\% of estimated values, with light blue error bars indicating cells with variability greater than 20\% of the parameter's population value. I considered dots that fell outside the gray bands as biased and error bar lengths that exceeded 20\% of the parameter's population value as indicative of low-precision estimation. Note that random-effect parameter units are in standard deviation units. See Table \ref{tab:exp3-alpha-theta-param-est} for specific values estimated for each parameter and Table \ref{tab:omega-exp3-slow-response} for $\upomega^2$ effect size values.}}
\end{figure}
```



## Appendix D: Parameter estimate tables

### Experiment 1

```{r exp-table-generation, echo=F}
exp_1_tables <- create_table_data_sets(param_summary_data = param_summary_exp_1, 
                                       wide_var = 'midpoint', first_col = 'measurement_spacing', second_col = 'number_measurements')
  
exp_2_tables <- create_table_data_sets(param_summary_data = param_summary_exp_2, 
                                       wide_var = 'sample_size', first_col = 'measurement_spacing', second_col = 'number_measurements')

exp_3_tables <- create_table_data_sets(param_summary_data = param_summary_exp_3, 
                                       wide_var = 'sample_size', first_col = 'time_structuredness', second_col = 'number_measurements') 

#remove measurement spacing columns 
col_to_remove <- which(str_detect(string = names(exp_3_tables$estimate_table), pattern = 'measurement_spacing'))

exp_3_tables$estimate_table <- exp_3_tables$estimate_table[, -col_to_remove]
exp_3_tables$removed_value_table <- exp_3_tables$removed_value_table[ , -col_to_remove]
```

\renewcommand{\arraystretch}{0.8}{0.9}
```{r exp1-alpha-theta-param-est, echo=F}
usepackage_latex('makecell')

print_param_table(table_ready_data = exp_1_tables$estimate_table, parameter_name = 'theta|alpha', 
            caption_name = 'Parameter Values Estimated in Experiment 1', 
            col_header_name = c('\\\\thead{$\\\\uptheta_{fixed}$ (Baseline)  \\\\\\\\ Pop value = 3.00}', 
                                '\\\\thead{$\\\\uptheta_{random}$ (Baseline) \\\\\\\\ Pop value = 0.05}',
                                '\\\\thead{$\\\\upalpha_{fixed}$ (Maximal \\\\\\\\ elevation)  \\\\\\\\ Pop value = 3.32}', 
                                '\\\\thead{$\\\\upalpha_{random}$ (Maximal \\\\\\\\ elevation) \\\\\\\\ Pop value = 0.05}'), 
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c('80', '180', '280'))
```

\addtocounter{table}{-1}

```{r exp1-beta-gamma-param-est, echo=F}
print_param_table(table_ready_data = exp_1_tables$estimate_table, parameter_name = 'beta|gamma', 
            caption_name = 'Parameter Values Estimated in Experiment 1 (continued)', 
            col_header_name = c('\\\\thead{$\\\\upbeta_{fixed}$ (Days to \\\\\\\\ halfway elevation)}', 
                                '\\\\thead{$\\\\upbeta_{random}$ (Days to \\\\\\\\ halfway elevation) \\\\\\\\ Pop value = 10.00}', 
                                '\\\\thead{$\\\\upgamma_{fixed}$ (Triquarter- \\\\\\\\ halfway delta) \\\\\\\\ Pop value = 20.00}', 
                                '\\\\thead{$\\\\upgamma_{random}$ (Triquarter- \\\\\\\\ halfway delta) \\\\\\\\ Pop value = 4.00}'),
             IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c(80, 180, 280))
```

\addtocounter{table}{-1}

```{r exp1-epsilon-param-est, echo=F}
print_param_table(table_ready_data = exp_1_tables$estimate_table, parameter_name = 'epsilon', 
            caption_name = 'Parameter Values Estimated in Experiment 1 (continued)', 
            col_header_name = c('\\\\thead{$\\\\upepsilon$(error) \\\\\\\\ Pop value = 0.03}'),
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c(80, 180, 280))
```

### Experiment 2

```{r exp2-theta-param-est, echo=F}
print_param_table(table_ready_data = exp_2_tables$estimate_table, parameter_name = 'theta', 
            caption_name = 'Parameter Values Estimated in Experiment 2', 
           col_header_name = c('\\\\thead{$\\\\uptheta_{fixed}$ (Baseline) \\\\\\\\ Pop value = 3.00}', 
                               '\\\\thead{$\\\\uptheta_{random}$ (Baseline) \\\\\\\\ Pop value = 0.05}'),
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```

\addtocounter{table}{-1}

```{r exp2-alpha-param-est, echo=F}
print_param_table(table_ready_data = exp_2_tables$estimate_table, parameter_name = 'alpha', 
            caption_name = 'Parameter Values Estimated in Experiment 2 (continued)', 
           col_header_name = c('\\\\thead{$\\\\upalpha_{fixed}$ (Maximal elevation) \\\\\\\\ Pop value = 3.32}', 
                               '\\\\thead{$\\\\upalpha_{random}$ (Maximal elevation) \\\\\\\\ Pop value = 0.05}'),
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```

\addtocounter{table}{-1}

```{r exp2-beta-param-est, echo=F}
print_param_table(table_ready_data = exp_2_tables$estimate_table, parameter_name = 'beta', 
            caption_name = 'Parameter Values Estimated in Experiment 2 (continued)', 
            col_header_name = c('\\\\thead{$\\\\upbeta_{fixed}$ (Days to halfway elevation) \\\\\\\\ Pop value = 180.00}', 
                               '\\\\thead{$\\\\upbeta_{random}$ (Days to halfway elevation) \\\\\\\\ Pop value = 10.00}'), 
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```

\addtocounter{table}{-1}

```{r exp2-gamma-param-est, echo=F}
print_param_table(table_ready_data = exp_2_tables$estimate_table, parameter_name = 'gamma', 
            caption_name = 'Parameter Values Estimated in Experiment 2 (continued)', 
            col_header_name = c('\\\\thead{$\\\\upgamma_{fixed}$ (Triquarter-halfway delta) \\\\\\\\ Pop value = 20.00}', 
                                '\\\\thead{$\\\\upgamma_{random}$ (Triquarter-halfway delta) \\\\\\\\ Pop value = 4.00}'),
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```

\addtocounter{table}{-1}

```{r exp2-epsilon-param-est, echo=F}
print_param_table(table_ready_data = exp_2_tables$estimate_table, parameter_name = 'epsilon', 
            caption_name = 'Parameter Values Estimated in Experiment 2 (continued)', 
            col_header_name = c('\\\\thead{$\\\\upepsilon$(error) \\\\\\\\ Pop value = 0.03}'), 
            IV_names =  c('Measurement Spacing', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```

### Experiment 3

```{r exp3-theta-param-est, echo=F}
print_param_table(table_ready_data = exp_3_tables$estimate_table, parameter_name = 'theta', 
            caption_name = 'Parameter Values Estimated in Experiment 3', 
           col_header_name = c('\\\\thead{$\\\\uptheta_{fixed}$ (Baseline) \\\\\\\\ Pop value = 3.00}', 
                               '\\\\thead{$\\\\uptheta_{random}$ (Baseline) \\\\\\\\ Pop value = 0.05}'),
           IV_names =  c( 'Time Structuredness', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```

```{r exp3-alpha-param-est, echo=F}
print_param_table(table_ready_data = exp_3_tables$estimate_table, parameter_name = 'alpha', 
            caption_name = 'Parameter Values Estimated in Experiment 3 (continued)', 
           col_header_name = c('\\\\thead{$\\\\upalpha_{fixed}$ (Maximal elevation) \\\\\\\\ Pop value = 3.32}', 
                               '\\\\thead{$\\\\upalpha_{random}$ (Maximal elevation) \\\\\\\\ Pop value = 0.05}'),
            IV_names =  c( 'Time Structuredness', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```

```{r exp3-beta-param-est, echo=F}
print_param_table(table_ready_data = exp_3_tables$estimate_table, parameter_name = 'beta', 
            caption_name = 'Parameter Values Estimated in Experiment 3 (continued)', 
            col_header_name = c('\\\\thead{$\\\\upbeta_{fixed}$ (Days to halfway elevation) \\\\\\\\ Pop value = 180.00}', 
                               '\\\\thead{$\\\\upbeta_{random}$ (Days to halfway elevation) \\\\\\\\ Pop value = 10.00}'), 
            IV_names =  c('Time Structuredness', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```

```{r exp3-gamma-param-est, echo=F}
print_param_table(table_ready_data = exp_3_tables$estimate_table, parameter_name = 'gamma', 
            caption_name = 'Parameter Values Estimated in Experiment 3 (continued)', 
            col_header_name = c('\\\\thead{$\\\\upbeta_{fixed}$ (Days to halfway elevation) \\\\\\\\ Pop value = 180.00}', 
                               '\\\\thead{$\\\\upbeta_{random}$ (Days to halfway elevation) \\\\\\\\ Pop value = 10.00}'), 
            IV_names =  c('Time Structuredness', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```

```{r exp3-epsilon-param-est, echo=F}
print_param_table(table_ready_data = exp_3_tables$estimate_table, parameter_name = 'epsilon', 
            caption_name = 'Parameter Values Estimated in Experiment 3 (continued)', 
            col_header_name = c('\\\\thead{$\\\\upepsilon$(error) \\\\\\\\ Pop value = 0.03}'), 
            IV_names =  c('Time Structuredness', 'Number of Measurements'), 
            column_names = c("30", "50", "100", "200", "500", "1000"))
```



